### 2016-08-17 paper/uist_2016/paper.tex
Upload LaTeX files for UIST 2016 submission

\documentclass{sigchi}

\toappear{Submitted for review.} % replace this with the actual copyright strip when preparing the camera-ready
\pagenumbering{arabic} % comment this out when preparing the camera-ready

\usepackage{balance} % balance columns on last page
\usepackage{booktabs} % use booktabs instead of ugly regular tables
\usepackage{graphicx}
\RequirePackage[l2tabu, orthodox]{nag}
\usepackage{microtype}
\usepackage{url} % consider a nicer typeface (like Inconsolata) for URLs

\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}

\interfootnotelinepenalty=10000 % split footnotes are ugly
\tolerance=400 % reduce how often words stick out into columns at the expense of word spacing

\graphicspath{{figures/}} % put all your figures in this folder

\begin{document}

\title{Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data}

\numberofauthors{3} % change this for additional authors
\author{
  \alignauthor {~}\\
    \affaddr{~}\\
    \affaddr{~}\\
    \email{~}\\
}

% DO NOT UNCOMMENT! submission is supposed to be anonymized
%\author{
% \alignauthor Eda Celen\\
%    \affaddr{Computer Science}\\
%    \affaddr{Brown University}\\
%    \email{edabingol@gmail.com}\\
% \alignauthor Phuc Anh D. Tran\\
%    \affaddr{Computer Science}\\
%    \affaddr{Brown University}\\
%    \email{pdtran@cs.brown.edu}\\
% \alignauthor Jeff Huang\\
%    \affaddr{Computer Science}\\
%    \affaddr{Brown University}\\
%    \email{uist@jeffhuang.com}\\ % Don't use my brown email here. Email addresses here get spam.
%}

\maketitle

\begin{abstract}
The Rewind system automatically recreates a digital memory of a past trip. It takes historical geolocation data and generates a stitched-together video made of streetside images from where a user has been. The images are manipulated based on the weather, time of day, and season to look like what the user may have seen when they were there. Users can go back and forth in time by scrubbing their pointer left or right over the video. Together, the composed Rewinds offer users a window into past travels. A user study of people collecting location data over two weeks reveals that users can remember the location from a photograph about half of the time, but when shown a Rewind, they can nearly always remember where they traveled. Furthermore, GPS users are less likely to remember the specifics of a location, and people are particularly interested in preserving Rewinds of infrequent trips and trips taken with others. Rewind serves as an experiment of the extreme scenario where people can freely roam and experience the world, keeping their mobile devices in their pockets, and still generate believable representations that capture the past.
\end{abstract}

\keywords{
Digital memories, geolocation, streetside images, travel.
}

% Obviously replace this with the appropriate classification.
% Check if the CHI format asks for using the 2012 ACM classification instead of the 1998 one.
\category{H.5.m.}{Information Interfaces and Presentation (e.g. HCI)}{Miscellaneous}

\section{Introduction}

Capturing a memory is a fundamental part of human nature. Not long ago, we chronicled significant moments in our lives through journals and diaries, to be filled at the end of the day. Then came the cameras, to take with us when we expected a memorable moment. Now smartphone cameras are always nearby, ready for an opportunity to capture both the spectacular and the mundane. This paper introduces Rewind, the next evolution in digital memories: nothing to prepare or take out, just rewind and replay a trip from the past.

While a camera or camcorder can explicitly capture a snapshot of an interesting moment, that one snapshot is only a tiny part of an experience, made even tinier when traveling. In fact, most travel experience happens in transit: the perfectly cloudy stroll from the Eiffel Tower to the Louvre, the sound of dry gravel crackling under bus tires traversing up to Machu Picchu or monsoon rains drumming on all the tin roofs of Hanoi, and even the flight over the Florida Keys on the way to the sun-bathed Caribbean islands. A simple photograph is conclusively lacking in context.

Geolocation data that can be automatically tracked and logged on a smartphone can be used to create context: to look up the weather at each moment, retrieve streetside photos from Google Street View at every step, and compute the mode of transportation (e.g., \cite{zheng2008learning}) and nearby geographical features. The Rewind system takes those cues and manipulates the conditions of retrieved photos to re-imagine what a person saw at some past point in time. The sequences of visuals are stitched together into an interface that allows users to directly manipulate the point in time being shown by scrubbing back and forth (Figure~\ref{fig:scrubbing}). So all a person has to do is enable location tracking on their mobile device to later rewind and re-experience a past trip.

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{scroll}
     \caption{Users move the stitched-together images forward and backward in time by scrubbing their pointer.}
     \label{fig:scrubbing}
\end{figure}

Rewind applies a framework for exploring fundamental questions about the human experience. Normally, it is difficult to ask someone about parts of their past that they do not entirely remember, because they do not remember what they do not remember. If you ask someone about a picture of themselves from ten years ago and they do not remember that particular point in time, there are no steps for re-remembering. Using timestamped location data, we investigate whether a more realistic and contextual digital memory can help remind users of times from the past. Perhaps these Rewinds, series of images moving back and forth, can even help the forgetful recover past experiences. This could be done for people who are already tracking their location intentionally (using a smartphone app like Moves or GPSLogger), or for the many people for whom location tracking has been enabled by default on Android phones. The Rewind system generates stitched-together and manipulated photos, called Rewinds, which we use to learn what makes memories memorable, believable, and desirable. Participants in a two-week study looked at their own Rewinds and assessed which trips or places were more memorable, whether the Rewinds felt believable as their own memories, which memories they desired to preserve, and in this process, helped us gain a sense of what Rewinds are beyond static photographs.

We realize that not all memories are equally desirable. Through our study, we discovered not only what factors contribute to making a trip or place more memorable, but whether these are memories worth preserving. Are there aspects of a route that make a person want to review or relive a trip?

The two main contributions of our work are: 1) the design and implementation of the system for generating Rewinds, and 2) findings from a two-week user study where participants review Rewinds to describe what makes them memorable, believable, and desirable.

\section{Related Work}
\subsection{Digital Memories}
Rewind is guided by literature about mediated memories, which provides a theoretical underpinning behind how the Rewind experience is constructed. \textit{Mediated Memories in the Digital Age} offers inspiration informing the relationship between experiences and memories \cite{van2007mediated}. van Dijck notes, ``Remembering is vital to our well being, because without autobiographical memories we would have no sense of past or future, and we would lack any sense of continuity'' (pg. 3). Rewind aims to give the user this sense of continuity in a time segment which has a past and future. By picking a start and end location from a particular trip and generating a Rewind between these points, the user relives their memories in a continuous manner.

van Dijck also states that ``Our memories organize themselves according to our actual or perceived participation in a (temporal) collectivity---a group vacation, a school class, a family, a generation---and recall tends to lean on a sense of belonging or sharing rather than on a relocation in real time or space'' (pg. 9). Relating to the concept of organization, our user study explores whether traveling alone or with others affects the remembrance and the value of a past trip.

Our study also extends the current state of knowledge about memory landmarks, although in a visual form. Horvitz et al. discuss how some events are particularly able to guide recall \cite{horvitz2004learning}. For example, these may be meetings with a high probability that the user will be in attendance. In Rewind, we seek to discover whether certain characteristics of a location, such as it being frequently visited or far away from home, serve as memory landmarks in the same way.

Previous work has been done in moving memory from the realm of the mind to digital space in the field of psychology. Legge et al. experiment with the Method of Loci, a mnemonic technique where one stores things-to-be-remembered in a mental construction of a familiar place, called a memory palace \cite{legge2012building}. The stored remembrances can be retrieved by going through the memory palace in one's mind. Legge et al. found that virtual environments performed as well as mental environments for remembering serial lists. Rewind takes digital location-based memories and enhances them further for a virtual environment. Our user study explores whether Rewinds as a digital mnemonic device can perform as well as their predecessor, the photo.

Perhaps the most similar system to Rewind is Google+ Stories \cite{googlestories}, where the location coordinates are extracted from a user's photos and overlaid on a map. The interactivity of the photo album allows users to feel like they are going through a trip, rather than simply a series of photographs. Rewind takes this a step further by testing the extreme case where no personal photos are available, and everything is generated purely from timestamped location data that has been collected automatically.

\subsection{Location History}
A project that also leverages location data to capture the essence of a trip is by Thudt et al., who discuss the creation and investigation into the challenges and limits of visual mementos \cite{thudt2016visual}. The authors define visual mementos as ``visualizations of personally relevant data for the purpose of reminiscing, and sharing of life experiences.'' They present one implementation example of visual mementos that involves GPS location histories. This common goal of providing a way for people to reminisce about their trips reinforces the purpose of Rewind. Another reinforcement can be found in the way that their system is enhanced with geotagged photos from Flickr. The three main challenges presented in Thudt et al.'s paper are: 1) evoking familiarity, 2) expressing subjectivity, and 3) obscuring sensitive data. The authors attempt to address those challenges in the tool they built, called Visits, and their findings from the case study show that there is benefit to the visualization of personal mementos. Rewind builds on their work by breaking a trip down into smaller sequences and recreating the visual experience, whereas Visits relies on a more traditional top-down map view and timeline.

Other research has used location history not to create a new interface for the user, but for other applications. Neuhaus's UrbanDiary project \cite{neuhaus2010urbandiary} uses GPS devices to create and visualize ``personal tracks'' as well as collective tracks for a city. These personal tracks are created using data from time and location tracking for each trip by each individual. The researchers focused on comparing the different visualization techniques used to portray the data. A two-month study involved twenty participants wearing GPS devices, but as the paper was published in 2010, they did not use smartphone GPS data. Each participant wore a device, and the paper suggests that doing so helped them feel in charge of the data collection. Furthermore, GPS tracking is noted as a good method for collecting data about movement of each person. A further exploration of this project was what participants' perceptions were while moving. The data from this study shows each person's location data can be used as a unique fingerprint. This supports the idea that location data can be used to help people recreate their individual travel experiences, for purposes of reminiscing and even sharing. In a similar vein, Cranshaw et al. \cite{cranshaw2012livehoods} recognize the ability for collective location data to understand the social patterns in a city. That everyone travels their own path, and this is part of their identity, is a core theme in Rewind.

Further work in GPS user behavior has been done by Leshed et al. to see how users interpret and interact with spaces differently when using in-car GPS navigation \cite{leshed2008car}. They found that ``the GPS disconnects the drivers from the external environment.'' As a result of the drivers' disengagement with their surroundings, ``the process of interpreting the world, adding value to it, and turning space into place is reduced to a certain extent and drivers remain detached from the indifferent environments that surround them.'' Since Rewind touches on the topic of travel, it also inherently deals with car travel and GPS. We imagine that regular GPS users will interact with Rewinds differently.

A common thing to do with location history data is to develop a visualization of it. Larsen et al. use a spiral chart for a user to see the continuity of their locations, where days are put around the spiral \cite{larsen2013qs}. This visualization allows users to explore and discover patterns in their daily lives. An early implementation of Visits by Thudt et al. focuses on the map and timeline views of location, interleaving them together \cite{thudt2013visits}. In their visualization, users can move from location to location using their pointer, which at the same time moves back and forth in time. This partially inspired the scrubbing technique in Rewind of traveling back and forth in time by scrubbing left and right, at the same time changing the image of what was seen at that time.

Finally, as location reveals where a person was at certain times, and is often a comprehensive view of someone's routes, there are substantial privacy concerns for this type of data. Not only can it reveal a person's home location, but it can also be used to forecast where they might be at a certain time in the future, or where they might not be. Lindqvist et al. \cite{lindqvist2011m} investigate the motivation behind sharing location data, and find that people are sensitive to privacy especially for places frequently visited (like their home). Tang et al. study the feeds of location histories meant for sharing, and discover that users desire different levels of details to be shared with other depending on their relationship with that person \cite{tang2011understanding}. The location itself is often not the concern, but that it is associated with an activity, which is the more sensitive variable. Users also unanimously disliked sharing time-based location, as it was too privacy-invasive. This informed our design of Rewind, where the generated experiences will not specify exactly the location, nor the time it represents. Users have the option to explicitly share a Rewind with another person after reviewing it themselves.

\begin{figure}[h]
   \centering
     \includegraphics[width=1\linewidth]{Rewind-Sample-Grid}
     \caption{Rewinds are generated by stitching together Google Street View images of consecutive points on a given route. They are played from left to right to simulate a person on the move.}
     \label{fig:rewinds}
\end{figure}

\section{The Rewind System}
Rewind is a system that takes user geolocation tracking data as input and outputs systematically selected location points that are shown to the user as a photo-video pair: a Google Street View image of the location and a Rewind that includes the location. A user's geolocation tracking data includes latitude and longitude coordinates, timestamps of when the user was at given coordinates, and an accuracy score for each geolocation record. Rewind expects the geolocation data to be formatted as JSON (but is compatible with other location-based formats like GPX), particularly in the same format that Google Takeout generates for Location History.

Rewind is implemented as a client-side only application and therefore does not transfer sensitive user data or store it; it does not have a server component for communication. The system is written with standard web technologies: HTML5, CSS, and JavaScript, in addition to various open source libraries and services. These libraries include the Google Maps API, determining routes between location points and retrieving Google Street View images of any given location; the StreetviewSequence.js library is also used in the process of generating Rewinds \cite{streetviewsequence}. The library takes in data in the form of a Google Route and composes a video sequence by stitching together Google Street View images from multiple points on the given route (Figure~\ref{fig:rewinds}). The CamanJS library \cite{caman} is used to manipulate the appearance of Google Street View images such as brightness, contrast, and saturation in order to better replicate the environmental conditions at a given time. More sophisticated image manipulation techniques were investigated \cite{laffont2014transient} but deemed to slow for Rewind's current real-time use.

Rewind generates location points for the user, using smart filtering based on visit frequencies to decrease the data noise and diversify the locations shown to the user. First, the user uploads their geolocation data to Rewind's main page. From there, less accurate location records are filtered out using the accuracy ratings provided by Google. Any location recording that has an accuracy radius greater than 200 meters is ignored. The accepted data is stored in memory to prepare the user's location points. A location frequency map is generated by counting the number of times each location appears in history. In order to minimize the minor coordinate variations and to identify close coordinate pair records, only the first 3 decimal digits of coordinates are used when counting the number of appearances. The location with the highest number of visits is marked as user's home. We then use the Haversine formula to calculate the individual distance between all given locations and the user's home, attaching the distance data to the location. % Finally, for the user study, Rewind generates the user's set of locations based on visit frequency: 5 from the least visited locations, 3 from the most visited locations, and 2 randomly selected locations.

Once the location set is determined, photos are retrieved from Google Street View and manipulated for time of year and time of day. For each selected location, a Google Street View image is requested and the timestamp of when the user visited the location is used to determine how the image should be manipulated to appear as close as possible to what the user saw. For the time of year, adjustments are made to the image's saturation (Figure~\ref{fig:season}), and for the time of day (Figure~\ref{fig:timeofday}), adjustments are made to the image's brightness. For example, if the location's timestamp denotes the summer, the image will be adjusted to have higher saturation to account for the vivid colors during that season. In the same vein, an image taken at noon will be adjusted to have higher brightness whereas an image taken at a time closer to sunset will be adjusted for lower brightness to account for the amount of sunlight captured. Taking this into account, Rewind evaluates the saturation and brightness of each Google Street View image as it is retrieved, and makes adjustments to mimic the actual date and time of user's visit. Weather adjustments for images are made at the same time as date and time adjustments. Using data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations, Rewind checks for factors that would require image adjustments. In our study, we adjusted only images from [anonymized: our state/province] and only for precipitation. However, it would not be difficult to do this for images from any location with a larger weather database, and other types of weather can be used to make adjustments besides precipitation. For our study, if there was precipitation at the time the user visited the location, the contrast is lowered to imitate cloudiness or rain. After these adjustments, the location set is now ready to be shown to the user.

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{Rewind-time_of_day}
     \caption{Brightness of Rewind images are manipulated in order to mimic the time of day that the trip took place.}
     \label{fig:timeofday}
\end{figure}

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{Rewind-seasons}
     \caption{Saturation of Rewind images are manipulated in order to mimic the season that the trip took place.}
     \label{fig:season}
\end{figure}

% (Jeff): I think this is an unnecessary detail for this paper
%For the user study, Rewind displayed one image at a time on the browser, along with an identifier code. The first character in the code is a letter from the group \{R,M,L\}, followed by an integer number. The first character represents the visit frequency of the location shown in the image: R for randomly selected, M for points selected from the most frequently visited locations, and L for points selected from the least frequently visited locations. The integer that follows denotes the distance in meters between a user's home and the given location "as the crow flies."

Users can click on the images to load the accompanying ``trip'' videos (stitched images), or Rewinds. The purpose of Rewinds is to help users remember locations and trips. Rewinds are composed of locations visited on the same date as the Rewind's corresponding image. When the user loads a Rewind, all the locations the user visited on that day are gathered and sorted, after which a route is mapped between the locations using the Google Maps API. This route data is passed to StreetviewSequence to generate Rewinds by stitching together images. For each point on a given route, StreetviewSequence requests panorama data from Google and determines the appropriate pitch and heading values to get the correct portion of the panorama. Those values are sent to Google Street View along with the necessary geolocation data to get the images that will be stitched together to make the Rewind.

In order to account for time of day and season changes, StreetviewSequence library is modified to allow Rewind to intercept and manipulate each frame of the trip video, similar to the manipulations applied to the 10 location images. Once all the images within a trip are gathered from Google Street View and processed with CamanJS, users can play Rewinds in a loop, or scrub forward and backward over the video to investigate individual images more closely.

\section{User Study}
\subsection{Research Questions}
Rewind enables us to ask questions that have not been possible to ask before, due to the scarcity of comprehensive data about where someone has been. We performed a within-subjects comparison of Rewind and static photography that are not sequenced together. By showing a user both types of digital memories, we can begin to understand what are the features that make the Rewinds more realistic are more believable for different trips.

There are some specific research questions we investigate about people's behaviors surrounding digital memories.

1) Do certain features of a Rewind make it more memorable? Are the participants able to recall a particular location or route most often in Rewinds with particular features?

2) Which Rewinds do users wish to save, and which ones would you like to share? For example, frequent trips close to home, long one-time journeys, or just the destinations and landmarks that the travel takes them to? Are these the Rewinds that are the most familiar, or ones that are unique and are not instantly recognizable?

3) Do people who frequently use a GPS have different memories than those who don't? What about frequent travelers or people who are traveling with companions? Again, this is something that has previously been difficult to study without location histories.

\subsection{Procedure}
A user study following a two-week tracking period with 21 participants from the [anonymized] area investigated the influence of Rewinds on recollection, and evaluated their memorability and believability.

Participants for the study were recruited online through Craigslist classifieds and local Reddit communities for the [anonymized] area. Offline, ads were posted in cafes and other small businesses in the the city. Of the 21 total participants, 13 identified as men and 8 identified as women. Participants ranged from ages under 20 to over 50. Most participants were local residents, with occupations varying from librarian to medical researcher to office worker to musician. A fifth of the participants were undergraduate or graduate students.

Study participation included a location-tracking setup session, at least twelve days of tracking, and a follow-up user study. At the location-tracking setup, participants were asked to activate geolocation tracking on their mobile phones. Participants with Android devices used Google's built-in location reporting services for tracking. iPhone users downloaded Google+ to use the same service. Participants with devices incompatible with Google's location reporting services were provided with an older Android device that used the app GPSLogger\footnote{\url{https://play.google.com/store/apps/details?id=com.mendhak.gpslogger&hl=en}} for tracking. Participants were asked to keep their phone charged and on their person as much as possible for approximately two weeks, until they could come in for a final interview with the experimenters.

At the in-person interview, participants were shown a series of images and accompanying Rewinds that represented the trips they took during the tracking period. The user's GPS data was trimmed so that images and Rewinds are created from only the past fourteen days at most. Of the ten image-Rewind pairs that were shown, five were of trips taken infrequently, three were of trips taken most frequently, and the remaining two were random.

At the beginning of the study, participants were asked for their gender, whether they considered themselves a frequent traveler, and whether they tended to use GPS in places they were already familiar with. Participants who used GPS in familiar locations were considered regular GPS users, and participants who didn't were considered non-regular GPS users.

For each image-Rewind pair, the participant was first shown an image of a location from their GPS data and asked to answer questions about it. Then they were shown a Rewind of the trip during which the image showed up, and the participant was asked to answer questions about the Rewind. While the Rewind was playing, participants could hover over the Rewind panel and scrub backwards and forwards horizontally through the images that composed the video. This allowed participants to ``walk through'' their memory at their own pace.

For both the image and the Rewind, the participants were asked questions related to memory recall. They were first asked whether they remember the locations. If they could, they were then asked to discuss specifics of the location: Participants were asked whether they could name the streets and whether they could name buildings, landmarks, or places around the locations. If the participant was looking at a Rewind, they were also asked whether they remembered the exact trip. To evaluate memorability of the photo or Rewind, participants were asked whether they would keep the image or video, and why or why not. Then they were asked whether they traveled alone or with a companion. Lastly, participants were asked questions related to the believability of the digital memory: was the photo or video accurate to their memory? Why or why not?

In addition to asking questions, we observed the users as they examined the Rewinds of their trips, since they could passively watch the Rewind or actively scrub through the individual images that made up the video. The user study took between 30 minutes to an hour for each participant, and participants were compensated \$30 for their time at the end of the study.

Data from three participants was not included in the results of this study. Two of the aforementioned participants were not able to do the user study. One of those participant's data points consisted of only one location. The participant used a mobile device provided by the study, so it's likely that they did not carry the device on their person. The other participant did not complete the user study due to health and scheduling reasons. The last participant only collected three days of data because they had their phone replaced during the tracking period and did not reactivate Google's location reporting services on the new device. This participant completed the user study, but we did not include the data gathered during this participant's session in the results.

\section{Findings}
The findings of our user study center on the participants' relationship to the Rewinds created from their location data. We focus on the participants' judgments of their Rewinds' memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds. We also discuss how the participants interacted with and reacted to their Rewinds. The results use data from user studies conducted with 12 men and 6 women. 6 of 12 participants identified themselves as frequent travelers. Additionally, 6 of 12 participants were regular GPS users.

\subsection{Memorability}
Rewinds are meant to engage a person's memory. To see if the Rewind system selected and portrayed memorable locations and trips, we investigated whether participants were able to remember the location shown in a photo or recall the trip portrayed by a Rewind. Location memorability is determined by whether or not the participant remembers the location depicted in a photo. Trip memorability is determined by whether or not the participant remembers and can distinguish the exact trip portrayed in a Rewind. In this section we will look at differences in location and trip remembrance between participants who are regular GPS users and participants who do not use GPS regularly, and examine the effect of location distance and visit frequency on memorability.

\subsubsection{Rewinds and Photos}
When participants were shown a street side photo from their location history, they were asked whether they recognized the location in the photo. In 50\% of cases, participants said they did. When they were shown the Rewind associated with that photo, nearly all participants knew the location captured---97\%. This result shows the impact of Rewind on memorability, as the addition images before and after the static photograph greatly impacts whether a past location is familiar to a user.

\subsubsection{GPS Usage}
Our findings show that participants who are not regular GPS users remember locations and trips more often than participants who are regular GPS users (Figure~\ref{fig:gpsmemory}). When asked whether they remember the location or trip being shown in a photo or Rewind, participants who do not use GPS regularly gave a positive answer 58\% of the time for location remembrance and 56\% of the time for trip remembrance. Regular GPS users remembered locations 33\% of the time and trips 47\% of the time. The data shows that participants who are regular GPS users did not remember the locations they visited or trips they took as often as participants who are not regular GPS users. Since regular GPS users are frequently directed step-by-step on how to navigate their environment, they may not pay as much attention to their surroundings. This diminished locational awareness could be the reason why regular GPS users had a lower remembrance rate for locations and trips. From these percentages, we also see that regular GPS users remember trips more often than they remember locations, while there is little difference between the two for participants who do not use GPS regularly.

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{GPS_remembrance_2}
     \caption{Regular GPS users remembered locations 33\% of the time and trips 47\%, compared to 58\% and 56\% for non-regular GPS users.}
     \label{fig:gpsmemory}
\end{figure}

\subsubsection{Visit Frequency}
Location memorability and trip memorability are affected differently by frequency of visits (Figure~\ref{fig:frequencymemory}). Location memorability is highest for places that are most frequently visited by the participant, while trip memorability is highest for places that are least frequently visited. The more frequently a place was visited, the more likely it was that the participant remembered the location when it was shown to them at the study. In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places. This effect does not occur for trip memorability. In the most frequently visited places, trips are remembered 51\% of the time. Instead of seeing trip memorability decrease for least frequently visited places, this factor increases to 56\%.

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{RML_2}
     \caption{Locations were more likely to be remembered where participants had visited the place more, whereas trips were more likely to be remembered where participants had visited the place less.}
     \label{fig:frequencymemory}
\end{figure}

\subsubsection{Distance}
The distance away from the participant’s home had differing effects on location memorability and trip memorability (Figure~\ref{fig:distancememory}). Distances ranged from 0 to 206,155 meters. For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from user's home location; Group 1 corresponded to a range of 10--100 meters; Group 2 corresponded to a range of 100--1,000 meters; Group 3 corresponded to a range of 1,000--10,000 meters; Group 4 corresponded to a range of 10,000--100,000 meters and Group 5 corresponded to a range of 100,000--1,000,000 meters from user's home location. As the distance increased, location memorability decreased, suggesting that locations further away from home were less likely to be remembered. Location remembrance dropped from 100\% for Distance Group 0, or home, to 74\% for Distance Group 1 down to 10\% for Distance Group 5, which represented the locations furthest away from home. For trips, remembrance was largely the same for most distance groups, except for distances that were very close to home and distances that were very far, but not the furthest, from home. Trip remembrance was at 60\% for Distance Group 0, then dipped momentarily to 25\% in Distance Group 1 before increasing back up to 60\% for Distance Group 2, 3, and 5. Only Distance Group 4 wavered with a trip remembrance rate of 48\%. This data suggests that participants often did not remember or could not distinguish the exact trips occurring in locations very close to home, where most trips happen, nor could they distinguish the exact trips that happened very far, but not especially far, from home.

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{distance}
     \caption{Location remembrance is inversely correlated to its distance from a participant's home.}
     \label{fig:distancememory}
\end{figure}

\subsubsection{Travel Companions}
Our findings show that trip remembrance is influenced by the presence of travel companions. As one might imagine, trips that were taken with other people were much more memorable than trips taken alone. Participants were not able to remember the exact trip of 33\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 89\% of Rewinds that were taken with company.

\subsection{Believability}
Rewinds should be believable as memories, and be able to serve as digitally-sourced memories of locations and trips. For that purpose, we define the believability of a Rewind as its accuracy to the participant's memories. Here we will look at how GPS usage and visit frequency affect participants' believability judgments, and discuss the features that participants pointed out as either contributing to or detracting from a Rewind's believability.

\subsubsection{GPS Usage}
Our results show that participants who were not regular GPS users found photos and Rewinds to be accurate to their memory more often than regular GPS users did. Photos and Rewinds could only be considered accurate to a participant's memory if the participant first confirmed that they remembered the locations in them. The results in this section reflect percentages from a total pool of only photos and Rewinds that have remembered locations. Regular GPS users found 65\% of photos and 45\% of Rewinds accurate to their memory out of the photos and Rewinds in which they remembered the locations. Participants who did not regularly use GPS found 78\% of photos and 63\% of Rewinds accurate to their memory. So far, our findings show that regular GPS users remembered the locations in their digital memories less often, and from the locations they did remember, they were less likely to find a photo or Rewind accurate to their memory. One participant who identified as a regular GPS user said, "I really don't pay attention to my surroundings when I'm driving. I'm focused on the GPS and the road," when asked about the accuracy of a trip.

% (Jeff): this figure is probably best replaced with some text
%\begin{figure}
%   \centering
%     \includegraphics[width=1\linewidth]{GPS_believability_2}
%     \caption{Participants who did not use GPS regularly found Rewinds to be accurate to their memory more often than regular GPS users did.}
%     \label{scroll}
%\end{figure}

\subsubsection{Visit Frequency}
We found that the more visits a location had, the less likely it was for the Rewind associated with it to be judged as accurate by the participant. Trips with a location that was visited most frequently by the participant were said to be accurate 75\% of the time. The more a person visits a location, the more they may notice inconsistencies between the actual place and a digitally-fabricated memory of it. Trips with a location that was visited least frequently had a higher accuracy rating of 82\%.

\subsubsection{Features}
To get a better understanding of what the important features of locational memories are, we looked at participants' responses to why they thought a Rewind was or was not accurate to their memory. Participants attributed the accuracy of a Rewind to the presence of different man-made structures. The most highly occurring answers to why a Rewind was accurate were: the route, the highways, roads, and streets, the signs, the landmarks, and the buildings. The reasons why a Rewind did not seem accurate to participants' memories included more temporal and environmental features. When participants responded that a Rewind was not accurate to their memory, they cited the streets, the season and foliage, the time of day, and the angle the Rewind viewed the world at as factors of inaccuracy.

Our results show that GPS usage influences what features participants pick out when deciding whether Rewinds are accurate reflections of their own memories of their trips. When we split the responses of regular GPS users from the other participants' responses, we saw that GPS users looked at signs in the Rewind the most to determine accuracy. Participants who were not regular GPS users cited the route and surrounding landmarks as features which made the Rewind believable as memories.

\subsection{Desirability and Value}
For Rewinds to be useful, they need to have value to their owners. We measured the value of photos and Rewinds by asking participants if they would want to keep the photo or Rewind after seeing it. In general, participants did not want to. In this section we will look at how the value of Rewind's digitally-fabricated memories differs between participants who consider themselves frequent travelers and participants who don't. We will also examine how visit frequency and travel companionship affect the desirability of a Rewind.

Overall, participants wanted to keep 11\% of the photos they were shown and 15\% of the Rewinds they were shown.

\subsubsection{Frequent Travelers}
Our study found that participants who considered themselves frequent travelers were more likely to keep their photos and Rewinds than participants who did not identify as frequent travelers (Figure~\ref{fig:frequencydesire}). Frequent travelers kept 13\% of the photos they were shown and 21\% of Rewinds. But participants who identified as infrequent travelers kept only 7\% of photos and 2\% of Rewinds. The results show that those who consider themselves frequent travelers tend to place higher value on digital memories than those who do not identify as frequent travelers.

\begin{figure}
   \centering
     \includegraphics[width=1\linewidth]{FreqTraveler_keep_2}
     \caption{Frequent travelers are more willing to keep copies of photos and Rewinds.}
     \label{fig:frequencydesire}
\end{figure}

\subsubsection{Visit Frequency}
We found that the desirability of a Rewind is partly influenced by how much the participant visits the location associated with the Rewind. Rewinds containing a location visited most frequently by the participant are kept 8\% of the time. This percentage increases significantly if the Rewind contains the location visited least frequently by the participant. Rewinds that include the least visited location are kept 13\% of the time. This data suggests that Rewinds are more desirable if they portray a trip that has locations that are not visited often.

\subsubsection{Travel Companions}
Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept. Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep. Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others. The data shows clearly that a Rewind is considered much more valuable if the trip it depicts was taken with company.

\subsubsection{Participant Responses}
When asked why they wanted to keep or not keep a photo or Rewind, patterns emerged in the participants' answers. Participants didn't want to keep anything that was "no use" or had "no meaning or significance." One participant said they "didn't need any more memories of work." Some participants acknowledged the "good composition," and one said, "It's not a bad photo but it wasn't taken by me." Participants were most likely to keep photos that reminded them of good memories,

\subsection{Participant Reactions}
There was a range of behaviors and attitudes toward Rewinds from the participants. One participant called Rewinds "creepy, eerie," and said they might "show them to a friend who's a conspiracy theorist." Another participant proclaimed that they weren't "paranoid about technology." Many participants, especially regular GPS users, examined signs in Rewinds intensely, looking at highway exit signs to try to remember their trip. Other participants did not feel positive after watching their Rewinds, saying that they "just realized how often [they] take the same route," or that they felt like they "needed to switch up [their] routine." One participant was amazed, and exclaimed, "It's like it's happening!" But the most important responses were from participants who changed their responses after recognizing an image in their Rewind: "I recognize the photo now." The Rewind had helped them remember the location of the original image.

\section{Discussion}
This work explores a future where digital memories can be retrieved in an instant, regenerated from trace data which is becoming increasingly ubiquitous. The ability to perform these actions encourages humanist values of self-reflection and intentional living. We seek to design an application that can produce moments of delight and thoughtful reflection.

While the study results provide a wealth of correlations between varying factors and participant groups, our most significant findings pertain to the effects of regular GPS usage, visit frequency, and travel companionship on Rewind memorability, believability, and desirability.

We found that regular GPS users are less able to remember locations and trips, and more often rely on road signs to jog their memory or determine Rewind believability. This confirms Leshed et al.'s findings that GPS users are typically disengaged with their environment \cite{leshed2008car}. We found that while GPS users had lower remembrance overall, the group experienced a huge jump between location remembrance and trip remembrance, suggesting that Rewinds may actually engage GPS users' memories.

We see high visit frequencies resulting in lower Rewind believability and low visit frequencies making Rewinds more desirable. This is quite intuitive because if you visit a place often, it is harder to distinguish the exact, particular trip you took to that place, just because there are more trips to choose from. Locations that you visit infrequently are likely special occasions, thus making the Rewinds more desirable because they present a precious memory.

Lastly, our results show that Rewinds of trips taken with a companion hold more value and are more memorable to participants. This supports van Dijck's idea that ``recall tends to lean on a sense of belonging or sharing'' \cite{van2007mediated}.

%What applications or tasks are possible now that we have made these discoveries/inventions?
%What can this be used for?
%		Ex: It can help people remember the past

%What are some implications for designing systems/interfaces in the future?
%	What would you tell a person who will design a similar system?
%		Ex: Scrolling is important for the user to be able to take a closer look at Rewinds., talk about features for believability

There are some inherent limitations to Rewind due to today's technologies. Location data is imperfect, and often can hop around the map, showing the user places they may have never been. But even more important is the limits to how realistic a Rewind can truly be. People and conversations, which are what we think about often, can't be shown in Rewinds without some additional recording device. Therefore, while Rewind does not recreate the exact memory, it's more of a proxy for what environment where the memory occurs.

\subsection{Rewinds More Real and More Salient}

How realistic can Rewind become in the near future? Currently, most street side images are of the road, as cameras that take these photos are attached to cars. But other forms of imagery has recently arrived: Google and Bing have expanded their street side photos to inside buildings, on hiking trails, and campus greens. Satellite images can be used for travel in airplanes and simulate the view outside the window from seat 17F. More sophisticated image manipulation algorithms are already here, but take many minutes to run offline (e.g., \cite{laffont2014transient,shih2013data}). Eventually, as computing performance continues to improve, and further research is done on the software, it's likely that entire Rewinds can be adjusted in real-time.

Besides visuals, a salient part of a memory is in the sounds from the past. This can be replicated through a number of styles: the pitter-patter of footsteps or sound of driving through the streets (mode of transportation can be detected purely from geolocation data \cite{zheng2008learning}), the whistle of the winds or thunderstorms at night, and even sounds based on geographical features like when the user was near water or by a outdoor market. van Djick explains, ``One memory rarely encompasses all sensory modes, because we tend to remember by selecting particular ones. For instance, we may recall a mood, locale or era through a particular smell (such as the smell of apple pie in the oven triggering the image of your mother's kitchen on Saturday afternoons), or we may remember a person by his nasal voice or twinkling eyes'' \cite{van2007mediated} (pg. 20). Audio and visuals combined can enrich the experience, as Rewind uses environmental data such as weather information or the season to incorporate other sensory modes. By leveraging environmental sensory data, users may be stimulated to recall something that may have been forgotten otherwise, and this information makes the experience feel more real.

In another direction, Rewind can be applied to virtual reality environments. Besides the visual and audio immersion, in a virtual reality environment, the user is physically situated inside the environment. Rather than sitting in a chair looking at a screen, the user is standing where they would have been standing in the past. This changes the experience from ``watching'' to ``being'' present in the past. Virtual reality environments have already been used as a tool to study human memory \cite{gamberini2000virtual}, so it is a natural extension for Rewind. To stand there with the power to scrub back and forth in time could create a new mode for experiencing memories.

One of the applications of Rewind is to support people with memory loss, those who have Alzheimer's or short-term amnesia. For example, photographs have been known to stimulate the memory of people afflicted with Alzheimer's \cite{grandmaison2003critical}. To be able to do the same, but with a sequence of realistic audio-visuals, may turn something that was forgotten back into a memory, and doing so for an important place or trip would be exciting.

\section{Conclusion}
We forget so much. So our own memories are incomplete glimpses of the past. Yet they are part of who we are. The ultimate goal of the Rewind system is to envision a new way to digitally capture memories in the future. As there are an increasing number of sensors (cameras, weather, microphones) in the environment, being able to reconstruct a rich experience becomes more feasible. Personal reflection and recalling the past has significance for everyone. A new form of digital memories is a direct tangible benefit people can get from their user own personal informatics data, and one that they have full control over.

Our study of people using Rewinds over 2 weeks reveals some interesting findings. When people are shown just a photograph, they remember the location half the time; but when shown a Rewind, participants nearly always remembered the location. We find that people who commonly use GPS devices do not remember places as well; they seem to notice street signs, routes, and landmarks more so than those who do not. When Rewinds are inaccurate, it's from people noticing the wrong season, view angle, or time of day. These are challenges that we are facing but trying to address through image manipulation based on past data. And we find that people are more likely to remember places that they visit more frequently, as expected. Rewinds are not really for places that you go often, as for those, the location is more memorable as a photo. But infrequent trips are where Rewinds can help someone resurface a memory, and take you back to the road less traveled.

\section{Acknowledgments}
[anonymized for review]

\balance

\bibliographystyle{SIGCHI-Reference-Format}
\bibliography{paper}
\end{document}

### 2016-08-17 paper/uist_2016/build.sh

@@ -1,0 +1,9 @@
+pdflatex paper.tex
+bibtex paper
+pdflatex paper.tex
+pdflatex paper.tex
+rm paper.log
+rm paper.blg
+rm paper.bbl
+rm paper.aux
+rm paper.out

### 2016-08-25 paper/uist_2016/paper.tex
audacious changes of the system section; to be continued..

@@
 
-Capturing a memory is a fundamental part of human nature.
+Preserving memorable moments is a fundamental part of human nature.
 Not long ago, we chronicled significant moments in our lives through journals and diaries, to be filled at the end of the day.
@@
 \section{The Rewind System}
-Rewind is a system that takes user geolocation tracking data as input and outputs systematically selected location points that are shown to the user as a photo-video pair: a Google Street View image of the location and a Rewind that includes the location.
+\textit{Rewind} recreats the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers.
+Differing from previously studied hyperlapse creation techniques by ***(Neel Joshi's and Johannes Kopf's work from Microsoft)****, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight.
+\textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images.
+The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimentional temporal cues.
+\textit{Rewind} is a client-side only application implemented with Google Maps API and third-party Javascript libraries, and therefore does not transfer sensitive user data nor store it.
+
+\subsubsection{Route Determination} (needs to be rephrased? perhaps?)
 A user's geolocation tracking data includes latitude and longitude coordinates, timestamps of when the user was at given coordinates, and an accuracy score for each geolocation record.
-Rewind expects the geolocation data to be formatted as JSON (but is compatible with other location-based formats like GPX), particularly in the same format that Google Takeout generates for Location History.
-
-Rewind is implemented as a client-side only application and therefore does not transfer sensitive user data or store it; it does not have a server component for communication.
-The system is written with standard web technologies: HTML5, CSS, and JavaScript, in addition to various open source libraries and services.
-These libraries include the Google Maps API, determining routes between location points and retrieving Google Street View images of any given location; the StreetviewSequence.js library is also used in the process of generating Rewinds \cite{streetviewsequence}.
-The library takes in data in the form of a Google Route and composes a video sequence by stitching together Google Street View images from multiple points on the given route (Figure~\ref{fig:rewinds}).
-The CamanJS library \cite{caman} is used to manipulate the appearance of Google Street View images such as brightness, contrast, and saturation in order to better replicate the environmental conditions at a given time.
-More sophisticated image manipulation techniques were investigated \cite{laffont2014transient} but deemed to slow for Rewind's current real-time use.
-
+\textit{Rewind} expects JSON formatted data, and is also compatible with other location-based formats such as GPX.
 Rewind generates location points for the user, using smart filtering based on visit frequencies to decrease the data noise and diversify the locations shown to the user.
@@
 We then use the Haversine formula to calculate the individual distance between all given locations and the user's home, attaching the distance data to the location.
-% Finally, for the user study, Rewind generates the user's set of locations based on visit frequency: 5 from the least visited locations, 3 from the most visited locations, and 2 randomly selected locations.
 
-Once the location set is determined, photos are retrieved from Google Street View and manipulated for time of year and time of day.
-For each selected location, a Google Street View image is requested and the timestamp of when the user visited the location is used to determine how the image should be manipulated to appear as close as possible to what the user saw.
-For the time of year, adjustments are made to the image's saturation (Figure~\ref{fig:season}), and for the time of day (Figure~\ref{fig:timeofday}), adjustments are made to the image's brightness.
-For example, if the location's timestamp denotes the summer, the image will be adjusted to have higher saturation to account for the vivid colors during that season.
-In the same vein, an image taken at noon will be adjusted to have higher brightness whereas an image taken at a time closer to sunset will be adjusted for lower brightness to account for the amount of sunlight captured.
-Taking this into account, Rewind evaluates the saturation and brightness of each Google Street View image as it is retrieved, and makes adjustments to mimic the actual date and time of user's visit.
-Weather adjustments for images are made at the same time as date and time adjustments.
-Using data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations, Rewind checks for factors that would require image adjustments.
-In our study, we adjusted only images from [anonymized: our state/province] and only for precipitation.
-However, it would not be difficult to do this for images from any location with a larger weather database, and other types of weather can be used to make adjustments besides precipitation.
-For our study, if there was precipitation at the time the user visited the location, the contrast is lowered to imitate cloudiness or rain.
-After these adjustments, the location set is now ready to be shown to the user.
+\subsubsection{Hyperlapse Creation} 
+The composition of one video recollection is consist of two hundred Google Street View images snapshotting the chosen route.
+Before stitching the imageries together using StreetviewSequence Javascript Library \cite{streetviewsequence}, we performed pixel-wise adjustment on each Google Street View image to reveal time-specific cues including diurnal cycle, seasonal characteristics and meteorological attributes.
+To achieve this, we used naive HVS and RGB color space mapping for sky and plantation approximation and modification.
+Similar to the method described by ****Irfanullah (An efficient approach for sky detection)*****, we generalized color mapping streamlines to estimate sky, cloud and plantation.
+(need to expand on this and mention Caman) For meteorological conditions in particular, we prepared a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations for weather lookup.
+(need to expand too)
+-- to be continued
 
@@
 Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep.
-Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others.
+Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% fare of trips in which the participant is traveling with others.
 The data shows clearly that a Rewind is considered much more valuable if the trip it depicts was taken with company.

### 2016-08-25 paper/uist_2016/paper.tex
restoring unintended changes..

@@
 
-Preserving memorable moments is a fundamental part of human nature.
+Capturing a memory is a fundamental part of human nature.
 Not long ago, we chronicled significant moments in our lives through journals and diaries, to be filled at the end of the day.
@@
 Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep.
-Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% fare of trips in which the participant is traveling with others.
+Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others.
 The data shows clearly that a Rewind is considered much more valuable if the trip it depicts was taken with company.

### 2016-08-28 paper/uist_2016/paper.tex
more on system

@@
 \subsubsection{Hyperlapse Creation} 
-The composition of one video recollection is consist of two hundred Google Street View images snapshotting the chosen route.
-Before stitching the imageries together using StreetviewSequence Javascript Library \cite{streetviewsequence}, we performed pixel-wise adjustment on each Google Street View image to reveal time-specific cues including diurnal cycle, seasonal characteristics and meteorological attributes.
-To achieve this, we used naive HVS and RGB color space mapping for sky and plantation approximation and modification.
-Similar to the method described by ****Irfanullah (An efficient approach for sky detection)*****, we generalized color mapping streamlines to estimate sky, cloud and plantation.
-(need to expand on this and mention Caman) For meteorological conditions in particular, we prepared a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations for weather lookup.
-(need to expand too)
--- to be continued
+Each video recollection created by \textit{Rewind} is composed of two hundred Google Street View image sequences of the chosen route being stitched together using StreetViewSequence \cite{streetviewsequence}.
+Each incoming Google Street View image has been retrieved with the same dimensions (640 px by 640 px) with similar spatial orientation (FOV, pitch and heading values).
+
+Since environmental characteristics, such as meterorological attributes, of images retrieved using Google Street View Static Image API are not directly exposed nor adjustable, it is hard to conclude if the retrieved images would correctly reflect the timely and ambient properties at the time when the user undertook the path.
+To compensate for this, we performed pixel-wise adjustment on each Google Street View image to better convey time-specific messages including times of the day, seasonal variances and meterological specifics.
+Previous work done by \cite{laffont2014transient,shih2013data} have successfully reconstructed images with varying diurnal and seasonal cycles, yet it would be computationally expensive to replicate the proposed techniques on large sets of image data on the browser.
+Considering each \textit{Rewind} hyperlapse would contain two hundred frames, and lifeloggers would probably not be willing to spare more than one minute waiting for the composition of the video, it would be challenging to incoporate a large training dataset into the rendering pipeline.
+Due to the stringent timing constraint, we have instead adopted a more generic and naive approach of color space mapping for object segmentation and color adjustment, with the facilitation of CamanJS \cite{caman}.
+
+As the Google Street view images of a given route have been retreived with the same dimensional parameters and optical orientation, locational and spatial information of each image is largely similar (ex.
+the sky normally resides in the upper 1/3 of the image, but could occupy more than 1/2 of the image at times).
+We have thus been able to approximate sky and ground regions by generalizing the observed geographical information of the incoming images.
+We first converted each pixel from RGB represenation into HSV color space.
+For seasonal changes, we estimated a range of HSV values that could be used for plantation classification, adjusted those HSV values that fell within the range for desired seasonal effects, and converted HSV back to RGB color space for Javascript canvas painting (Figure~\ref{fig:season}).
+Similarly, for creating nightly effects such as sunset and evening scenes, we adjusted sky colors and applied linear brightness and saturation filters locally and globally (Figure~\ref{fig:timeofday}).
+As an example of creating the evening scene, we segemented the incoming Google Street View image into three major areas: 1.
+Approximated sky region 2.
+Non-sky region in the approximated sky region 3.
+Approximated Ground region.
+We then down-scaled the RGB values of each pixel based on the region it is classified in.
+
+For meteorological conditions, we prepared a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations for weather lookup (currently only available for images from [anonymized: our state/province]).
+We adjusted sky colors using a similar technique mentioned previously for overcast, rainy and snowy sky.
+For determined rainy and snowy periods of time, we overlayed an animated precipitation layer accompanied by corresponding audio effects to emulate the environment partially exposed by the weather data.
 

### 2016-08-30 paper/uist_2016/paper.tex
grammatical changes; added some references; updated pictures; tbc

--- 2016-08-25 paper/uist_2016/paper.tex
@@
 \textit{Rewind} recreats the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers.
-Differing from previously studied hyperlapse creation techniques by ***(Neel Joshi's and Johannes Kopf's work from Microsoft)****, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight.
+Differing from previously studied hyperlapse creation techniques by \cite{kopf2014firstperson, joshi2015realtime}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight.
 \textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images.
-The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimentional temporal cues.
-\textit{Rewind} is a client-side only application implemented with Google Maps API and third-party Javascript libraries, and therefore does not transfer sensitive user data nor store it.
+The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues.
+\textit{Rewind} is a client-side only application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it.
 
@@
 \subsubsection{Hyperlapse Creation} 
-The composition of one video recollection is consist of two hundred Google Street View images snapshotting the chosen route.
-Before stitching the imageries together using StreetviewSequence Javascript Library \cite{streetviewsequence}, we performed pixel-wise adjustment on each Google Street View image to reveal time-specific cues including diurnal cycle, seasonal characteristics and meteorological attributes.
-To achieve this, we used naive HVS and RGB color space mapping for sky and plantation approximation and modification.
-Similar to the method described by ****Irfanullah (An efficient approach for sky detection)*****, we generalized color mapping streamlines to estimate sky, cloud and plantation.
-(need to expand on this and mention Caman) For meteorological conditions in particular, we prepared a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations for weather lookup.
-(need to expand too)
--- to be continued
+Each video recollection created by \textit{Rewind} is composed of two hundred Google Street View image sequences of the chosen route being stitched together using StreetViewSequence \cite{streetviewsequence}.
+Each incoming Google Street View image has been retrieved with the same dimensions (640 px by 640 px) with similar spatial orientation (FOV, pitch and heading values).
+
+Since environmental characteristics, such as meteorological attributes, of images retrieved using Google Street View Static Image API are not directly exposed nor adjustable, it is hard to conclude if the retrieved images would correctly reflect the timely and ambient properties at the time when the user undertook the path.
+To compensate for this, pixel-wise adjustment was applied on each Google Street View image to better convey time-specific messages including times of the day, seasonal variances and meteorological specifics.
+Previous work done by \cite{laffont2014transient,shih2013data} have successfully reconstructed images with varying diurnal and seasonal cycles, yet it would be computationally expensive to replicate the proposed techniques on large sets of image data on the browser.
+Considering each \textit{Rewind} hyperlapse would contain two hundred frames, and lifeloggers would probably not be willing to spare more than one minute waiting for the composition of the video, it would be challenging to incorporate a large training dataset into the rendering pipeline.
+Due to the stringent timing constraint, we have instead adopted a more generic and naive approach of color space mapping for object segmentation and color adjustment, with the facilitation of CamanJS \cite{caman}.
+
+As the Google Street view images of a given route have been retrieved with the same dimensional parameters and optical orientation, locational and spatial information of each image is largely similar (ex.
+the sky normally resides in the upper 1/3 of the image, but could occupy more than 1/2 of the image at times).
+Thus sky and ground regions could be approximated by generalizing the observed geographical information of the incoming images.
+Each pixel was first converted from RGB representation into HSV color space.
+For seasonal changes, a range of HSV values was estimated for plantation classification and those HSV values that fell within the range were adjusted for desired seasonal effects.
+Each HSV value was then converted back to RGB color space for JavaScript canvas painting (Figure~\ref{fig:season}).
+Similarly, for creating nightly effects such as sunset and evening scenes, sky colors were modified using the same technique.
+In addition, two linear brightness and saturation filters were applied locally and globally (Figure~\ref{fig:timeofday}).
+As an example of creating the evening scene, the incoming Google Street View images were segmented into three major areas: 1.
+Approximated sky region 2.
+Non-sky region in the approximated sky region 3.
+Approximated Ground region.
+RGB values of each pixel were down-scaled based on the region the pixel is classified in.
+
+For meteorological conditions, a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations was used for weather lookup (currently only available for images from [anonymized: our state/province]).
+Sky colors was adjusted again using the technique mentioned previously for overcast, rainy and snowy sky.
+For determined rainy and snowy periods of time, an animated precipitation layer was overlaid on the hyperlapse and accompanied by corresponding audio effects to emulate the weather conditions exposed by the data (Figure~\ref{fig:weather}).
 
@@
    \centering
-     \includegraphics[width=1\linewidth]{Rewind-time_of_day}
-     \caption{Brightness of Rewind images are manipulated in order to mimic the time of day that the trip took place.}
+     \includegraphics[width=1\linewidth]{Rewind-seasons2}
+     \caption{Plantation is classified using HSV color space, and the HSV values were adjusted to reflect seasonal changes}
+     \label{fig:season}
+\end{figure}
+
+\begin{figure}
+   \centering
+     \includegraphics[width=1\linewidth]{Rewind-time_of_day2}
+     \caption{Per-pixel change is applied based on classified region}
      \label{fig:timeofday}
@@
    \centering
-     \includegraphics[width=1\linewidth]{Rewind-seasons}
-     \caption{Saturation of Rewind images are manipulated in order to mimic the season that the trip took place.}
-     \label{fig:season}
+     \includegraphics[width=1\linewidth]{Rewind-weather}
+     \caption{Meterological attributes are depicted using JavaScript canvas painting and animation}
+     \label{fig:weather}
 \end{figure}

### 2016-09-10 paper/uist_2016/paper.tex
added three more references in related work

@@
 By picking a start and end location from a particular trip and generating a Rewind between these points, the user relives their memories in a continuous manner.
+Similarly in his famous seminal paper \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through``associative trails'', giving mankind the ability of``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''.
+Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one’s sensory experiences about past visits.
 
@@
 
+Another project by de Silva and Aizawa has also relied on geolocation data to provide a visual examination of interested traveling routes by linking geo-tagging metadata with online imageries, specifically Google Street View images \cite{deSilva:2009:RMT:1631272.1631414}.
+The authors proposed a sketch-based interface that would perform spatial and temporal queries on line drawings specified by the users.
+Rewind resembles this interactive system, in a way that the reconstructed sceneries are of a careful mapping results from GPS data and Google Street View images.
+However, Rewind differs in that the mapping is finalized with GPS data provided by lifeloggers tracked using smartphones.
+This means that Rewind serves more of a getaway for recalling episodic memory rather than reviewing a potential travelling itinerary, aiming to provide a mechanism for reminiscence and sharing of past experience while exploring lifeloggers' behavioral patterns.
+Moreover, the reconstruction techniques used in Rewind would differentiate the same retrieved image with various temporal cues such as changes in seasons; yet the immediate results from the temporal queries suggested by de Silva and Aizawa have not been fully revealed.
+
 Other research has used location history not to create a new interface for the user, but for other applications.
@@
 Furthermore, GPS tracking is noted as a good method for collecting data about movement of each person.
-A further exploration of this project was what participants' perceptions were while moving.
-The data from this study shows each person's location data can be used as a unique fingerprint.
+Using geotagged images from Flickr, Becker et al's work has shown that movement trajactories in metropolian areas tend to converge at Points of Interests(POIs) \cite{Becker2015}.
+As noted, a further exploration of these projects could be investigating what participants' perceptions were while moving.
+The data from these studies show each person's location data can be used as a unique fingerprint.
 This supports the idea that location data can be used to help people recreate their individual travel experiences, for purposes of reminiscing and even sharing.
@@
 \textit{Rewind} recreats the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers.
-Differing from previously studied hyperlapse creation techniques by \cite{kopf2014firstperson, joshi2015realtime}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight.
+Differing from previously studied hyperlapse creation techniques by Kopft et al.
+and Joshi et al \cite{opf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight.
 \textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images.

### 2016-09-12 paper/uist_2016/paper.tex
Rewrite user study section

@@
 \subsection{Research Questions}
-Rewind enables us to ask questions that have not been possible to ask before, due to the scarcity of comprehensive data about where someone has been.
-We performed a within-subjects comparison of Rewind and static photography that are not sequenced together.
-By showing a user both types of digital memories, we can begin to understand what are the features that make the Rewinds more realistic are more believable for different trips.
+The Rewind system enables us to ask questions about people's attitudes and behaviors surrounding digital memories that were not possible to answer before due to the scarcity of comprehensive data about where someone has been.
+To start to understand what makes a digital memory meaningful to a person, we performed a within-subjects comparison of Rewinds and static photography.
+By comparing Rewinds to today's most prevalent form of digital memory media, we can begin to distill what features make a Rewind meaningful and representative as a memory of a trip.
 
-There are some specific research questions we investigate about people's behaviors surrounding digital memories.
+Our research questions examine the effectiveness of Rewinds through three aspects: memorability, believability, and desirability.
 
-1) Do certain features of a Rewind make it more memorable? Are the participants able to recall a particular location or route most often in Rewinds with particular features?
+1) Memorability: Do certain features of a location or trip depicted in a digital memory make the memory more recallable?
 
-2) Which Rewinds do users wish to save, and which ones would you like to share?
-For example, frequent trips close to home, long one-time journeys, or just the destinations and landmarks that the travel takes them to?
-Are these the Rewinds that are the most familiar, or ones that are unique and are not instantly recognizable?
+2) Believability:  Is the digital memory accurate to the participant's memory? What features make a digital memory accurate or inaccurate?
 
-3) Do people who frequently use a GPS have different memories than those who don't?
-What about frequent travelers or people who are traveling with companions?
-Again, this is something that has previously been difficult to study without location histories.
+3) Desirability: Which digital memories do users wish to save? Do certain features make a digital memory more likely to be kept?
+
+\subsection{Participants}
+Participants for the user study were recruited online through local Craigslist classifieds and Reddit communities for the Providence area.
+Offline, ads were posted in cafes and other small businesses in the the city.
+Of the 21 total participants, 13 identified as men and 8 identified as women.
+Participants ranged from ages 20 to 50.
+Most participants were local residents, with occupations including librarian, medical researcher, office worker, IT consultant, musician, and comedian.
+A fifth of the participants were undergraduate or graduate students.
 
 \subsection{Procedure}
-A user study following a two-week tracking period with 21 participants from the [anonymized] area investigated the influence of Rewinds on recollection, and evaluated their memorability and believability.
+Participants underwent a two-week tracking period followed by a user study which investigated the memorability, believability, and desirability of the Rewinds produced from the two weeks of location data.
 
-Participants for the study were recruited online through Craigslist classifieds and local Reddit communities for the [anonymized] area.
-Offline, ads were posted in cafes and other small businesses in the the city.
-Of the 21 total participants, 13 identified as men and 8 identified as women.
-Participants ranged from ages under 20 to over 50.
-Most participants were local residents, with occupations varying from librarian to medical researcher to office worker to musician.
-A fifth of the participants were undergraduate or graduate students.
-
-Study participation included a location-tracking setup session, at least twelve days of tracking, and a follow-up user study.
-At the location-tracking setup, participants were asked to activate geolocation tracking on their mobile phones.
+Study participation included a setup session for location tracking, at least twelve days of tracking, and a follow-up user study.
+At the location tracking setup, participants were asked to activate geolocation tracking on their mobile phones.
 Participants with Android devices used Google's built-in location reporting services for tracking.
-iPhone users downloaded Google+ to use the same service.
-Participants with devices incompatible with Google's location reporting services were provided with an older Android device that used the app GPSLogger\footnote{\url{https://play.google.com/store/apps/details?id=com.mendhak.gpslogger&hl=en}} for tracking.
+iPhone users downloaded the Google+ app to use the same service.
+Participants with devices incompatible with Google's location reporting services were provided with an older Android device that used the GPSLogger\footnote{\url{https://play.google.com/store/apps/details?id=com.mendhak.gpslogger&hl=en}} app for tracking.
 Participants were asked to keep their phone charged and on their person as much as possible for approximately two weeks, until they could come in for a final interview with the experimenters.
 
-At the in-person interview, participants were shown a series of images and accompanying Rewinds that represented the trips they took during the tracking period.
-The user's GPS data was trimmed so that images and Rewinds are created from only the past fourteen days at most.
-Of the ten image-Rewind pairs that were shown, five were of trips taken infrequently, three were of trips taken most frequently, and the remaining two were random.
+At the in-person interview, participants were shown a series of photos and accompanying Rewinds that represented the trips they took during the tracking period.
+The participant's geolocation data was trimmed to ensure that photos and Rewind videos were generated from data gathered no earlier than the past two weeks.
+Participants were shown ten photo-Rewind pairs.
+Of the ten pairs, five showed trips taken infrequently, three showed trips taken most frequently, and the remaining two were random.
 
-At the beginning of the study, participants were asked for their gender, whether they considered themselves a frequent traveler, and whether they tended to use GPS in places they were already familiar with.
-Participants who used GPS in familiar locations were considered regular GPS users, and participants who didn't were considered non-regular GPS users.
+At the beginning of the study, participants were asked to identify their gender, whether they considered themselves a frequent traveler, and whether they tended to use GPS in places they were already familiar with.
+Participants who used GPS in familiar locations were considered regular GPS users, and participants who did not were considered non-regular GPS users.
 
-For each image-Rewind pair, the participant was first shown an image of a location from their GPS data and asked to answer questions about it.
-Then they were shown a Rewind of the trip during which the image showed up, and the participant was asked to answer questions about the Rewind.
-While the Rewind was playing, participants could hover over the Rewind panel and scrub backwards and forwards horizontally through the images that composed the video.
+For each photo-Rewind pair, the participant was first shown a photo of one of the locations found in their GPS data. The participant was asked to answer the following questions about the photo:
+
+Do you remember this location? If so, can you name the street? Can you name what is around the location, such as buildings, landmarks, or other places?
+
+Would you want to keep this photo? Why or why not? Were you traveling alone?
+
+If you remember the location, is the photo accurate to your memory? Why or why not? What was different?
+
+The participant was then shown a Rewind of the trip that they were on when the previous location was encountered.
+While the Rewind was playing, the participant could hover over the Rewind panel and scrub backwards and forwards horizontally through the images that composed the video.
 This allowed participants to ``walk through'' their memory at their own pace.
+The participant was asked the following questions while the Rewind played:
 
-For both the image and the Rewind, the participants were asked questions related to memory recall.
-They were first asked whether they remember the locations.
-If they could, they were then asked to discuss specifics of the location: Participants were asked whether they could name the streets and whether they could name buildings, landmarks, or places around the locations.
-If the participant was looking at a Rewind, they were also asked whether they remembered the exact trip.
-To evaluate memorability of the photo or Rewind, participants were asked whether they would keep the image or video, and why or why not.
-Then they were asked whether they traveled alone or with a companion.
-Lastly, participants were asked questions related to the believability of the digital memory: was the photo or video accurate to their memory?
-Why or why not?
+Do you remember these locations? Do you remember this trip? Can  you name some of the streets? Can you name what is around these locations, such as buildings, landmarks, or other places?
 
-In addition to asking questions, we observed the users as they examined the Rewinds of their trips, since they could passively watch the Rewind or actively scrub through the individual images that made up the video.
-The user study took between 30 minutes to an hour for each participant, and participants were compensated \$30 for their time at the end of the study.
+Would you want to keep this video? Why or why not? Were you traveling alone?
+
+If you remember these locations, is the video accurate to your memory? Why or why not? What was different?
+
+Questions about the photos and Rewinds tested their memorability, believability, and desirability as memory media.
+
+In addition to asking questions, we observed the users as they examined their generated Rewinds, since they could passively watch the Rewind or actively scrub through the individual images that made up the Rewind.
+
+The user study took between 30 minutes to an hour for each participant, and participants were compensated \$30 cash for their time at the end of the study.
 
 Data from three participants was not included in the results of this study.
-Two of the aforementioned participants were not able to do the user study.
-One of those participant's data points consisted of only one location.
-The participant used a mobile device provided by the study, so it's likely that they did not carry the device on their person.
-The other participant did not complete the user study due to health and scheduling reasons.
-The last participant only collected three days of data because they had their phone replaced during the tracking period and did not reactivate Google's location reporting services on the new device.
-This participant completed the user study, but we did not include the data gathered during this participant's session in the results.
+One of the participants' data points consisted of only one location.
+The participant used a mobile device provided by the study, so it is likely that they did not carry the device on their person.
+Another participant did not complete the in-person interview portion of the user study due to health and scheduling reasons.
+The last participant only collected three days of data because they had their phone replaced during the tracking period, and did not reactivate Google's location reporting services on their new device.
+This participant completed the in-person interview portion of the user study, but we did not include the data gathered during this participant's session in the results.
 
 \section{Findings}
-The findings of our user study center on the participants' relationship to the Rewinds created from their location data.
+The findings of our user study center on the participants' relationship to the Rewinds generated from their location data.
 We focus on the participants' judgments of their Rewinds' memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds.
-We also discuss how the participants interacted with and reacted to their Rewinds.
-The results use data from user studies conducted with 12 men and 6 women.
-6 of 12 participants identified themselves as frequent travelers.
-Additionally, 6 of 12 participants were regular GPS users.
+We also discuss the participants' interactions with and reactions to their Rewinds.
+The results use data from the user studies conducted with 12 men and 6 women.
+Half of the participants identified themselves as frequent travelers.
+Additionally, half of the participants were regular GPS users, or people who used GPS even in locations already familiar to them.
 

### 2016-09-12 paper/uist_2016/paper.tex
fix some typos

--- 2016-09-10 paper/uist_2016/paper.tex
@@
 People and conversations, which are what we think about often, can't be shown in Rewinds without some additional recording device.
-Therefore, while Rewind does not recreate the exact memory, it's more of a proxy for what environment where the memory occurs.
+Therefore, while Rewind does not recreate the exact memory, it's a proxy for what environment where the memory occurs.
 
@@
 This can be replicated through a number of styles: the pitter-patter of footsteps or sound of driving through the streets (mode of transportation can be detected purely from geolocation data \cite{zheng2008learning}), the whistle of the winds or thunderstorms at night, and even sounds based on geographical features like when the user was near water or by a outdoor market.
-van Djick explains, ``One memory rarely encompasses all sensory modes, because we tend to remember by selecting particular ones.
+van Dijck explains, ``One memory rarely encompasses all sensory modes, because we tend to remember by selecting particular ones.
 For instance, we may recall a mood, locale or era through a particular smell (such as the smell of apple pie in the oven triggering the image of your mother's kitchen on Saturday afternoons), or we may remember a person by his nasal voice or twinkling eyes'' \cite{van2007mediated} (pg.

### 2016-09-12 paper/uist_2016/paper.tex
minor writing edits

@@
 When they were shown the Rewind associated with that photo, nearly all participants knew the location captured---97\%.
-This result shows the impact of Rewind on memorability, as the addition images before and after the static photograph greatly impacts whether a past location is familiar to a user.
+This result shows the impact of Rewind on memorability, as the addition images before and after the static photograph changes whether a past location is familiar to a user.
 
@@
 This confirms Leshed et al.'s findings that GPS users are typically disengaged with their environment \cite{leshed2008car}.
-We found that while GPS users had lower remembrance overall, the group experienced a huge jump between location remembrance and trip remembrance, suggesting that Rewinds may actually engage GPS users' memories.
+We found that while GPS users had lower remembrance overall, the group experienced a jump between location remembrance and trip remembrance, suggesting that Rewinds may actually engage GPS users' memories.
 

### 2016-09-12 paper/uist_2016/paper.tex
memorability findings

--- 2016-09-12 paper/uist_2016/paper.tex
@@
 
-Do you remember these locations? Do you remember this trip? Can  you name some of the streets? Can you name what is around these locations, such as buildings, landmarks, or other places?
+Do you remember these locations? Do you remember this particular trip? Can  you name some of the streets? Can you name what is around these locations, such as buildings, landmarks, or other places?
 
@@
 Half of the participants identified themselves as frequent travelers.
-Additionally, half of the participants were regular GPS users, or people who used GPS even in locations already familiar to them.
+Additionally, half of the participants were regular GPS users, that is people who used GPS even in locations already familiar to them.
 
@@
 Rewinds are meant to engage a person's memory.
-To see if the Rewind system selected and portrayed memorable locations and trips, we investigated whether participants were able to remember the location shown in a photo or recall the trip portrayed by a Rewind.
-Location memorability is determined by whether or not the participant remembers the location depicted in a photo.
-Trip memorability is determined by whether or not the participant remembers and can distinguish the exact trip portrayed in a Rewind.
-In this section we will look at differences in location and trip remembrance between participants who are regular GPS users and participants who do not use GPS regularly, and examine the effect of location distance and visit frequency on memorability.
+To find out more about what features make a digital memory memorable, we examined participant responses to whether or not they were able to remember the location shown in a photo or recall the trip portrayed by a Rewind.
+Photo memorability is determined by whether or not the participant remembered the location depicted in a photo.
+Because a Rewind contains many locations, it would be unfair to consider the memorability of Rewind based on whether participant remembers any locations in the Rewind.
+So, Rewind memorability is determined by whether or not the participant remembered and could distinguish the particular trip portrayed in a Rewind.
+In this section, we will look at differences in photo and Rewind memorability based on the variables of distance from the participant's home, visit frequency, presence of travel companions, regular GPS usage, and whether the participant considered themselves a frequent traveler.
 
-\subsubsection{Rewinds and Photos}
+\subsubsection{Rewinds versus Photos}
 When participants were shown a street side photo from their location history, they were asked whether they recognized the location in the photo.
 In 50\% of cases, participants said they did.
-When they were shown the Rewind associated with that photo, nearly all participants knew the location captured---97\%.
-This result shows the impact of Rewind on memorability, as the addition images before and after the static photograph greatly impacts whether a past location is familiar to a user.
+When they were shown the Rewind associated with that photo, nearly every case had recognizable locations---97\%.
+This result is expected since Rewinds contain more location information than static photos, so if participants do not recognize some depicted locations, they still have many other chances to pick out locations they remember.
+Rewind memorability as calculated by whether participants could identify the particular trip they were on from watching the Rewind was 54\%.
+However, there were cases where the participant would only remember the photo after seeing its accompanying Rewind, which provided a context.
+More than one participant exclaimed after watching a Rewind, ``I recognize the photo now!''
 
-\subsubsection{GPS Usage}
-Our findings show that participants who are not regular GPS users remember locations and trips more often than participants who are regular GPS users (Figure~\ref{fig:gpsmemory}).
-When asked whether they remember the location or trip being shown in a photo or Rewind, participants who do not use GPS regularly gave a positive answer 58\% of the time for location remembrance and 56\% of the time for trip remembrance.
-Regular GPS users remembered locations 33\% of the time and trips 47\% of the time.
-The data shows that participants who are regular GPS users did not remember the locations they visited or trips they took as often as participants who are not regular GPS users.
-Since regular GPS users are frequently directed step-by-step on how to navigate their environment, they may not pay as much attention to their surroundings.
-This diminished locational awareness could be the reason why regular GPS users had a lower remembrance rate for locations and trips.
-From these percentages, we also see that regular GPS users remember trips more often than they remember locations, while there is little difference between the two for participants who do not use GPS regularly.
+\subsubsection{Distance}
+The distance away from the participant’s home had differing effects on photo memorability and Rewind memorability (Figure~\ref{fig:distancememory}).
+Distances ranged from 0 to 206,155 meters.
+For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 corresponded to a range of 10--100 meters; Group 2 corresponded to a range of 100--1,000 meters; Group 3 corresponded to a range of 1,000--10,000 meters; Group 4 corresponded to a range of 10,000--100,000 meters and Group 5 corresponded to a range of 100,000--1,000,000 meters from the participant's home location.
+
+Photo memorability and distance had a clear linear relationship.
+As the distance increased, photo memorability decreased, suggesting that locations further away from home were less likely to be remembered.
+Remembrance was 100\% for Distance Group 0, or home.
+One participant recognized a photo because her ``husband's car is in the driveway.'' Remembrance dropped to 74\% for Distance Group 1, then down to 10\% for Distance Group 5, which represented the locations furthest away from home.
+These percentages are statistically significant, with a p-value of 0.0028.
+
+There was no statistical significance for Rewind remembrance.
+Our data does show, however, that Rewind remembrance was largely the same for most distance groups, except for distances that were close to home.
+While remembrance for almost all distance groups was on average near 60\%, remembrance for Rewinds in Distance Group 1 was 25\%.
+This data suggests that participants often did not remember or could not distinguish the exact trips occurring in locations close to their home, where most trips happen.
 
@@
 	\centering
-     \includegraphics[width=1\linewidth]{GPS_remembrance_2}
-     \caption{Regular GPS users remembered locations 33\% of the time and trips 47\%, compared to 58\% and 56\% for non-regular GPS users.}
-     \label{fig:gpsmemory}
+	\includegraphics[width=1\linewidth]{distance}
+	\caption{Location remembrance is inversely correlated to its distance from a participant's home.}
+	\label{fig:distancememory}
 \end{figure}
@@
 
-\subsubsection{Distance}
-The distance away from the participant’s home had differing effects on location memorability and trip memorability (Figure~\ref{fig:distancememory}).
-Distances ranged from 0 to 206,155 meters.
-For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from user's home location; Group 1 corresponded to a range of 10--100 meters; Group 2 corresponded to a range of 100--1,000 meters; Group 3 corresponded to a range of 1,000--10,000 meters; Group 4 corresponded to a range of 10,000--100,000 meters and Group 5 corresponded to a range of 100,000--1,000,000 meters from user's home location.
-As the distance increased, location memorability decreased, suggesting that locations further away from home were less likely to be remembered.
-Location remembrance dropped from 100\% for Distance Group 0, or home, to 74\% for Distance Group 1 down to 10\% for Distance Group 5, which represented the locations furthest away from home.
-For trips, remembrance was largely the same for most distance groups, except for distances that were very close to home and distances that were very far, but not the furthest, from home.
-Trip remembrance was at 60\% for Distance Group 0, then dipped momentarily to 25\% in Distance Group 1 before increasing back up to 60\% for Distance Group 2, 3, and 5.
-Only Distance Group 4 wavered with a trip remembrance rate of 48\%.
-This data suggests that participants often did not remember or could not distinguish the exact trips occurring in locations very close to home, where most trips happen, nor could they distinguish the exact trips that happened very far, but not especially far, from home.
-
-\begin{figure}
-   \centering
-     \includegraphics[width=1\linewidth]{distance}
-     \caption{Location remembrance is inversely correlated to its distance from a participant's home.}
-     \label{fig:distancememory}
-\end{figure}
-
 \subsubsection{Travel Companions}
@@
 Participants were not able to remember the exact trip of 33\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 89\% of Rewinds that were taken with company.
+
+\subsubsection{GPS Usage}
+Our findings show that participants who are not regular GPS users remember locations and trips more often than participants who are regular GPS users (Figure~\ref{fig:gpsmemory}).
+When asked whether they remember the location or trip being shown in a photo or Rewind, participants who do not use GPS regularly gave a positive answer 58\% of the time for location remembrance and 56\% of the time for trip remembrance.
+Regular GPS users remembered locations 33\% of the time and trips 47\% of the time.
+The data shows that participants who are regular GPS users did not remember the locations they visited or trips they took as often as participants who are not regular GPS users.
+Since regular GPS users are frequently directed step-by-step on how to navigate their environment, they may not pay as much attention to their surroundings.
+This diminished locational awareness could be the reason why regular GPS users had a lower remembrance rate for locations and trips.
+From these percentages, we also see that regular GPS users remember trips more often than they remember locations, while there is little difference between the two for participants who do not use GPS regularly.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{GPS_remembrance_2}
+	\caption{Regular GPS users remembered locations 33\% of the time and trips 47\%, compared to 58\% and 56\% for non-regular GPS users.}
+	\label{fig:gpsmemory}
+\end{figure}
+
+\subsubsection{Frequent Travelers}
+Our findings show that trip remembrance is influenced by the presence of travel companions.
+As one might imagine, trips that were taken with other people were much more memorable than trips taken alone.
+Participants were not able to remember the exact trip of 33\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 89\% of Rewinds that were taken with company.
+
+\subsubsection{Other Variables}
 

### 2016-09-14 paper/uist_2016/paper.tex
shorten a related work section, and
change some instances of "GPS" to "geolocation"

@@
 The authors proposed a sketch-based interface that would perform spatial and temporal queries on line drawings specified by the users.
-Rewind resembles this interactive system, in a way that the reconstructed sceneries are of a careful mapping results from GPS data and Google Street View images.
-However, Rewind differs in that the mapping is finalized with GPS data provided by lifeloggers tracked using smartphones.
+Rewind resembles this interactive system, in a way that the reconstructed sceneries are of a careful mapping results from geolocation data and Google Street View images.
+However, Rewind differs in that the mapping is finalized with geolocation data provided by lifeloggers tracked using smartphones.
 This means that Rewind serves more of a getaway for recalling episodic memory rather than reviewing a potential travelling itinerary, aiming to provide a mechanism for reminiscence and sharing of past experience while exploring lifeloggers' behavioral patterns.
@@
 These personal tracks are created using data from time and location tracking for each trip by each individual.
-The researchers focused on comparing the different visualization techniques used to portray the data.
-A two-month study involved twenty participants wearing GPS devices, but as the paper was published in 2010, they did not use smartphone GPS data.
-Each participant wore a device, and the paper suggests that doing so helped them feel in charge of the data collection.
-Furthermore, GPS tracking is noted as a good method for collecting data about movement of each person.
-Using geotagged images from Flickr, Becker et al's work has shown that movement trajactories in metropolian areas tend to converge at Points of Interests(POIs) \cite{Becker2015}.
-As noted, a further exploration of these projects could be investigating what participants' perceptions were while moving.
+The researchers focused on comparing the different visualization techniques used to portray data from a two-month study involved twenty participants wearing GPS devices.
+Using geotagged images from Flickr, Becker et al.'s work has shown that movement trajactories in metropolian areas tend to converge at Points of Interests(POIs) \cite{Becker2015}.
 The data from these studies show each person's location data can be used as a unique fingerprint.
@@
 
-Further work in GPS user behavior has been done by Leshed et al.
+Further work in location-based user behavior has been done by Leshed et al.
 to see how users interpret and interact with spaces differently when using in-car GPS navigation \cite{leshed2008car}.
@@
 \section{The Rewind System}
-\textit{Rewind} recreats the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers.
+\textit{Rewind} recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers.
 Differing from previously studied hyperlapse creation techniques by Kopft et al.
 and Joshi et al \cite{opf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight.
-\textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images.
+\textit{Rewind} is a web interface that receives lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images.
 The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues.
@@
 
-For each photo-Rewind pair, the participant was first shown a photo of one of the locations found in their GPS data. The participant was asked to answer the following questions about the photo:
+For each photo-Rewind pair, the participant was first shown a photo of one of the locations found in their geolocation data.
+The participant was asked to answer the following questions about the photo:
 

### 2016-09-14 paper/uist_2016/paper.tex
added one flowchart; changed abstract

--- 2016-09-12 paper/uist_2016/paper.tex
@@
 \begin{abstract}
-The Rewind system automatically recreates a digital memory of a past trip.
-It takes historical geolocation data and generates a stitched-together video made of streetside images from where a user has been.
-The images are manipulated based on the weather, time of day, and season to look like what the user may have seen when they were there.
-Users can go back and forth in time by scrubbing their pointer left or right over the video.
-Together, the composed Rewinds offer users a window into past travels.
-A user study of people collecting location data over two weeks reveals that users can remember the location from a photograph about half of the time, but when shown a Rewind, they can nearly always remember where they traveled.
-Furthermore, GPS users are less likely to remember the specifics of a location, and people are particularly interested in preserving Rewinds of infrequent trips and trips taken with others.
-Rewind serves as an experiment of the extreme scenario where people can freely roam and experience the world, keeping their mobile devices in their pockets, and still generate believable representations that capture the past.
+GPS tracking using smartphones have been prevalent, providing self-trackers insights into their past visits and traveling patterns.
+Using tracked GPS information, we proposed \textit{Rewind}, a system that recreates sceneries of past trips to assist the recall of episodic memory.
+\textit{Rewind} takes historical GPS data from the users, maps out movement trajectories, and generates stitched-together videos to simulate the ways how past trips were taken.
+Users of \textit{Rewind} can change their moving directions by scrubbing their pointers over the video.
+Images used in \textit{Rewind} videos are post-processed to reveal weather and timely characteristics of the emulated environment.
+Our study of self-trackers using two-week of GPS data with \textit{Rewind} has revealed that non-GPS users tend to think \textit{Rewind} videos have accurately captured their past trips, and users are particularly interested in preserving \textit{Rewind} videos of infrequent trips and trips accompanied by others.
+Overall, \textit{Rewind} serves as an experiment of the extreme scenario where people can freely roam and experience the world, keeping their mobile devices in their pockets, and still generate believable representations that capture the past.
 \end{abstract}
@@
 \textit{Rewind} is a client-side only application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it.
+\ref{fig:flowchart}
+
+\begin{figure}
+     \includegraphics[width=1\linewidth]{Rewind-flowchart}
+     \caption{Plantation is classified using HSV color space, and the HSV values were adjusted to reflect seasonal changes}
+     \label{fig:flowchart}
+\end{figure}
 

### 2016-09-14 paper/uist_2016/paper.tex

@@
 \section{The Rewind System}
-\textit{Rewind} recreats the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers.
+\textit{Rewind} recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers.
 Differing from previously studied hyperlapse creation techniques by Kopft et al.

### 2016-09-16 paper/uist_2016/paper.tex
updated abstract, edited reference typo

@@
 \begin{abstract}
-GPS tracking using smartphones have been prevalent, providing self-trackers insights into their past visits and traveling patterns.
-Using tracked GPS information, we proposed \textit{Rewind}, a system that recreates sceneries of past trips to assist the recall of episodic memory.
-\textit{Rewind} takes historical GPS data from the users, maps out movement trajectories, and generates stitched-together videos to simulate the ways how past trips were taken.
-Users of \textit{Rewind} can change their moving directions by scrubbing their pointers over the video.
-Images used in \textit{Rewind} videos are post-processed to reveal weather and timely characteristics of the emulated environment.
-Our study of self-trackers using two-week of GPS data with \textit{Rewind} has revealed that non-GPS users tend to think \textit{Rewind} videos have accurately captured their past trips, and users are particularly interested in preserving \textit{Rewind} videos of infrequent trips and trips accompanied by others.
-Overall, \textit{Rewind} serves as an experiment of the extreme scenario where people can freely roam and experience the world, keeping their mobile devices in their pockets, and still generate believable representations that capture the past.
+We propose \textit{Rewind}, a system that assists in the recall of episodic memory by automatically recreating interactive sceneries of past trips.
+\textit{Rewind} uses historical geolocation data to generate egocentric videos of earlier experiences from Google's Street View images.
+Since the effectiveness of memory cues is determined by their level of integration with the target memory, the images are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience.
+Users can interactively go back and forth in time by scrubbing over the video.
+Together, the composed \textit{Rewind} videos offer users a window into past travels.
+We report the results of a user study with eighteen participants conducted to collect location data over two weeks.
+Trips taken in groups were more likely to be recalled using \textit{Rewind} videos than trips taken alone.
+\textit{Rewind} also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still generating believable representations that capture the past.
 \end{abstract}
@@
 Differing from previously studied hyperlapse creation techniques by Kopft et al.
-and Joshi et al \cite{opf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight.
+and Joshi et al \cite{Kopf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight.
 \textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images.
@@
 \textit{Rewind} is a client-side only application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it.
-\ref{fig:flowchart}
+%\ref{fig:flowchart}
 
-\begin{figure}
-     \includegraphics[width=1\linewidth]{Rewind-flowchart}
-     \caption{Plantation is classified using HSV color space, and the HSV values were adjusted to reflect seasonal changes}
-     \label{fig:flowchart}
-\end{figure}
+% \begin{figure}
+%      \includegraphics[width=1\linewidth]{Rewind-flowchart}
+%      \caption{Plantation is classified using HSV color space, and the HSV values were adjusted to reflect seasonal changes}
+%      \label{fig:flowchart}
+% \end{figure}
 

### 2016-09-17 paper/uist_2016/paper.tex
first draft of the table

@@
 \usepackage{url} % consider a nicer typeface (like Inconsolata) for URLs
+
+%added for table
+\usepackage{multirow}
+\usepackage[table,xcdraw]{xcolor}
+\usepackage{adjustbox}
+\usepackage{amsmath}
 
@@
 The integer that follows denotes the distance in meters between a user's home and the given location "as the crow flies."
+
+\begin{table*}[t]
+	\centering
+	\caption{My caption}
+	\begin{adjustbox}{width=1\textwidth}
+		\small
+		\label{my-label}
+		\begin{tabular}{ccccccccccccccccc}
+			\cline{4-17}
+			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{2}{c|}{GPS usage}                                                                                       & \multicolumn{2}{c|}{Traveller type}                                                                                  & \multicolumn{2}{c|}{Accompany}                                                                                               & \multicolumn{6}{c|}{Distance}                                                                                                                                                                                                                                                                                                            & \multicolumn{2}{c|}{Visit frequency}                                                                                 \\ \cline{4-17}
+			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{1}{c|}{GPS user}                             & \multicolumn{1}{c|}{non-GPS user}                        & \multicolumn{1}{c|}{Frequent}                             & \multicolumn{1}{c|}{Non-frequent}                        & \multicolumn{1}{c|}{Alone}                                     & \multicolumn{1}{c|}{Not alone}                              & \multicolumn{1}{c|}{0}                                & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{2}                               & \multicolumn{1}{c|}{3}                               & \multicolumn{1}{c|}{4}                               & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{Most}                                 & \multicolumn{1}{c|}{Least}                               \\ \hline
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}60}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}74}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}47}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81}          \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}66.67\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}42.02\%}     & \multicolumn{1}{c|}{50.83\%}                              & \multicolumn{1}{c|}{47.46\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}55.00\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.22\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}43.66\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}51.56\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}27.66\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.20\%}     \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{l|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$\\ p =0.0016\end{tabular}}  & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$\\ p = 0.3953\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 31.812$\\ p \textless0.0001\end{tabular}}  & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$\\ p = 0.0028\end{tabular}}                                                                                                                                                                                                                   & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$\\ p = 0.0001\end{tabular}} \\ \cline{2-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{58}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{57}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{64}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{48.28\%}                              & \multicolumn{1}{c|}{56.30\%}                             & \multicolumn{1}{c|}{53.33\%}                              & \multicolumn{1}{c|}{54.39\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}61.70\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89.74\%}        & \multicolumn{1}{c|}{60.00\%}                          & \multicolumn{1}{c|}{25.00\%}                         & \multicolumn{1}{c|}{55.56\%}                         & \multicolumn{1}{c|}{59.15\%}                         & \multicolumn{1}{c|}{50.00\%}                         & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{52.17\%}                              & \multicolumn{1}{c|}{56.25\%}                             \\ \cline{3-17}
+			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Memorability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$\\ p =0.1992\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$\\ p = 0.4478\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,  133) = 9.016$\\ p = 0.0013\end{tabular}}        & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$\\ p = 0.4467\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$\\ p =  0.3987\end{tabular}}                        \\ \hline
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{19}                                   & \multicolumn{1}{c|}{67}                                  & \multicolumn{1}{c|}{61}                                   & \multicolumn{1}{c|}{25}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{13}                              & \multicolumn{1}{c|}{30}                              & \multicolumn{1}{c|}{32}                              & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}34}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}27}          \\ \cline{3-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{68.42\%}                              & \multicolumn{1}{c|}{80.60\%}                             & \multicolumn{1}{c|}{77.05\%}                              & \multicolumn{1}{c|}{80.00\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81.69\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.00\%}        & \multicolumn{1}{c|}{80.00\%}                          & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{69.23\%}                         & \multicolumn{1}{c|}{90.00\%}                         & \multicolumn{1}{c|}{75.00\%}                         & \multicolumn{1}{c|}{0.00\%}                          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}70.59\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}88.89\%}     \\ \cline{3-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$\\ p = 0.2073\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$\\ p = 0.4947\end{tabular}}                          & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 20.956$\\ p \textless 0.0001\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$\\ p= 0.1709\end{tabular}}                                                                                                                                                                                                                                               & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$\\ p =0.078\end{tabular}}    \\ \cline{2-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}91}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}37}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}53}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}49}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}6}       & \multicolumn{1}{c|}{33}                                   & \multicolumn{1}{c|}{58}                                  \\ \cline{3-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}69.23\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}84.27\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}85.71\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.86\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.09\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}71.79\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.91\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}79.59\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}33.33\%} & \multicolumn{1}{c|}{69.70\%}                              & \multicolumn{1}{c|}{81.03\%}                             \\ \cline{3-17}
+			\multicolumn{1}{|l|}{\multirow{-6}{*}{\rotatebox{90}{Believability}}} & \multicolumn{1}{l|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$\\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$\\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$\\ p =0.086\end{tabular}}           & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$\\ p = 0.0726\end{tabular}}                                                                                                                                                                                                                    & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$\\ p = 0.1647\end{tabular}}                          \\ \hline
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{60}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{74}                                        & \multicolumn{1}{c|}{20}                                     & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{67}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{47}                                   & \multicolumn{1}{c|}{81}                                  \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{13.33\%}                              & \multicolumn{1}{c|}{9.24\%}                              & \multicolumn{1}{c|}{12.50\%}                              & \multicolumn{1}{c|}{6.78\%}                              & \multicolumn{1}{c|}{12.16\%}                                   & \multicolumn{1}{c|}{10.00\%}                                & \multicolumn{1}{c|}{20.00\%}                          & \multicolumn{1}{c|}{37.50\%}                         & \multicolumn{1}{c|}{5.56\%}                          & \multicolumn{1}{c|}{7.04\%}                          & \multicolumn{1}{c|}{13.43\%}                         & \multicolumn{1}{c|}{10.00\%}                         & \multicolumn{1}{c|}{14.89\%}                              & \multicolumn{1}{c|}{9.88\%}                              \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$\\ p = 0.2804\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$\\ p = 0.3948\end{tabular}}                                  & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$\\ p = 0.1492\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$\\ p = 0.2858\end{tabular}}                           \\ \cline{2-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}58}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}120}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}66}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10}      & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.86\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}9.24\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20.83\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}1.75\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12.77\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}25.64\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}   & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}11.11\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}19.70\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}40.00\%} & \multicolumn{1}{c|}{10.87\%}                              & \multicolumn{1}{c|}{17.50\%}                             \\ \cline{3-17}
+			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Desirability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$\\ p = 0.0034\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$\\ p = 0.059\end{tabular}}          & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$\\ p= 0.0729\end{tabular}}                                                                                                                                                                                                                     & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$\\ p = 0.2288\end{tabular}}                         \\ \hline
+		\end{tabular}
+	\end{adjustbox}
+\end{table*}
 

### 2016-09-17 paper/uist_2016/paper.tex
fixed inconsistent table bg color

@@
 			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Memorability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$\\ p =0.1992\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$\\ p = 0.4478\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,  133) = 9.016$\\ p = 0.0013\end{tabular}}        & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$\\ p = 0.4467\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$\\ p =  0.3987\end{tabular}}                        \\ \hline
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{19}                                   & \multicolumn{1}{c|}{67}                                  & \multicolumn{1}{c|}{61}                                   & \multicolumn{1}{c|}{25}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{13}                              & \multicolumn{1}{c|}{30}                              & \multicolumn{1}{c|}{32}                              & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}34}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}27}          \\ \cline{3-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{68.42\%}                              & \multicolumn{1}{c|}{80.60\%}                             & \multicolumn{1}{c|}{77.05\%}                              & \multicolumn{1}{c|}{80.00\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81.69\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.00\%}        & \multicolumn{1}{c|}{80.00\%}                          & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{69.23\%}                         & \multicolumn{1}{c|}{90.00\%}                         & \multicolumn{1}{c|}{75.00\%}                         & \multicolumn{1}{c|}{0.00\%}                          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}70.59\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}88.89\%}     \\ \cline{3-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$\\ p = 0.2073\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$\\ p = 0.4947\end{tabular}}                          & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 20.956$\\ p \textless 0.0001\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$\\ p= 0.1709\end{tabular}}                                                                                                                                                                                                                                               & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$\\ p =0.078\end{tabular}}    \\ \cline{2-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{19}                                   & \multicolumn{1}{c|}{67}                                  & \multicolumn{1}{c|}{61}                                   & \multicolumn{1}{c|}{25}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{13}                              & \multicolumn{1}{c|}{30}                              & \multicolumn{1}{c|}{32}                              & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}34}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}27}          \\ \cline{3-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{68.42\%}                              & \multicolumn{1}{c|}{80.60\%}                             & \multicolumn{1}{c|}{77.05\%}                              & \multicolumn{1}{c|}{80.00\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81.69\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.00\%}        & \multicolumn{1}{c|}{80.00\%}                          & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{69.23\%}                         & \multicolumn{1}{c|}{90.00\%}                         & \multicolumn{1}{c|}{75.00\%}                         & \multicolumn{1}{c|}{0.00\%}                          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70.59\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88.89\%}     \\ \cline{3-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$\\ p = 0.2073\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$\\ p = 0.4947\end{tabular}}                          & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 20.956$\\ p \textless 0.0001\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$\\ p= 0.1709\end{tabular}}                                                                                                                                                                                                                                               & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$\\ p =0.078\end{tabular}}    \\ \cline{2-17}
 			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}91}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}37}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}53}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}49}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}6}       & \multicolumn{1}{c|}{33}                                   & \multicolumn{1}{c|}{58}                                  \\ \cline{3-17}

### 2016-09-18 paper/uist_2016/paper.tex
moving around/deleting pics

@@
 \subsubsection{Hyperlapse Creation} 
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{Rewind-seasons2}
+	\caption{Plantation is classified using HSV color space, and the HSV values were adjusted to reflect seasonal changes}
+	\label{fig:season}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{Rewind-weather}
+	\caption{Meterological attributes are depicted using JavaScript canvas painting and animation}
+	\label{fig:weather}
+\end{figure*}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{Rewind-time_of_day2}
+	\caption{Per-pixel change is applied based on classified region}
+	\label{fig:timeofday}
+\end{figure}
+
 Each video recollection created by \textit{Rewind} is composed of two hundred Google Street View image sequences of the chosen route being stitched together using StreetViewSequence \cite{streetviewsequence}.
@@
 
-\begin{figure}
-   \centering
-     \includegraphics[width=1\linewidth]{Rewind-seasons2}
-     \caption{Plantation is classified using HSV color space, and the HSV values were adjusted to reflect seasonal changes}
-     \label{fig:season}
-\end{figure}
-
-\begin{figure}
-   \centering
-     \includegraphics[width=1\linewidth]{Rewind-time_of_day2}
-     \caption{Per-pixel change is applied based on classified region}
-     \label{fig:timeofday}
-\end{figure}
-
-\begin{figure}
-   \centering
-     \includegraphics[width=1\linewidth]{Rewind-weather}
-     \caption{Meterological attributes are depicted using JavaScript canvas painting and animation}
-     \label{fig:weather}
-\end{figure}
-
 % (Jeff): I think this is an unnecessary detail for this paper
@@
 The integer that follows denotes the distance in meters between a user's home and the given location "as the crow flies."
-
-\begin{table*}[t]
-	\centering
-	\caption{My caption}
-	\begin{adjustbox}{width=1\textwidth}
-		\small
-		\label{my-label}
-		\begin{tabular}{ccccccccccccccccc}
-			\cline{4-17}
-			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{2}{c|}{GPS usage}                                                                                       & \multicolumn{2}{c|}{Traveller type}                                                                                  & \multicolumn{2}{c|}{Accompany}                                                                                               & \multicolumn{6}{c|}{Distance}                                                                                                                                                                                                                                                                                                            & \multicolumn{2}{c|}{Visit frequency}                                                                                 \\ \cline{4-17}
-			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{1}{c|}{GPS user}                             & \multicolumn{1}{c|}{non-GPS user}                        & \multicolumn{1}{c|}{Frequent}                             & \multicolumn{1}{c|}{Non-frequent}                        & \multicolumn{1}{c|}{Alone}                                     & \multicolumn{1}{c|}{Not alone}                              & \multicolumn{1}{c|}{0}                                & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{2}                               & \multicolumn{1}{c|}{3}                               & \multicolumn{1}{c|}{4}                               & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{Most}                                 & \multicolumn{1}{c|}{Least}                               \\ \hline
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}60}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}74}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}47}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81}          \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}66.67\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}42.02\%}     & \multicolumn{1}{c|}{50.83\%}                              & \multicolumn{1}{c|}{47.46\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}55.00\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.22\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}43.66\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}51.56\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}27.66\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.20\%}     \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{l|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$\\ p =0.0016\end{tabular}}  & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$\\ p = 0.3953\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 31.812$\\ p \textless0.0001\end{tabular}}  & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$\\ p = 0.0028\end{tabular}}                                                                                                                                                                                                                   & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$\\ p = 0.0001\end{tabular}} \\ \cline{2-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{58}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{57}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{64}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{48.28\%}                              & \multicolumn{1}{c|}{56.30\%}                             & \multicolumn{1}{c|}{53.33\%}                              & \multicolumn{1}{c|}{54.39\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}61.70\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89.74\%}        & \multicolumn{1}{c|}{60.00\%}                          & \multicolumn{1}{c|}{25.00\%}                         & \multicolumn{1}{c|}{55.56\%}                         & \multicolumn{1}{c|}{59.15\%}                         & \multicolumn{1}{c|}{50.00\%}                         & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{52.17\%}                              & \multicolumn{1}{c|}{56.25\%}                             \\ \cline{3-17}
-			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Memorability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$\\ p =0.1992\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$\\ p = 0.4478\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,  133) = 9.016$\\ p = 0.0013\end{tabular}}        & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$\\ p = 0.4467\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$\\ p =  0.3987\end{tabular}}                        \\ \hline
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{19}                                   & \multicolumn{1}{c|}{67}                                  & \multicolumn{1}{c|}{61}                                   & \multicolumn{1}{c|}{25}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{13}                              & \multicolumn{1}{c|}{30}                              & \multicolumn{1}{c|}{32}                              & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}34}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}27}          \\ \cline{3-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{68.42\%}                              & \multicolumn{1}{c|}{80.60\%}                             & \multicolumn{1}{c|}{77.05\%}                              & \multicolumn{1}{c|}{80.00\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81.69\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.00\%}        & \multicolumn{1}{c|}{80.00\%}                          & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{69.23\%}                         & \multicolumn{1}{c|}{90.00\%}                         & \multicolumn{1}{c|}{75.00\%}                         & \multicolumn{1}{c|}{0.00\%}                          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70.59\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88.89\%}     \\ \cline{3-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$\\ p = 0.2073\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$\\ p = 0.4947\end{tabular}}                          & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 20.956$\\ p \textless 0.0001\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$\\ p= 0.1709\end{tabular}}                                                                                                                                                                                                                                               & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$\\ p =0.078\end{tabular}}    \\ \cline{2-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}91}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}37}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}53}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}49}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}6}       & \multicolumn{1}{c|}{33}                                   & \multicolumn{1}{c|}{58}                                  \\ \cline{3-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}69.23\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}84.27\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}85.71\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.86\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.09\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}71.79\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.91\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}79.59\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}33.33\%} & \multicolumn{1}{c|}{69.70\%}                              & \multicolumn{1}{c|}{81.03\%}                             \\ \cline{3-17}
-			\multicolumn{1}{|l|}{\multirow{-6}{*}{\rotatebox{90}{Believability}}} & \multicolumn{1}{l|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$\\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$\\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$\\ p =0.086\end{tabular}}           & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$\\ p = 0.0726\end{tabular}}                                                                                                                                                                                                                    & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$\\ p = 0.1647\end{tabular}}                          \\ \hline
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{60}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{74}                                        & \multicolumn{1}{c|}{20}                                     & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{67}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{47}                                   & \multicolumn{1}{c|}{81}                                  \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{13.33\%}                              & \multicolumn{1}{c|}{9.24\%}                              & \multicolumn{1}{c|}{12.50\%}                              & \multicolumn{1}{c|}{6.78\%}                              & \multicolumn{1}{c|}{12.16\%}                                   & \multicolumn{1}{c|}{10.00\%}                                & \multicolumn{1}{c|}{20.00\%}                          & \multicolumn{1}{c|}{37.50\%}                         & \multicolumn{1}{c|}{5.56\%}                          & \multicolumn{1}{c|}{7.04\%}                          & \multicolumn{1}{c|}{13.43\%}                         & \multicolumn{1}{c|}{10.00\%}                         & \multicolumn{1}{c|}{14.89\%}                              & \multicolumn{1}{c|}{9.88\%}                              \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$\\ p = 0.2804\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$\\ p = 0.3948\end{tabular}}                                  & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$\\ p = 0.1492\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$\\ p = 0.2858\end{tabular}}                           \\ \cline{2-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}58}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}120}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}66}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10}      & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.86\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}9.24\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20.83\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}1.75\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12.77\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}25.64\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}   & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}11.11\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}19.70\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}40.00\%} & \multicolumn{1}{c|}{10.87\%}                              & \multicolumn{1}{c|}{17.50\%}                             \\ \cline{3-17}
-			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Desirability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$\\ p = 0.0034\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$\\ p = 0.059\end{tabular}}          & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$\\ p= 0.0729\end{tabular}}                                                                                                                                                                                                                     & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$\\ p = 0.2288\end{tabular}}                         \\ \hline
-		\end{tabular}
-	\end{adjustbox}
-\end{table*}
 
@@
 Additionally, half of the participants were regular GPS users, that is people who used GPS even in locations already familiar to them.
+
+\begin{table*}[t]
+	\centering
+	\caption{My caption}
+	\begin{adjustbox}{width=1\textwidth}
+		\small
+		\label{my-label}
+		\begin{tabular}{ccccccccccccccccc}
+			\cline{4-17}
+			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{2}{c|}{GPS usage}                                                                                       & \multicolumn{2}{c|}{Traveller type}                                                                                  & \multicolumn{2}{c|}{Accompany}                                                                                               & \multicolumn{6}{c|}{Distance}                                                                                                                                                                                                                                                                                                            & \multicolumn{2}{c|}{Visit frequency}                                                                                 \\ \cline{4-17}
+			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{1}{c|}{GPS user}                             & \multicolumn{1}{c|}{non-GPS user}                        & \multicolumn{1}{c|}{Frequent}                             & \multicolumn{1}{c|}{Non-frequent}                        & \multicolumn{1}{c|}{Alone}                                     & \multicolumn{1}{c|}{Not alone}                              & \multicolumn{1}{c|}{0}                                & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{2}                               & \multicolumn{1}{c|}{3}                               & \multicolumn{1}{c|}{4}                               & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{Most}                                 & \multicolumn{1}{c|}{Least}                               \\ \hline
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}60}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}74}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}47}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81}          \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}66.67\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}42.02\%}     & \multicolumn{1}{c|}{50.83\%}                              & \multicolumn{1}{c|}{47.46\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}55.00\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.22\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}43.66\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}51.56\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}27.66\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.20\%}     \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{l|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$\\ p =0.0016\end{tabular}}  & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$\\ p = 0.3953\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 31.812$\\ p \textless0.0001\end{tabular}}  & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$\\ p = 0.0028\end{tabular}}                                                                                                                                                                                                                   & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$\\ p = 0.0001\end{tabular}} \\ \cline{2-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{58}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{57}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{64}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{48.28\%}                              & \multicolumn{1}{c|}{56.30\%}                             & \multicolumn{1}{c|}{53.33\%}                              & \multicolumn{1}{c|}{54.39\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}61.70\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89.74\%}        & \multicolumn{1}{c|}{60.00\%}                          & \multicolumn{1}{c|}{25.00\%}                         & \multicolumn{1}{c|}{55.56\%}                         & \multicolumn{1}{c|}{59.15\%}                         & \multicolumn{1}{c|}{50.00\%}                         & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{52.17\%}                              & \multicolumn{1}{c|}{56.25\%}                             \\ \cline{3-17}
+			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Memorability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$\\ p =0.1992\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$\\ p = 0.4478\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,  133) = 9.016$\\ p = 0.0013\end{tabular}}        & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$\\ p = 0.4467\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$\\ p =  0.3987\end{tabular}}                        \\ \hline
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{19}                                   & \multicolumn{1}{c|}{67}                                  & \multicolumn{1}{c|}{61}                                   & \multicolumn{1}{c|}{25}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{13}                              & \multicolumn{1}{c|}{30}                              & \multicolumn{1}{c|}{32}                              & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}34}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}27}          \\ \cline{3-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{68.42\%}                              & \multicolumn{1}{c|}{80.60\%}                             & \multicolumn{1}{c|}{77.05\%}                              & \multicolumn{1}{c|}{80.00\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81.69\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.00\%}        & \multicolumn{1}{c|}{80.00\%}                          & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{69.23\%}                         & \multicolumn{1}{c|}{90.00\%}                         & \multicolumn{1}{c|}{75.00\%}                         & \multicolumn{1}{c|}{0.00\%}                          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70.59\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88.89\%}     \\ \cline{3-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$\\ p = 0.2073\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$\\ p = 0.4947\end{tabular}}                          & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 20.956$\\ p \textless 0.0001\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$\\ p= 0.1709\end{tabular}}                                                                                                                                                                                                                                               & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$\\ p =0.078\end{tabular}}    \\ \cline{2-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}91}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}37}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}53}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}49}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}6}       & \multicolumn{1}{c|}{33}                                   & \multicolumn{1}{c|}{58}                                  \\ \cline{3-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}69.23\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}84.27\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}85.71\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.86\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.09\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}71.79\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.91\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}79.59\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}33.33\%} & \multicolumn{1}{c|}{69.70\%}                              & \multicolumn{1}{c|}{81.03\%}                             \\ \cline{3-17}
+			\multicolumn{1}{|l|}{\multirow{-6}{*}{\rotatebox{90}{Believability}}} & \multicolumn{1}{l|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$\\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$\\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$\\ p =0.086\end{tabular}}           & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$\\ p = 0.0726\end{tabular}}                                                                                                                                                                                                                    & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$\\ p = 0.1647\end{tabular}}                          \\ \hline
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{60}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{74}                                        & \multicolumn{1}{c|}{20}                                     & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{67}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{47}                                   & \multicolumn{1}{c|}{81}                                  \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{13.33\%}                              & \multicolumn{1}{c|}{9.24\%}                              & \multicolumn{1}{c|}{12.50\%}                              & \multicolumn{1}{c|}{6.78\%}                              & \multicolumn{1}{c|}{12.16\%}                                   & \multicolumn{1}{c|}{10.00\%}                                & \multicolumn{1}{c|}{20.00\%}                          & \multicolumn{1}{c|}{37.50\%}                         & \multicolumn{1}{c|}{5.56\%}                          & \multicolumn{1}{c|}{7.04\%}                          & \multicolumn{1}{c|}{13.43\%}                         & \multicolumn{1}{c|}{10.00\%}                         & \multicolumn{1}{c|}{14.89\%}                              & \multicolumn{1}{c|}{9.88\%}                              \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$\\ p = 0.2804\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$\\ p = 0.3948\end{tabular}}                                  & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$\\ p = 0.1492\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$\\ p = 0.2858\end{tabular}}                           \\ \cline{2-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}58}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}120}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}66}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10}      & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.86\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}9.24\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20.83\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}1.75\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12.77\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}25.64\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}   & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}11.11\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}19.70\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}40.00\%} & \multicolumn{1}{c|}{10.87\%}                              & \multicolumn{1}{c|}{17.50\%}                             \\ \cline{3-17}
+			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Desirability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$\\ p = 0.0034\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$\\ p = 0.059\end{tabular}}          & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$\\ p= 0.0729\end{tabular}}                                                                                                                                                                                                                     & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$\\ p = 0.2288\end{tabular}}                         \\ \hline
+		\end{tabular}
+	\end{adjustbox}
+\end{table*}
 

### 2016-09-18 paper/uist_2016/paper.tex
major edits throughout

--- 2016-09-17 paper/uist_2016/paper.tex
@@
 \begin{abstract}
-We propose \textit{Rewind}, a system that assists in the recall of episodic memory by automatically recreating interactive sceneries of past trips.
-\textit{Rewind} uses historical geolocation data to generate egocentric videos of earlier experiences from Google's Street View images.
+We introduce \textit{Rewind}, a system that assists in the recall of episodic memory by automatically recreating interactive sceneries of past trips.
+\textit{Rewind} uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images.
 Since the effectiveness of memory cues is determined by their level of integration with the target memory, the images are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience.
@@
 Trips taken in groups were more likely to be recalled using \textit{Rewind} videos than trips taken alone.
-\textit{Rewind} also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still generating believable representations that capture the past.
+\textit{Rewind} also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still preserve believable representations that capture the past.
 \end{abstract}
@@
 Now smartphone cameras are always nearby, ready for an opportunity to capture both the spectacular and the mundane.
-This paper introduces Rewind, the next evolution in digital memories: nothing to prepare or take out, just rewind and replay a trip from the past.
+This paper introduces Rewind, a prototype of the next evolution in digital memories: nothing to prepare or take out, just rewind and replay a trip from the past.
 
-While a camera or camcorder can explicitly capture a snapshot of an interesting moment, that one snapshot is only a tiny part of an experience, made even tinier when traveling.
+While a camera or camcorder can explicitly capture a snapshot of an interesting moment, that one snapshot is only a small part of an experience, made even smaller when traveling.
 In fact, most travel experience happens in transit: the perfectly cloudy stroll from the Eiffel Tower to the Louvre, the sound of dry gravel crackling under bus tires traversing up to Machu Picchu or monsoon rains drumming on all the tin roofs of Hanoi, and even the flight over the Florida Keys on the way to the sun-bathed Caribbean islands.
-A simple photograph is conclusively lacking in context.
+A simple photograph lacks this type of context.
 
-Geolocation data that can be automatically tracked and logged on a smartphone can be used to create context: to look up the weather at each moment, retrieve streetside photos from Google Street View at every step, and compute the mode of transportation (e.g., \cite{zheng2008learning}) and nearby geographical features.
+Geolocation data that can be automatically tracked and logged on a smartphone can be used to recreate context: to look up the weather at each moment, retrieve street side photos (e.g.
+from Google Street View) at every step, and compute the mode of transportation (e.g., \cite{zheng2008learning}) and nearby geographical features.
 The Rewind system takes those cues and manipulates the conditions of retrieved photos to re-imagine what a person saw at some past point in time.
@@
      \includegraphics[width=1\linewidth]{scroll}
-     \caption{Users move the stitched-together images forward and backward in time by scrubbing their pointer.}
+     \caption{Users move the stitched-together sequences of images forward and backward in time by scrubbing their pointer.}
      \label{fig:scrubbing}
@@
 Normally, it is difficult to ask someone about parts of their past that they do not entirely remember, because they do not remember what they do not remember.
-If you ask someone about a picture of themselves from ten years ago and they do not remember that particular point in time, there are no steps for re-remembering.
+% Note from Jeff: I'm not a fan of this example (that I commented out) because Rewinds don't recreate pictures of you either. Photos are actually much better at doing this.
+% If you ask someone about a picture of themselves from ten years ago and they do not remember that particular point in time, there are no steps for re-remembering.
 Using timestamped location data, we investigate whether a more realistic and contextual digital memory can help remind users of times from the past.
-Perhaps these Rewinds, series of images moving back and forth, can even help the forgetful recover past experiences.
+Perhaps these Rewinds, sequence of images moving back and forth, can even help the forgetful recover past experiences.
 This could be done for people who are already tracking their location intentionally (using a smartphone app like Moves or GPSLogger), or for the many people for whom location tracking has been enabled by default on Android phones.
-The Rewind system generates stitched-together and manipulated photos, called Rewinds, which we use to learn what makes memories memorable, believable, and desirable.
+
+Through Rewind, we investigate what makes memories memorable, believable, and desirable.
 Participants in a two-week study looked at their own Rewinds and assessed which trips or places were more memorable, whether the Rewinds felt believable as their own memories, which memories they desired to preserve, and in this process, helped us gain a sense of what Rewinds are beyond static photographs.
-
-We realize that not all memories are equally desirable.
+But not all memories are equally desirable.
 Through our study, we discovered not only what factors contribute to making a trip or place more memorable, but whether these are memories worth preserving.
@@
 Rewind resembles this interactive system, in a way that the reconstructed sceneries are of a careful mapping results from geolocation data and Google Street View images.
-However, Rewind differs in that the mapping is finalized with geolocation data provided by lifeloggers tracked using smartphones.
-This means that Rewind serves more of a getaway for recalling episodic memory rather than reviewing a potential travelling itinerary, aiming to provide a mechanism for reminiscence and sharing of past experience while exploring lifeloggers' behavioral patterns.
+However, Rewind differs in that the mapping is finalized with geolocation data provided by users tracked using smartphones.
+This means that Rewind serves more of a getaway for recalling episodic memory rather than reviewing a potential travelling itinerary, aiming to provide a mechanism for reminiscence and sharing of past experience while exploring users' behavioral patterns.
 Moreover, the reconstruction techniques used in Rewind would differentiate the same retrieved image with various temporal cues such as changes in seasons; yet the immediate results from the temporal queries suggested by de Silva and Aizawa have not been fully revealed.
@@
      \includegraphics[width=1\linewidth]{Rewind-Sample-Grid}
-     \caption{Rewinds are generated by stitching together Google Street View images of consecutive points on a given route. They are played from left to right to simulate a person on the move.}
+     \caption{Rewinds are generated by stitching together Google Street View images of consecutive points on a given route, which are manipulated to match the conditions from the past point in time.
+Rewinds are played from left to right to simulate a person on the move.}
      \label{fig:rewinds}
@@
 \section{The Rewind System}
-\textit{Rewind} recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers.
+\textit{Rewind} recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved from location-tracking apps, including the default tracking behavior on Android phones.
 Differing from previously studied hyperlapse creation techniques by Kopft et al.
 and Joshi et al \cite{Kopf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight.
-\textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images.
+\textit{Rewind} inputs geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images (although other street side photo services may be used).
 The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues.
-\textit{Rewind} is a client-side only application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it.
+The current version of \textit{Rewind} is a web-based application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it.
 %\ref{fig:flowchart}
@@
 
-\subsubsection{Route Determination} (needs to be rephrased? perhaps?)
-A user's geolocation tracking data includes latitude and longitude coordinates, timestamps of when the user was at given coordinates, and an accuracy score for each geolocation record.
+\subsection{Route Selection}
+A user's geolocation tracking data includes latitude and longitude coordinates, and timestamps of when the user was at given coordinates.
 \textit{Rewind} expects JSON formatted data, and is also compatible with other location-based formats such as GPX.
 Rewind generates location points for the user, using smart filtering based on visit frequencies to decrease the data noise and diversify the locations shown to the user.
-First, the user uploads their geolocation data to Rewind's main page.
-From there, less accurate location records are filtered out using the accuracy ratings provided by Google.
-Any location recording that has an accuracy radius greater than 200 meters is ignored.
-The accepted data is stored in memory to prepare the user's location points.
-A location frequency map is generated by counting the number of times each location appears in history.
+
+When the user loads their location data into Rewind, it filters out location coordinates with < 200 meter accuracy, and a location frequency map is generated by counting the number of times each location appears in history.
 In order to minimize the minor coordinate variations and to identify close coordinate pair records, only the first 3 decimal digits of coordinates are used when counting the number of appearances.
 The location with the highest number of visits is marked as user's home.
-We then use the Haversine formula to calculate the individual distance between all given locations and the user's home, attaching the distance data to the location.
+Rewind then uses the Haversine formula to calculate the individual distance between all given locations and the user's home, attaching the distance data to the location.
 
-\subsubsection{Hyperlapse Creation} 
+\subsection{Sequence Creation} 
 Each video recollection created by \textit{Rewind} is composed of two hundred Google Street View image sequences of the chosen route being stitched together using StreetViewSequence \cite{streetviewsequence}.
@@
 To compensate for this, pixel-wise adjustment was applied on each Google Street View image to better convey time-specific messages including times of the day, seasonal variances and meteorological specifics.
-Previous work done by \cite{laffont2014transient,shih2013data} have successfully reconstructed images with varying diurnal and seasonal cycles, yet it would be computationally expensive to replicate the proposed techniques on large sets of image data on the browser.
-Considering each \textit{Rewind} hyperlapse would contain two hundred frames, and lifeloggers would probably not be willing to spare more than one minute waiting for the composition of the video, it would be challenging to incorporate a large training dataset into the rendering pipeline.
-Due to the stringent timing constraint, we have instead adopted a more generic and naive approach of color space mapping for object segmentation and color adjustment, with the facilitation of CamanJS \cite{caman}.
+Previous work done by \cite{laffont2014transient,shih2013data} have successfully reconstructed images with varying diurnal and seasonal cycles, yet it would be computationally expensive to replicate the proposed techniques in real-time on large sets of images.
+Considering each \textit{Rewind} sequence of images would contain two hundred frames, this process would take many hours per route, and it would be challenging to incorporate a large training dataset into the rendering pipeline.
+Due to the timing constraint, Rewind instead adopts a simplified approach of color space mapping for object segmentation and color adjustment, with the facilitation of CamanJS \cite{caman}.
 
-As the Google Street view images of a given route have been retrieved with the same dimensional parameters and optical orientation, locational and spatial information of each image is largely similar (ex.
+As the Google Street View images of a given route have been retrieved with the same dimensional parameters and optical orientation, locational and spatial information of each image is largely similar (ex.
 the sky normally resides in the upper 1/3 of the image, but could occupy more than 1/2 of the image at times).
@@
 In addition, two linear brightness and saturation filters were applied locally and globally (Figure~\ref{fig:timeofday}).
-As an example of creating the evening scene, the incoming Google Street View images were segmented into three major areas: 1.
-Approximated sky region 2.
-Non-sky region in the approximated sky region 3.
-Approximated Ground region.
+As an example of creating the evening scene, the incoming Google Street View images were segmented into three major areas: 1) Approximated sky region 2) Non-sky region in the approximated sky region 3) Approximated Ground region.
 RGB values of each pixel were down-scaled based on the region the pixel is classified in.
 
-For meteorological conditions, a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations was used for weather lookup (currently only available for images from [anonymized: our state/province]).
-Sky colors was adjusted again using the technique mentioned previously for overcast, rainy and snowy sky.
-For determined rainy and snowy periods of time, an animated precipitation layer was overlaid on the hyperlapse and accompanied by corresponding audio effects to emulate the weather conditions exposed by the data (Figure~\ref{fig:weather}).
+For meteorological conditions, a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations was used for weather lookup (for the study, only data from [anonymized: our state/province] was loaded).
+Sky colors were adjusted again using the technique mentioned previously for overcast, rainy and snowy sky.
+For determined rainy and snowy periods of time, an animated precipitation layer was overlaid on the sequence of images and accompanied by corresponding audio effects to emulate the weather conditions exposed by the data (Figure~\ref{fig:weather}).
+Note that in the user study reported in this paper, an earlier version of the image manipulation was used, which adjusted whole-image color attributes.
 
@@
 
-Users can click on the images to load the accompanying ``trip'' videos (stitched images), or Rewinds.
-The purpose of Rewinds is to help users remember locations and trips.
-Rewinds are composed of locations visited on the same date as the Rewind's corresponding image.
+Users can click on the images to load the accompanying ``trip'' videos (stitched sequence of images), or Rewinds. The purpose of the Rewinds is to help users remember locations and trips.
+% Note from Jeff: Cut this sentence because I don't understand it. What's a ``corresponding image''?
+% Rewinds are composed of locations visited on the same date as the Rewind's corresponding image.
 When the user loads a Rewind, all the locations the user visited on that day are gathered and sorted, after which a route is mapped between the locations using the Google Maps API.
-This route data is passed to StreetviewSequence to generate Rewinds by stitching together images.
-For each point on a given route, StreetviewSequence requests panorama data from Google and determines the appropriate pitch and heading values to get the correct portion of the panorama.
-Those values are sent to Google Street View along with the necessary geolocation data to get the images that will be stitched together to make the Rewind.
+% Note from Jeff: Reader doesn't know what StreetviewSequence is, and probably does not need to
+% This route data is passed to StreetviewSequence to generate Rewinds by stitching together images. For each point on a given route, StreetviewSequence
+For each point in the route, Rewind determines the appropriate pitch and heading values to get the correct portion of the panorama.
+Those values are sent to Google Street View along with the necessary geolocation data to retrieve images that will be stitched together to make the Rewind.
 
-In order to account for time of day and season changes, StreetviewSequence library is modified to allow Rewind to intercept and manipulate each frame of the trip video, similar to the manipulations applied to the 10 location images.
+In order to account for time of day and season changes,
+% StreetviewSequence library is modified to allow Rewind to
+Rewind intercepts and manipulate each frame of the trip video, similar to the manipulations applied to the 10 location images.
 Once all the images within a trip are gathered from Google Street View and processed with CamanJS, users can play Rewinds in a loop, or scrub forward and backward over the video to investigate individual images more closely.
@@
 \subsection{Research Questions}
-The Rewind system enables us to ask questions about people's attitudes and behaviors surrounding digital memories that were not possible to answer before due to the scarcity of comprehensive data about where someone has been.
-To start to understand what makes a digital memory meaningful to a person, we performed a within-subjects comparison of Rewinds and static photography.
-By comparing Rewinds to today's most prevalent form of digital memory media, we can begin to distill what features make a Rewind meaningful and representative as a memory of a trip.
+The Rewind system enables us to ask questions about people's attitudes and behaviors surrounding digital memories that were not possible to answer before due to the scarcity of comprehensive data about where a person has been.
+To understand what makes a digital memory meaningful to a person, we performed a within-subjects comparison of Rewinds and static photos.
+By comparing Rewinds to today's most prevalent form of digital memory media, we can distill what features make a Rewind meaningful and representative as a memory of a trip.
 
-Our research questions examine the effectiveness of Rewinds through three aspects: memorability, believability, and desirability.
+Our research questions examine the effectiveness of Rewinds through three virtues of a memory: memorability, believability, and desirability.
 
-1) Memorability: Do certain features of a location or trip depicted in a digital memory make the memory more recallable?
-
-2) Believability:  Is the digital memory accurate to the participant's memory? What features make a digital memory accurate or inaccurate?
-
-3) Desirability: Which digital memories do users wish to save? Do certain features make a digital memory more likely to be kept?
+\begin{enumerate}
+\item Memorability: Do certain features of a location or trip depicted in a digital memory make the memory more recallable? 
+\item Believability:  Is the digital memory accurate to the participant's memory? What features make a digital memory accurate or inaccurate?
+\item Desirability: Which digital memories do users wish to save? Do certain features make a digital memory more likely to be kept?
+\end{enumerate}
 
 \subsection{Participants}
-Participants for the user study were recruited online through local Craigslist classifieds and Reddit communities for the Providence area.
+To recruit a diverse local population, participants for the user study were recruited online through local forums (Craigslist classifieds and local Reddit communities).
 Offline, ads were posted in cafes and other small businesses in the the city.
-Of the 21 total participants, 13 identified as men and 8 identified as women.
-Participants ranged from ages 20 to 50.
-Most participants were local residents, with occupations including librarian, medical researcher, office worker, IT consultant, musician, and comedian.
-A fifth of the participants were undergraduate or graduate students.
+Of the 21 total participants, 13 identified as men and 8 identified as women, and ranged from 20 to 50 years old.
+Participants were mainly local residents, with occupations including librarian, medical researcher, office worker, IT consultant, student, musician, and comedian.
+% Jeff notes, comment this out because it's not remarkable
+% A fifth of the participants were undergraduate or graduate students.
 
@@
 The participant's geolocation data was trimmed to ensure that photos and Rewind videos were generated from data gathered no earlier than the past two weeks.
-Participants were shown ten photo-Rewind pairs.
+Participants were shown ten photo-Rewind pairs in a semi-structured interview.
 Of the ten pairs, five showed trips taken infrequently, three showed trips taken most frequently, and the remaining two were random.
@@
 At the beginning of the study, participants were asked to identify their gender, whether they considered themselves a frequent traveler, and whether they tended to use GPS in places they were already familiar with.
-Participants who used GPS in familiar locations were considered regular GPS users, and participants who did not were considered non-regular GPS users.
+Then, questions about the photos and Rewinds investigated their memorability, believability, and desirability.
 
+%Participants who used GPS in familiar locations were considered regular GPS users, and participants who did not were considered non-regular GPS users.
 For each photo-Rewind pair, the participant was first shown a photo of one of the locations found in their geolocation data.
-The participant was asked to answer the following questions about the photo:
-
-Do you remember this location? If so, can you name the street? Can you name what is around the location, such as buildings, landmarks, or other places?
-
-Would you want to keep this photo? Why or why not? Were you traveling alone?
-
-If you remember the location, is the photo accurate to your memory? Why or why not? What was different?
+The participant was asked to answer the following questions about the photo: Do you remember this location?
+If so, can you name the street?
+Can you name what is around the location, such as buildings, landmarks, or other places?
+Would you want to keep this photo?
+Why or why not?
+Were you traveling alone?
+If you remember the location, is the photo accurate to your memory?
+Why or why not?
+What was different?
 
@@
 This allowed participants to ``walk through'' their memory at their own pace.
-The participant was asked the following questions while the Rewind played:
-
-Do you remember these locations? Do you remember this particular trip? Can  you name some of the streets? Can you name what is around these locations, such as buildings, landmarks, or other places?
-
-Would you want to keep this video? Why or why not? Were you traveling alone?
-
-If you remember these locations, is the video accurate to your memory? Why or why not? What was different?
-
-Questions about the photos and Rewinds tested their memorability, believability, and desirability as memory media.
+The participant was asked the following questions while the Rewind played: Do you remember these locations?
+Do you remember this particular trip?
+Can  you name some of the streets?
+Can you name what is around these locations, such as buildings, landmarks, or other places?
+Would you want to keep this video?
+Why or why not?
+Were you traveling alone?
+If you remember these locations, is the video accurate to your memory?
+Why or why not?
+What was different?
 
 In addition to asking questions, we observed the users as they examined their generated Rewinds, since they could passively watch the Rewind or actively scrub through the individual images that made up the Rewind.
-
-The user study took between 30 minutes to an hour for each participant, and participants were compensated \$30 cash for their time at the end of the study.
+The user study took between 30 minutes to an hour for each participant, and participants were compensated \$30 for their time at the end of the study.
 
@@
 Our findings show that trip remembrance is influenced by the presence of travel companions.
-As one might imagine, trips that were taken with other people were much more memorable than trips taken alone.
+As one might imagine, trips that were taken with other people were more memorable than trips taken alone.
 Participants were not able to remember the exact trip of 33\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 89\% of Rewinds that were taken with company.
@@
 So far, our findings show that regular GPS users remembered the locations in their digital memories less often, and from the locations they did remember, they were less likely to find a photo or Rewind accurate to their memory.
-One participant who identified as a regular GPS user said, "I really don't pay attention to my surroundings when I'm driving.
-I'm focused on the GPS and the road," when asked about the accuracy of a trip.
+One participant who identified as a regular GPS user said, ``I really don't pay attention to my surroundings when I'm driving.
+I'm focused on the GPS and the road,'' when asked about the accuracy of a trip.
 
@@
 We measured the value of photos and Rewinds by asking participants if they would want to keep the photo or Rewind after seeing it.
-In general, participants did not want to.
+Overall, participants wished to keep 11\% of the photos they were shown and 15\% of the Rewinds they were shown.
+Because these were images from third-party services, they are naturally less likely to be desirable than media captured by the user themselves.
 In this section we will look at how the value of Rewind's digitally-fabricated memories differs between participants who consider themselves frequent travelers and participants who don't.
 We will also examine how visit frequency and travel companionship affect the desirability of a Rewind.
-
-Overall, participants wanted to keep 11\% of the photos they were shown and 15\% of the Rewinds they were shown.
 
@@
 Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others.
-The data shows clearly that a Rewind is considered much more valuable if the trip it depicts was taken with company.
+The data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.
 
@@
 When asked why they wanted to keep or not keep a photo or Rewind, patterns emerged in the participants' answers.
-Participants didn't want to keep anything that was "no use" or had "no meaning or significance." One participant said they "didn't need any more memories of work." Some participants acknowledged the "good composition," and one said, "It's not a bad photo but it wasn't taken by me." Participants were most likely to keep photos that reminded them of good memories,
+Participants didn't want to keep anything that was ``no use'' or had ``no meaning or significance.'' One participant said they ``didn't need any more memories of work.'' Some participants acknowledged the ``good composition,'' and one said, ``It's not a bad photo but it wasn't taken by me.'' Participants were most likely to keep photos that reminded them of good memories,
 
@@
 There was a range of behaviors and attitudes toward Rewinds from the participants.
-One participant called Rewinds "creepy, eerie," and said they might "show them to a friend who's a conspiracy theorist." Another participant proclaimed that they weren't "paranoid about technology." Many participants, especially regular GPS users, examined signs in Rewinds intensely, looking at highway exit signs to try to remember their trip.
-Other participants did not feel positive after watching their Rewinds, saying that they "just realized how often [they] take the same route," or that they felt like they "needed to switch up [their] routine." One participant was amazed, and exclaimed, "It's like it's happening!" But the most important responses were from participants who changed their responses after recognizing an image in their Rewind: "I recognize the photo now." The Rewind had helped them remember the location of the original image.
+One participant called Rewinds ``creepy, eerie,'' and said they might ``show them to a friend who's a conspiracy theorist.'' Another participant proclaimed that they weren't ``paranoid about technology.'' Many participants, especially regular GPS users, examined signs in Rewinds intensely, looking at highway exit signs to try to remember their trip.
+Other participants did not feel positive after watching their Rewinds, saying that they ``just realized how often [they] take the same route,'' or that they felt like they ``needed to switch up [their] routine.'' One participant was amazed, and exclaimed, ``It's like it's happening!'' But the most important responses were from participants who changed their responses after recognizing an image in their Rewind: ``I recognize the photo now.'' The Rewind had helped them remember the location of the original image.
 
@@
 While the study results provide a wealth of correlations between varying factors and participant groups, our most significant findings pertain to the effects of regular GPS usage, visit frequency, and travel companionship on Rewind memorability, believability, and desirability.
-
-We found that regular GPS users are less able to remember locations and trips, and more often rely on road signs to jog their memory or determine Rewind believability.
+Regular GPS users are less able to remember locations and trips, and more often rely on road signs to jog their memory or determine Rewind believability.
 This confirms Leshed et al.'s findings that GPS users are typically disengaged with their environment \cite{leshed2008car}.
@@
 Currently, most street side images are of the road, as cameras that take these photos are attached to cars.
-But other forms of imagery has recently arrived: Google and Bing have expanded their street side photos to inside buildings, on hiking trails, and campus greens.
+But other forms of imagery have recently arrived: Google and Bing have expanded their street side photos to inside buildings, on hiking trails, and campus greens, and recent open source street side offerings like OpenStreetView have surfaced.
 Satellite images can be used for travel in airplanes and simulate the view outside the window from seat 17F.

### 2016-09-18 paper/uist_2016/paper.tex
add a minor note about mixed-methods

@@
 
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{Rewind-seasons2}
+	\caption{Plantation is classified using HSV color space, and the HSV values were adjusted to reflect seasonal changes}
+	\label{fig:season}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{Rewind-weather}
+	\caption{Meterological attributes are depicted using JavaScript canvas painting and animation}
+	\label{fig:weather}
+\end{figure*}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{Rewind-time_of_day2}
+	\caption{Per-pixel change is applied based on classified region}
+	\label{fig:timeofday}
+\end{figure}
+
 \subsection{Sequence Creation}
@@
 \subsection{Procedure}
-Participants underwent a two-week tracking period followed by a user study which investigated the memorability, believability, and desirability of the Rewinds produced from the two weeks of location data.
+Participants underwent a two-week tracking period followed by a mixed-methods user study which investigated the memorability, believability, and desirability of the Rewinds produced from the two weeks of location data.
 

### 2016-09-18 paper/uist_2016/paper.tex
dumped numbers in memorability section; fixed typos in the table

@@
 			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}60}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}74}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}47}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81}          \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}66.67\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}42.02\%}     & \multicolumn{1}{c|}{50.83\%}                              & \multicolumn{1}{c|}{47.46\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}55.00\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.22\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}43.66\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}51.56\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}27.66\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.20\%}     \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}33.33\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57.98\%}     & \multicolumn{1}{c|}{50.83\%}                              & \multicolumn{1}{c|}{47.46\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}55.00\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.22\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}43.66\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}51.56\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.34\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}35.80\%}     \\ \cline{3-17}
 			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{l|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$\\ p =0.0016\end{tabular}}  & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$\\ p = 0.3953\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 31.812$\\ p \textless0.0001\end{tabular}}  & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$\\ p = 0.0028\end{tabular}}                                                                                                                                                                                                                   & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$\\ p = 0.0001\end{tabular}} \\ \cline{2-17}
@@
 
+% shall we change photo/rewind video rememberance to location/trip rememberance?
 \subsection{Memorability}
@@
 
+% didn't do the stats for video location vs photo locations, not sure if it is necessary?
 \subsubsection{Rewinds versus Photos}
@@
 
+\subsubsection{GPS Usage}
+% Our findings show that GPS usage significantly affect the rememberance of locations $\chi^2(1,179) = 8.734$, p < 0.01, but does not impose a siginificant effect on trip rememberance.
+(GPS users remember locations 33% of the time whereas non-GPS users remember locations 58% of the time)
+Our findings show that participants who are not regular GPS users remember locations and trips more often than participants who are regular GPS users (Figure~\ref{fig:gpsmemory}).
+When asked whether they remember the location or trip being shown in a photo or Rewind, participants who do not use GPS regularly gave a positive answer 58\% of the time for location remembrance and 56\% of the time for trip remembrance.
+Regular GPS users remembered locations 33\% of the time and trips 48\% of the time.
+The data shows that participants who are regular GPS users did not remember the locations they visited or trips they took as often as participants who are not regular GPS users.
+Since regular GPS users are frequently directed step-by-step on how to navigate their environment, they may not pay as much attention to their surroundings.
+This diminished locational awareness could be the reason why regular GPS users had a lower remembrance rate for locations and trips.
+From these percentages, we also see that regular GPS users remember trips more often than they remember locations, while there is little difference between the two for participants who do not use GPS regularly.
+
+\subsubsection{Frequent Travelers}
+% has no siginifant effects on location no trip rememberance
+Our findings show that trip remembrance is influenced by the presence of travel companions.
+As one might imagine, trips that were taken with other people were more memorable than trips taken alone.
+Participants were not able to remember the exact trip of 33\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 89\% of Rewinds that were taken with company.
+
+\subsubsection{Travel Companions}
+% trip accompanies have siginificant effects on both location and trip rememberance. 
+% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
+% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
+Our findings show that trip remembrance is influenced by the presence of travel companions.
+As one might imagine, trips that were taken with other people were more memorable than trips taken alone.
+Participants were able to remember the exact trip of 67\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 90\% of Rewinds that were taken with company, with $\chi^2(1,133) = 9.016$, p < 0.01.
+
 \subsubsection{Distance}
+% only affect location rememberance
+% 0 - 100%, 1 - 75%, 2 - 72%, 3 - 44%, 4 - 52%, 5 - 10%, $\chi^2(5,179) = 18.106$, p < 0.01
 The distance away from the participant’s home had differing effects on photo memorability and Rewind memorability (Figure~\ref{fig:distancememory}).
@@
 Remembrance was 100\% for Distance Group 0, or home.
-One participant recognized a photo because her ``husband's car is in the driveway.'' Remembrance dropped to 74\% for Distance Group 1, then down to 10\% for Distance Group 5, which represented the locations furthest away from home.
+One participant recognized a photo because her ``husband's car is in the driveway.'' Remembrance dropped to 75\% for Distance Group 1, then down to 10\% for Distance Group 5, which represented the locations furthest away from home.
 These percentages are statistically significant, with a p-value of 0.0028.
@@
 \subsubsection{Visit Frequency}
+% only affect location rememberance
+% most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
 Location memorability and trip memorability are affected differently by frequency of visits (Figure~\ref{fig:frequencymemory}).
@@
 The more frequently a place was visited, the more likely it was that the participant remembered the location when it was shown to them at the study.
-In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places.
+In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places, with a significance at $\chi^2(1,128) = 14.458$, p < 0.01.
 This effect does not occur for trip memorability.
@@
 
-\subsubsection{Travel Companions}
-Our findings show that trip remembrance is influenced by the presence of travel companions.
-As one might imagine, trips that were taken with other people were more memorable than trips taken alone.
-Participants were not able to remember the exact trip of 33\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 89\% of Rewinds that were taken with company.
-
-\subsubsection{GPS Usage}
-Our findings show that participants who are not regular GPS users remember locations and trips more often than participants who are regular GPS users (Figure~\ref{fig:gpsmemory}).
-When asked whether they remember the location or trip being shown in a photo or Rewind, participants who do not use GPS regularly gave a positive answer 58\% of the time for location remembrance and 56\% of the time for trip remembrance.
-Regular GPS users remembered locations 33\% of the time and trips 47\% of the time.
-The data shows that participants who are regular GPS users did not remember the locations they visited or trips they took as often as participants who are not regular GPS users.
-Since regular GPS users are frequently directed step-by-step on how to navigate their environment, they may not pay as much attention to their surroundings.
-This diminished locational awareness could be the reason why regular GPS users had a lower remembrance rate for locations and trips.
-From these percentages, we also see that regular GPS users remember trips more often than they remember locations, while there is little difference between the two for participants who do not use GPS regularly.
-
 \begin{figure}
@@
 \end{figure}
-
-\subsubsection{Frequent Travelers}
-Our findings show that trip remembrance is influenced by the presence of travel companions.
-As one might imagine, trips that were taken with other people were more memorable than trips taken alone.
-Participants were not able to remember the exact trip of 33\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 89\% of Rewinds that were taken with company.
 

### 2016-09-19 paper/uist_2016/paper.tex
belivability

@@
 % only affect location rememberance
+% trip rememberance $\chi^2(1,126) = 0.066$, p = 0.3987 (> 0.05)
 % most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
@@
 \subsubsection{Other Variables}
+% needs to be filled?
 
@@
 \subsubsection{GPS Usage}
+% no significant effects on location belivability $\chi^2(1,86) = 0.666$, p = 0.2073(> 0.05)
+% signifant effects on trip belivability $\chi^2(1,128) = 2.917$, p = 0.0483(< 0.05)
+% GPS - 69%, non-GPS - 81%
 Our results show that participants who were not regular GPS users found photos and Rewinds to be accurate to their memory more often than regular GPS users did.
@@
 
+\subsubsection{Frequent Travelers}
+% no significant effects on photo belivability $\chi^2(1,86) = 0$, p = 0.4947(> 0.05)
+% significant effects on video belivability $\chi^2(1,128) = 5.837$, p = 0.0079 (< 0.01)
+% frequent - 86%, non-frequent - 65%
+
+\subsubsection{Travel Companions}
+% significant effects on photo/location belivability $\chi^2(1,91) = 20.956$, p < 0.01
+% traveling alone - 82%, not alone - 25%
+% significant effects on video/trip belivability if we use alpha = 0.1 - $\chi^2(1,127) = 1.865$, p = 0.086(< 0.1)
+% traveling alone - 84%, not alone - 72%
+Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept.
+Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep.
+Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others.
+The data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.
+
+\subsubsection{Distance}
+% no ignificant effects on photo/location belivability $\chi^2(5,86) = 7.745$, p = 0.1709 (> 0.05)
+% significant effects on video/trip belivability if we use alpha = 0.1 - $\chi^2(5,128) = 10.093$, p = 0.0726(< 0.1)
+% 0 - 100%, 1 - 75%, 2 - 75%, 3 - 85%, 4 - 80%, 5 - 33%
+
+\subsubsection{Visit Frequency}
+% significant effects on photo belivability if we use alpha = 0.1 - $\chi^2(1,61) = 2.012$, p = 0.078(< 0.1)
+% most frequently visited location - 71%, least frequently visited location - 89%
+% no significant effects on video/trip belivability $\chi^2(1,91) = 0.951$, p = 0.1647(> 0.05)
+% trip that include most frequently visited locations  -  70%, trip that include least frequently visited locations - 81%
+We found that the more visits a location had, the less likely it was for the Rewind associated with it to be judged as accurate by the participant.
+Trips with a location that was visited most frequently by the participant were said to be accurate 75\% of the time.
+The more a person visits a location, the more they may notice inconsistencies between the actual place and a digitally-fabricated memory of it.
+Trips with a location that was visited least frequently had a higher accuracy rating of 82\%.
+
 % (Jeff): this figure is probably best replaced with some text
@@
 %\end{figure}
-
-\subsubsection{Visit Frequency}
-We found that the more visits a location had, the less likely it was for the Rewind associated with it to be judged as accurate by the participant.
-Trips with a location that was visited most frequently by the participant were said to be accurate 75\% of the time.
-The more a person visits a location, the more they may notice inconsistencies between the actual place and a digitally-fabricated memory of it.
-Trips with a location that was visited least frequently had a higher accuracy rating of 82\%.
 
@@
 
-\subsubsection{Frequent Travelers}
+\subsection{Frequent Travellers}
 Our study found that participants who considered themselves frequent travelers were more likely to keep their photos and Rewinds than participants who did not identify as frequent travelers (Figure~\ref{fig:frequencydesire}).
@@
 This data suggests that Rewinds are more desirable if they portray a trip that has locations that are not visited often.
-
-\subsubsection{Travel Companions}
-Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept.
-Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep.
-Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others.
-The data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.
 

### 2016-09-19 paper/uist_2016/paper.tex
desirability

@@
 
+\subsection{Desirability}
+For Rewinds to be useful, they need to have value to their owners.
+We measured the value of photos and Rewinds by asking participants if they would want to keep the photo or Rewind after seeing it.
+Overall, participants wished to keep 11\% of the photos they were shown and 15\% of the Rewinds they were shown.
+Because these were images from third-party services, they are naturally less likely to be desirable than media captured by the user themselves.
+In this section we will look at how the value of Rewind's digitally-fabricated memories differs between participants who consider themselves frequent travelers and participants who don't.
+We will also examine how visit frequency and travel companionship affect the desirability of a Rewind.
+
+\subsubsection{GPS usage}
+% no significant effects on photo desirability $\chi^2(1,179) = 0.338$, p = 0.2804(> 0.05)
+% significant effects on video/trip desirability $\chi^2(1, 177) = 7.319$, p = 0.0034(< 0.01)
+% GPS - 26%, non-GPS - 9%
+
+\subsection{Frequent Travellers}
+% no significant effects on photo desirability $\chi^2(1,179) = 0.828$, p = 0.1814(> 0.05)
+% significant effects on video/trip desirability $\chi^2(1, 179) = 9.754$, p = 0.0009(< 0.01)
+% frequent - 21 %, non-frequent - 2%
+Our study found that participants who considered themselves frequent travelers were more likely to keep their photos and Rewinds than participants who did not identify as frequent travelers (Figure~\ref{fig:frequencydesire}).
+Frequent travelers kept 13\% of the photos they were shown and 21\% of Rewinds.
+But participants who identified as infrequent travelers kept only 7\% of photos and 2\% of Rewinds.
+The results show that those who consider themselves frequent travelers tend to place higher value on digital memories than those who do not identify as frequent travelers.
+
+\subsubsection{Travel Companions}
+% no significant effects on photo desirability $\chi^2(1,94) = 0.071$, p = 0.3948(> 0.05)
+% significant effects on video/trip desirability if alpha = 0.1 - $\chi^2(1, 133) = 2.443$, p = 0.059(< 0.1)
+% alone - 13%, not alone - 26%
+
+\subsubsection{Distance}
+% no significant effects on photo desirability $\chi^2(1,179) = 8.131$, p = 0.1492(> 0.05)
+% significant effects on video/trip desirability if alphe = 0.1 -  $\chi^2(5, 177) = 10.084$, p = 0.0729(< 0.1)
+% 0 - 0%, 1 - 0%, 2 - 11%,  3 - 10%, 4 - 20%,  5 - 40%
+
+\subsubsection{Visit Frequency}
+% no significant effects on photo desirability $\chi^2(1,128) = 0.32$, p = 0.2858(> 0.05)
+% most - 15%, least - 10%
+%  no significant effects on video/trip desirability $\chi^2(1, 126) = 0.552$, p = 0.2288(> 0.05)
+% most - 11%, least - 18%
+We found that the desirability of a Rewind is partly influenced by how much the participant visits the location associated with the Rewind.
+Rewinds containing a location visited most frequently by the participant are kept 8\% of the time.
+This percentage increases significantly if the Rewind contains the location visited least frequently by the participant.
+Rewinds that include the least visited location are kept 13\% of the time.
+This data suggests that Rewinds are more desirable if they portray a trip that has locations that are not visited often.
+
 \subsubsection{Features}
@@
 
-\subsection{Desirability and Value}
-For Rewinds to be useful, they need to have value to their owners.
-We measured the value of photos and Rewinds by asking participants if they would want to keep the photo or Rewind after seeing it.
-Overall, participants wished to keep 11\% of the photos they were shown and 15\% of the Rewinds they were shown.
-Because these were images from third-party services, they are naturally less likely to be desirable than media captured by the user themselves.
-In this section we will look at how the value of Rewind's digitally-fabricated memories differs between participants who consider themselves frequent travelers and participants who don't.
-We will also examine how visit frequency and travel companionship affect the desirability of a Rewind.
-
-\subsection{Frequent Travellers}
-Our study found that participants who considered themselves frequent travelers were more likely to keep their photos and Rewinds than participants who did not identify as frequent travelers (Figure~\ref{fig:frequencydesire}).
-Frequent travelers kept 13\% of the photos they were shown and 21\% of Rewinds.
-But participants who identified as infrequent travelers kept only 7\% of photos and 2\% of Rewinds.
-The results show that those who consider themselves frequent travelers tend to place higher value on digital memories than those who do not identify as frequent travelers.
-
 \begin{figure}
@@
 \end{figure}
-
-\subsubsection{Visit Frequency}
-We found that the desirability of a Rewind is partly influenced by how much the participant visits the location associated with the Rewind.
-Rewinds containing a location visited most frequently by the participant are kept 8\% of the time.
-This percentage increases significantly if the Rewind contains the location visited least frequently by the participant.
-Rewinds that include the least visited location are kept 13\% of the time.
-This data suggests that Rewinds are more desirable if they portray a trip that has locations that are not visited often.
 

### 2016-09-19 paper/uist_2016/paper.tex
before major changes

@@
 \section{User Study}
+% this needs to be polished
 \subsection{Research Questions}
-The Rewind system enables us to ask questions about people's attitudes and behaviors surrounding digital memories that were not possible to answer before due to the scarcity of comprehensive data about where a person has been.
+% is "digital memory" the right phrase for describing Rewind? Isn't rewind a medium for providing the cues to retrieve exisiting memories rather than creating new memories?
+\textit{Rewind} enables us to ask questions about people's attitudes and behaviors surrounding digital memories that were not possible to answer before due to the scarcity of comprehensive data about where a person has been.
 To understand what makes a digital memory meaningful to a person, we performed a within-subjects comparison of Rewinds and static photos.
@@
 
-Our research questions examine the effectiveness of Rewinds through three virtues of a memory: memorability, believability, and desirability.
+Our research questions examine the effectiveness of \textit{Rewind} videos through three virtues of a memory: memorability, believability, and desirability.
+%do we need a reference for the three virtues?
 
+% best way to put it?
 \begin{enumerate}
-\item Memorability: Do certain features of a location or trip depicted in a digital memory make the memory more recallable? 
-\item Believability:  Is the digital memory accurate to the participant's memory? What features make a digital memory accurate or inaccurate?
-\item Desirability: Which digital memories do users wish to save? Do certain features make a digital memory more likely to be kept?
+\item Memorability: How would \textit{Rewind} facilitate the retrival of episodic memory? What types of users are most likely to recall their memories using \textit{Rewind}?
+\item Believability:  How accurate are \textit{Rewind} artifacts in the eyes of the users' ? 
+\item Desirability: What factors are inherent to users' decisions in preserving artifacts created by \textit{Rewind}?
 \end{enumerate}
+
+% where to put this part or do we need a summary like this at all?
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Our user study explored the following five metrics that could potentially influence the aforesaid three measurements of \textit{Rewind} vidoes. These five metrics are:
+\begin{enumerate}
+\item GPS usage: how self-identified regular GPS users and non-regular GPS users differ in their responses to \textit{Rewind} videos.
+\item Traveler type: how self-identified frequent travelers and non-frequent travelers report to the three measurements of \textit{Rewind} videos differently.
+\item Companions: how traveling companionship and solitude affect users' viewpoints on \textit{Rewind} videos.
+\item Distance: how traveling distances affect users' perceptions of \textit{Rewind} videos.
+\item Visit frequency: how visit frequency of a particular place influence users' reporting on \textit{Rewind} videos.
+\end{enumerate}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Offline, ads were posted in cafes and other small businesses in the the city.
-Of the 21 total participants, 13 identified as men and 8 identified as women, and ranged from 20 to 50 years old.
+Of the 21 total participants, 13 were identified as men and 8 were identified as women, with age ranged from 20 to 50 years old.
 Participants were mainly local residents, with occupations including librarian, medical researcher, office worker, IT consultant, student, musician, and comedian.
@@
 \subsection{Procedure}
-Participants underwent a two-week tracking period followed by a mixed-methods user study which investigated the memorability, believability, and desirability of the Rewinds produced from the two weeks of location data.
+Participants underwent a two-week tracking period followed by a mixed-methods user study which investigated the memorability, believability, and desirability of \textit{Rewind} artifacts produced from the two weeks of location data.
 
@@
 
+% Rewind of the trip or Rewind video of the trip?
 The participant was then shown a Rewind of the trip that they were on when the previous location was encountered.
@@
 
+% ...that they did not carry the device on their person. - grammatical error?
 Data from three participants was not included in the results of this study.
@@
 
+% need to be rephrased.
 \section{Findings}
-The findings of our user study center on the participants' relationship to the Rewinds generated from their location data.
+Our user study explored five metrics that could potentially affect participants' memorability, belivability, and desirability of \textit{Rewind} vidoes. These five metrics are:
+
+participants' relationship to \textit{Rewind} videos generated from their location data.
 We focus on the participants' judgments of their Rewinds' memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds.
@@
 			\cline{4-17}
-			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{2}{c|}{GPS usage}                                                                                       & \multicolumn{2}{c|}{Traveller type}                                                                                  & \multicolumn{2}{c|}{Accompany}                                                                                               & \multicolumn{6}{c|}{Distance}                                                                                                                                                                                                                                                                                                            & \multicolumn{2}{c|}{Visit frequency}                                                                                 \\ \cline{4-17}
+			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{2}{c|}{GPS usage}                                                                                       & \multicolumn{2}{c|}{Traveller type}                                                                                  & \multicolumn{2}{c|}{Companions}                                                                                               & \multicolumn{6}{c|}{Distance}                                                                                                                                                                                                                                                                                                            & \multicolumn{2}{c|}{Visit frequency}                                                                                 \\ \cline{4-17}
 			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{1}{c|}{GPS user}                             & \multicolumn{1}{c|}{non-GPS user}                        & \multicolumn{1}{c|}{Frequent}                             & \multicolumn{1}{c|}{Non-frequent}                        & \multicolumn{1}{c|}{Alone}                                     & \multicolumn{1}{c|}{Not alone}                              & \multicolumn{1}{c|}{0}                                & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{2}                               & \multicolumn{1}{c|}{3}                               & \multicolumn{1}{c|}{4}                               & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{Most}                                 & \multicolumn{1}{c|}{Least}                               \\ \hline

### 2016-09-19 paper/uist_2016/paper.tex
the right version before major changes..

@@
 
+% heather - perhaps giving this part a new title?
+\subsection{User Interaction}
 Users can click on the images to load the accompanying ``trip'' videos (stitched sequence of images), or Rewinds. The purpose of the Rewinds is to help users remember locations and trips.
@@
 \section{User Study}
-% this needs to be polished
 \subsection{Research Questions}
-% is "digital memory" the right phrase for describing Rewind? Isn't rewind a medium for providing the cues to retrieve exisiting memories rather than creating new memories?
-\textit{Rewind} enables us to ask questions about people's attitudes and behaviors surrounding digital memories that were not possible to answer before due to the scarcity of comprehensive data about where a person has been.
+% heather - is "digital memory" the right phrase for describing Rewind? Isn't rewind a medium for providing the cues to retrieve exisiting memories rather than creating new memories?
+The Rewind system enables us to ask questions about people's attitudes and behaviors surrounding digital memories that were not possible to answer before due to the scarcity of comprehensive data about where a person has been.
 To understand what makes a digital memory meaningful to a person, we performed a within-subjects comparison of Rewinds and static photos.
@@
 Our research questions examine the effectiveness of \textit{Rewind} videos through three virtues of a memory: memorability, believability, and desirability.
-%do we need a reference for the three virtues?
+% heather - do we need a reference for the three virtues?
 
-% best way to put it?
+% heather - I changed this part...
 \begin{enumerate}
-\item Memorability: How would \textit{Rewind} facilitate the retrival of episodic memory? What types of users are most likely to recall their memories using \textit{Rewind}?
+\item Memorability: How would \textit{Rewind} facilitate with the retrival of episodic memory? What types of users are most likely to recall their memories using \textit{Rewind}?
 \item Believability:  How accurate are \textit{Rewind} artifacts in the eyes of the users' ? 
@@
 
-% where to put this part or do we need a summary like this at all?
+% heather - where to put this part or do we need a summary like this at all?
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Our user study explored the following five metrics that could potentially influence the aforesaid three measurements of \textit{Rewind} vidoes. These five metrics are:
-\begin{enumerate}
-\item GPS usage: how self-identified regular GPS users and non-regular GPS users differ in their responses to \textit{Rewind} videos.
-\item Traveler type: how self-identified frequent travelers and non-frequent travelers report to the three measurements of \textit{Rewind} videos differently.
-\item Companions: how traveling companionship and solitude affect users' viewpoints on \textit{Rewind} videos.
-\item Distance: how traveling distances affect users' perceptions of \textit{Rewind} videos.
-\item Visit frequency: how visit frequency of a particular place influence users' reporting on \textit{Rewind} videos.
-\end{enumerate}
+\item GPS usage: how self-identified regular GPS users and non-regular GPS users differ in their responses to \textit{Rewind} vidoes.
+\item Traveller type: how self-identified frequent travellers and non-frequent travellers report to the three measurements of \textit{Rewind} vidoes differently.
+\item Companions: how travelling companionship and solitude affect users' viewpoints on \textit{Rewind} vidoes.
+\item Distance: how travelling distances affect users' perceptions of \textit{Rewind} vidoes.
+\item Visit frequency: how visit frequency of a particular place influence users' reporting on \textit{Rewind} vidoes.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% Rewind of the trip or Rewind video of the trip?
+% heather - Rewind of the trip or Rewind video of the trip?
 The participant was then shown a Rewind of the trip that they were on when the previous location was encountered.
@@
 
-% ...that they did not carry the device on their person. - grammatical error?
+% heather - ...that they did not carry the device on their person. - grammatical error?
 Data from three participants was not included in the results of this study.
@@
 
-% need to be rephrased.
+% heather - need to be rephrased perhaps? Should we give a high level summary of all the relationships we've found? More analysis to be done for photo vs. videos, another table?
 \section{Findings}
-Our user study explored five metrics that could potentially affect participants' memorability, belivability, and desirability of \textit{Rewind} vidoes. These five metrics are:
-
-participants' relationship to \textit{Rewind} videos generated from their location data.
-We focus on the participants' judgments of their Rewinds' memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds.
+The findings of our user study center on the participants’ relationship to the Rewinds generated from their location data.
+We focus on the participants’ judgments of their Rewinds’ memorability, believability, and desirability in comparison to their judgments of the photos paired with paired with the Rewinds.
 We also discuss the participants' interactions with and reactions to their Rewinds.
@@
 
-% didn't do the stats for video location vs photo locations, not sure if it is necessary?
+% heather - didn't do the stats for video location vs photo locations, not sure if it is necessary? - photo vs video stats?
 \subsubsection{Rewinds versus Photos}

### 2016-09-20 paper/uist_2016/paper.tex
findings

@@
 \section{Related Work}
+% heather - trips vs locations -> (define) semantic memory vs episodic memory - check references, relate to some work done by SenseCam perhaps?
+% cut down GPS usage
 \subsection{Digital Memories}
@@
 \section{The Rewind System}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% heather - depth of processing, retrival cues, uniqueness of encoding - Rewind ----> retrival cues
+% http://www.psych.utoronto.ca/Neuropsychologylab/PDF/Depth%20of%20processing,%20retrieval%20cues,%20and.pdf
+% go into introduction?
+% come back to this section if time allows.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \textit{Rewind} recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved from location-tracking apps, including the default tracking behavior on Android phones.
-Differing from previously studied hyperlapse creation techniques by Kopft et al.
+Differing from previously studied hyperlapse creation techniques, such as the studies by Kopft et al.
 and Joshi et al \cite{Kopf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight.
@@
 The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues.
-The current version of \textit{Rewind} is a web-based application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it.
+The current version of \textit{Rewind} is a open-sourced, web-based application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store them.
+\textit{Rewind} can be accessed at [anonymized: url to rewind].
 %\ref{fig:flowchart}
@@
 % heather - is "digital memory" the right phrase for describing Rewind? Isn't rewind a medium for providing the cues to retrieve exisiting memories rather than creating new memories?
+% talk about both within-subject and between-subject comparisons 
+% within-subject -> memorability -> efficacy of semantic memory retrival vs episodic memory retrival -> video is better for both sementic and episodic
+% between-subject -> memorability -> what type of users benefit the most from episodic memory retrival using Rewind; what kind of trip is Rewind best at capturing - (least frequently visited trip?
+most frequently visited trip?
+trip that's far away from home?)
 The Rewind system enables us to ask questions about people's attitudes and behaviors surrounding digital memories that were not possible to answer before due to the scarcity of comprehensive data about where a person has been.
@@
 \begin{enumerate}
-\item Memorability: How would \textit{Rewind} facilitate with the retrival of episodic memory? What types of users are most likely to recall their memories using \textit{Rewind}?
+\item Memorability: How would \textit{Rewind} facilitate the retrival of semantic and episodic memory? What types of users are most likely to recall their memories using \textit{Rewind}?
 \item Believability:  How accurate are \textit{Rewind} artifacts in the eyes of the users' ? 
@@
 Our user study explored the following five metrics that could potentially influence the aforesaid three measurements of \textit{Rewind} vidoes. These five metrics are:
-\item GPS usage: how self-identified regular GPS users and non-regular GPS users differ in their responses to \textit{Rewind} vidoes.
-\item Traveller type: how self-identified frequent travellers and non-frequent travellers report to the three measurements of \textit{Rewind} vidoes differently.
-\item Companions: how travelling companionship and solitude affect users' viewpoints on \textit{Rewind} vidoes.
-\item Distance: how travelling distances affect users' perceptions of \textit{Rewind} vidoes.
-\item Visit frequency: how visit frequency of a particular place influence users' reporting on \textit{Rewind} vidoes.
+\begin{enumerate}
+\item GPS usage: how self-identified regular GPS users and non-regular GPS users differ in their responses to \textit{Rewind} videos.
+\item Traveler type: how self-identified frequent and non-frequent travelers report to the three measurements of \textit{Rewind} videos differently.
+\item Companions: how traveling companionship and solitude affect users' viewpoints on \textit{Rewind} videos.
+\item Distance: how traveling distances influence users' perceptions of \textit{Rewind} videos.
+\item Visit frequency: how visit frequency of a particular place influences users' reporting on \textit{Rewind} videos.
+\end{enumerate}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % heather - need to be rephrased perhaps? Should we give a high level summary of all the relationships we've found? More analysis to be done for photo vs. videos, another table?
+% semantic vs episodic memory
 \section{Findings}
+upper-bound estimates of event-related memories. 
 The findings of our user study center on the participants’ relationship to the Rewinds generated from their location data.
-We focus on the participants’ judgments of their Rewinds’ memorability, believability, and desirability in comparison to their judgments of the photos paired with paired with the Rewinds.
+We focus on the participants’ judgments of their Rewinds’ memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds.
 We also discuss the participants' interactions with and reactions to their Rewinds.
@@
 Additionally, half of the participants were regular GPS users, that is people who used GPS even in locations already familiar to them.
+
+\subsection{Within-subject study}
+\subsubsection{Memorability}
+Within-subject comparison in our study reveals that participants are significantly better at recalling semantic memory of a particular location with \textit{Rewind} videos than with static street-view images, $\chi^2(1, 356) = 96.987$, $p < 0.01$.
+When being presented with a street-side image retrieved based on their location data, participants were able to recognize places visited 50\% of the time; yet recognition rate of locations reached 97\% when participants started playing accompanied \textit{Rewind} video, with a significant increase of 47\%.
+It is perhaps not too surprising as cinematic media like \textit{Rewind} video would provide users with more contextual meanings and retrival cues for semantic processing, as more than one participant have expressed their contentment after wathing \textit{Rewind} videos by claiming ``I recognize the photo now!'' when their initial attempts with static images were fruitless.
+
+It could possibly be inferred that participants are likely to benefit more from \textit{Rewind} videos than static street-view images at recalling episodic memory.
+Although participants were not explicitly asked about trip rememberance when presented with static images, location rememberance from static images may serve as an upper-bound estimation of how much an individual could recall about a particular trip.
+- tbc
+\subsubsection{Belivability and Desirability}
+Although not statistically significant,
+
+\subsection{Between-subject study}
+
+\begin{table*}[t]
+	\centering
+	\caption{My caption}
+	\small
+	\label{within-subject-table}
+	\begin{tabular}{c|c|c|c|c|c|c|c|c|}
+		\cline{2-9}
+		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Belivability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
+		& \begin{tabular}[c]{@{}c@{}}video\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}video\\ trip\end{tabular} & photo & video & photo & video \\ \hline
+		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
+		\multicolumn{1}{|c|}{\%} & 96.61\% & \multicolumn{2}{c|}{49.72\%} & 53.67\% & 77.91\% & 79.69\% & 10.61\% & 14.69\% \\ \hline
+		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
+	\end{tabular}
+\end{table*}
+% 2nd table %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 		\small
-		\label{my-label}
+		\label{between-subject-table}
 		\begin{tabular}{ccccccccccccccccc}
@@
 			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}60}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}74}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}47}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81}          \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}33.33\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57.98\%}     & \multicolumn{1}{c|}{50.83\%}                              & \multicolumn{1}{c|}{47.46\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}55.00\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.22\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}43.66\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}51.56\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.34\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}35.80\%}     \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}33.33\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57.98\%}     & \multicolumn{1}{c|}{50.83\%}                              & \multicolumn{1}{c|}{47.46\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}55.00\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.22\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}43.66\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}51.56\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.34\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}35.80\%}     \\ \cline{3-17}
 			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{l|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$\\ p =0.0016\end{tabular}}  & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$\\ p = 0.3953\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 31.812$\\ p \textless0.0001\end{tabular}}  & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$\\ p = 0.0028\end{tabular}}                                                                                                                                                                                                                   & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$\\ p = 0.0001\end{tabular}} \\ \cline{2-17}
 			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{58}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{57}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{64}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{48.28\%}                              & \multicolumn{1}{c|}{56.30\%}                             & \multicolumn{1}{c|}{53.33\%}                              & \multicolumn{1}{c|}{54.39\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}61.70\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89.74\%}        & \multicolumn{1}{c|}{60.00\%}                          & \multicolumn{1}{c|}{25.00\%}                         & \multicolumn{1}{c|}{55.56\%}                         & \multicolumn{1}{c|}{59.15\%}                         & \multicolumn{1}{c|}{50.00\%}                         & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{52.17\%}                              & \multicolumn{1}{c|}{56.25\%}                             \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{48.28\%}                              & \multicolumn{1}{c|}{56.30\%}                             & \multicolumn{1}{c|}{53.33\%}                              & \multicolumn{1}{c|}{54.39\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}61.70\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89.74\%}        & \multicolumn{1}{c|}{60.00\%}                          & \multicolumn{1}{c|}{25.00\%}                         & \multicolumn{1}{c|}{55.56\%}                         & \multicolumn{1}{c|}{59.15\%}                         & \multicolumn{1}{c|}{50.00\%}                         & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{52.17\%}                              & \multicolumn{1}{c|}{56.25\%}                             \\ \cline{3-17}
 			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Memorability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$\\ p =0.1992\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$\\ p = 0.4478\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,  133) = 9.016$\\ p = 0.0013\end{tabular}}        & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$\\ p = 0.4467\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$\\ p =  0.3987\end{tabular}}                        \\ \hline
 			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{19}                                   & \multicolumn{1}{c|}{67}                                  & \multicolumn{1}{c|}{61}                                   & \multicolumn{1}{c|}{25}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{13}                              & \multicolumn{1}{c|}{30}                              & \multicolumn{1}{c|}{32}                              & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}34}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}27}          \\ \cline{3-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{68.42\%}                              & \multicolumn{1}{c|}{80.60\%}                             & \multicolumn{1}{c|}{77.05\%}                              & \multicolumn{1}{c|}{80.00\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81.69\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.00\%}        & \multicolumn{1}{c|}{80.00\%}                          & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{69.23\%}                         & \multicolumn{1}{c|}{90.00\%}                         & \multicolumn{1}{c|}{75.00\%}                         & \multicolumn{1}{c|}{0.00\%}                          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70.59\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88.89\%}     \\ \cline{3-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{68.42\%}                              & \multicolumn{1}{c|}{80.60\%}                             & \multicolumn{1}{c|}{77.05\%}                              & \multicolumn{1}{c|}{80.00\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81.69\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.00\%}        & \multicolumn{1}{c|}{80.00\%}                          & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{69.23\%}                         & \multicolumn{1}{c|}{90.00\%}                         & \multicolumn{1}{c|}{75.00\%}                         & \multicolumn{1}{c|}{0.00\%}                          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70.59\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88.89\%}     \\ \cline{3-17}
 			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$\\ p = 0.2073\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$\\ p = 0.4947\end{tabular}}                          & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 20.956$\\ p \textless 0.0001\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$\\ p= 0.1709\end{tabular}}                                                                                                                                                                                                                                               & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$\\ p =0.078\end{tabular}}    \\ \cline{2-17}
 			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}91}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}37}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}53}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}49}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}6}       & \multicolumn{1}{c|}{33}                                   & \multicolumn{1}{c|}{58}                                  \\ \cline{3-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}69.23\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}84.27\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}85.71\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.86\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.09\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}71.79\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.91\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}79.59\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}33.33\%} & \multicolumn{1}{c|}{69.70\%}                              & \multicolumn{1}{c|}{81.03\%}                             \\ \cline{3-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}69.23\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}84.27\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}85.71\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.86\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.09\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}71.79\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.91\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}79.59\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}33.33\%} & \multicolumn{1}{c|}{69.70\%}                              & \multicolumn{1}{c|}{81.03\%}                             \\ \cline{3-17}
 			\multicolumn{1}{|l|}{\multirow{-6}{*}{\rotatebox{90}{Believability}}} & \multicolumn{1}{l|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$\\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$\\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$\\ p =0.086\end{tabular}}           & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$\\ p = 0.0726\end{tabular}}                                                                                                                                                                                                                    & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$\\ p = 0.1647\end{tabular}}                          \\ \hline
 			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{60}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{74}                                        & \multicolumn{1}{c|}{20}                                     & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{67}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{47}                                   & \multicolumn{1}{c|}{81}                                  \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{13.33\%}                              & \multicolumn{1}{c|}{9.24\%}                              & \multicolumn{1}{c|}{12.50\%}                              & \multicolumn{1}{c|}{6.78\%}                              & \multicolumn{1}{c|}{12.16\%}                                   & \multicolumn{1}{c|}{10.00\%}                                & \multicolumn{1}{c|}{20.00\%}                          & \multicolumn{1}{c|}{37.50\%}                         & \multicolumn{1}{c|}{5.56\%}                          & \multicolumn{1}{c|}{7.04\%}                          & \multicolumn{1}{c|}{13.43\%}                         & \multicolumn{1}{c|}{10.00\%}                         & \multicolumn{1}{c|}{14.89\%}                              & \multicolumn{1}{c|}{9.88\%}                              \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{13.33\%}                              & \multicolumn{1}{c|}{9.24\%}                              & \multicolumn{1}{c|}{12.50\%}                              & \multicolumn{1}{c|}{6.78\%}                              & \multicolumn{1}{c|}{12.16\%}                                   & \multicolumn{1}{c|}{10.00\%}                                & \multicolumn{1}{c|}{20.00\%}                          & \multicolumn{1}{c|}{37.50\%}                         & \multicolumn{1}{c|}{5.56\%}                          & \multicolumn{1}{c|}{7.04\%}                          & \multicolumn{1}{c|}{13.43\%}                         & \multicolumn{1}{c|}{10.00\%}                         & \multicolumn{1}{c|}{14.89\%}                              & \multicolumn{1}{c|}{9.88\%}                              \\ \cline{3-17}
 			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$\\ p = 0.2804\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$\\ p = 0.3948\end{tabular}}                                  & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$\\ p = 0.1492\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$\\ p = 0.2858\end{tabular}}                           \\ \cline{2-17}
 			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}58}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}120}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}66}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10}      & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{mean}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.86\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}9.24\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20.83\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}1.75\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12.77\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}25.64\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}   & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}11.11\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}19.70\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}40.00\%} & \multicolumn{1}{c|}{10.87\%}                              & \multicolumn{1}{c|}{17.50\%}                             \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.86\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}9.24\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20.83\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}1.75\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12.77\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}25.64\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}   & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}11.11\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}19.70\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}40.00\%} & \multicolumn{1}{c|}{10.87\%}                              & \multicolumn{1}{c|}{17.50\%}                             \\ \cline{3-17}
 			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Desirability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$\\ p = 0.0034\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$\\ p = 0.059\end{tabular}}          & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$\\ p= 0.0729\end{tabular}}                                                                                                                                                                                                                     & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$\\ p = 0.2288\end{tabular}}                         \\ \hline
@@
 % heather - didn't do the stats for video location vs photo locations, not sure if it is necessary? - photo vs video stats?
-\subsubsection{Rewinds versus Photos}
-When participants were shown a street side photo from their location history, they were asked whether they recognized the location in the photo.
+% will add this part back in within-group comparison
+
+% \subsubsection{Rewinds versus Photos}
+% When participants were shown a street side photo from their location history, they were asked whether they recognized the location in the photo.
 In 50\% of cases, participants said they did.
@@
 (GPS users remember locations 33% of the time whereas non-GPS users remember locations 58% of the time)
-Our findings show that participants who are not regular GPS users remember locations and trips more often than participants who are regular GPS users (Figure~\ref{fig:gpsmemory}).
-When asked whether they remember the location or trip being shown in a photo or Rewind, participants who do not use GPS regularly gave a positive answer 58\% of the time for location remembrance and 56\% of the time for trip remembrance.
-Regular GPS users remembered locations 33\% of the time and trips 48\% of the time.
-The data shows that participants who are regular GPS users did not remember the locations they visited or trips they took as often as participants who are not regular GPS users.
-Since regular GPS users are frequently directed step-by-step on how to navigate their environment, they may not pay as much attention to their surroundings.
-This diminished locational awareness could be the reason why regular GPS users had a lower remembrance rate for locations and trips.
-From these percentages, we also see that regular GPS users remember trips more often than they remember locations, while there is little difference between the two for participants who do not use GPS regularly.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% heather - come back to this if time allows
+% because memories are simply not encoded so there's no way to retrieve it in the first place?
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Our findings show that GPS usage significantly affect participants' remembrance of locations $\chi^2(1,179) = 8.734$, p = 0.0016 ($< 0.01$), but does not impose significant effects on trip remembrance $\chi^2(1,177) = 0.713$, p = 0.1992 ($> 0.05$).
+When asked whether they remember the location in a static photo, non-regular GPS users gave a positive answer 58\% of the time whereas regular GPS users gave a positive answer 33\% of the time.
+Although the difference between non-regular and regular GPS users' trip remembrance is not statistically significance, the between-subject percentage values still lean towards the observation that it is perhaps easier for non-GPS users to recall episodic memories from external memory cues, given that the total trip remembrance rate for non-GPS users is 48\% and that of GPS users is 56\%.
+Since regular GPS users are frequently directed step-by-step on how to navigate through their environment, regular GPS users may not need to pay as much attention to their surroundings, leading to potentially diminished locational awareness which could be the reason why regular GPS users had a lower remembrance rate for their ambience, particularly locations.
+\\
 
@@
 % has no siginifant effects on location no trip rememberance
-Our findings show that trip remembrance is influenced by the presence of travel companions.
-As one might imagine, trips that were taken with other people were more memorable than trips taken alone.
-Participants were not able to remember the exact trip of 33\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 89\% of Rewinds that were taken with company.
+% needing explaination perhaps?
+Although location rememberance is slightly higher for frequent traveler (51\% for frequent and 48\% for non-frequent), and trip rememberance is slightly higher for non-frequent traveler (53\% for frequent and 54\% for non-frequent), our study has not found these variances statistically significant.
 
@@
 % trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
-Our findings show that trip remembrance is influenced by the presence of travel companions.
-As one might imagine, trips that were taken with other people were more memorable than trips taken alone.
-Participants were able to remember the exact trip of 67\% of Rewinds taken when they were traveling alone, but they could remember the exact trip of 90\% of Rewinds that were taken with company, with $\chi^2(1,133) = 9.016$, p < 0.01.
+Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way.
+For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1,94) = 31.812$, $p < 0.00001$.
+On the other hand, trip details tend to be more easily remembered during accompanied visits.
+Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching a \textit{Rewind} video, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=1\linewidth]{distance}
-	\caption{Location remembrance is inversely correlated to its distance from a participant's home.}
-	\label{fig:distancememory}
-\end{figure}
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=1\linewidth]{distance}
+% 	\caption{Location remembrance is inversely correlated to its distance from a participant's home.}
+% 	\label{fig:distancememory}
+% \end{figure}
 
@@
 
-\begin{figure}
-   \centering
-     \includegraphics[width=1\linewidth]{RML_2}
-     \caption{Locations were more likely to be remembered where participants had visited the place more, whereas trips were more likely to be remembered where participants had visited the place less.}
-     \label{fig:frequencymemory}
-\end{figure}
+% \begin{figure}
+%    \centering
+%      \includegraphics[width=1\linewidth]{RML_2}
+%      \caption{Locations were more likely to be remembered where participants had visited the place more, whereas trips were more likely to be remembered where participants had visited the place less.}
+%      \label{fig:frequencymemory}
+% \end{figure}
 
-\begin{figure}
-	\centering
-	\includegraphics[width=1\linewidth]{GPS_remembrance_2}
-	\caption{Regular GPS users remembered locations 33\% of the time and trips 47\%, compared to 58\% and 56\% for non-regular GPS users.}
-	\label{fig:gpsmemory}
-\end{figure}
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=1\linewidth]{GPS_remembrance_2}
+% 	\caption{Regular GPS users remembered locations 33\% of the time and trips 47\%, compared to 58\% and 56\% for non-regular GPS users.}
+% 	\label{fig:gpsmemory}
+% \end{figure}
 
@@
 % GPS - 69%, non-GPS - 81%
-Our results show that participants who were not regular GPS users found photos and Rewinds to be accurate to their memory more often than regular GPS users did.
+Our results show that participants who were non-regular GPS users found photos and Rewinds to be accurate to their memory more often than regular GPS users did.
 Photos and Rewinds could only be considered accurate to a participant's memory if the participant first confirmed that they remembered the locations in them.
@@
 % frequent - 21 %, non-frequent - 2%
-Our study found that participants who considered themselves frequent travelers were more likely to keep their photos and Rewinds than participants who did not identify as frequent travelers (Figure~\ref{fig:frequencydesire}).
+Our study found that participants who considered themselves frequent travelers were more likely to keep their photos and Rewinds than participants who did not identify as frequent travelers.
 Frequent travelers kept 13\% of the photos they were shown and 21\% of Rewinds.
@@
 
-\begin{figure}
-   \centering
-     \includegraphics[width=1\linewidth]{FreqTraveler_keep_2}
-     \caption{Frequent travelers are more willing to keep copies of photos and Rewinds.}
-     \label{fig:frequencydesire}
-\end{figure}
+% \begin{figure}
+%    \centering
+%      \includegraphics[width=1\linewidth]{FreqTraveler_keep_2}
+%      \caption{Frequent travelers are more willing to keep copies of photos and Rewinds.}
+%      \label{fig:frequencydesire}
+% \end{figure}
 

### 2016-09-20 paper/uist_2016/paper.tex
more to come

@@
 
+% heather - add more results in here since we have more to report. Probably cut down image manipulation?
 \begin{abstract}
-We introduce \textit{Rewind}, a system that assists in the recall of episodic memory by automatically recreating interactive sceneries of past trips.
+We introduce \textit{Rewind}, a system that assists in the recall of semantic and episodic memory by automatically recreating interactive sceneries of past trips.
 \textit{Rewind} uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images.
-Since the effectiveness of memory cues is determined by their level of integration with the target memory, the images are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience.
+Since the effectiveness of memory cues is determined by their level of integration with the target memory, images used in \textit{Rewind} are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience.
 Users can interactively go back and forth in time by scrubbing over the video.
@@
 
+% heather - add determination of home?
 \subsection{Route Selection}
@@
 % semantic vs episodic memory
+% mention distance categories in the beginning (up up up) + everything else 
 \section{Findings}
-upper-bound estimates of event-related memories. 
 The findings of our user study center on the participants’ relationship to the Rewinds generated from their location data.
@@
 \subsection{Within-subject study}
-\subsubsection{Memorability}
-Within-subject comparison in our study reveals that participants are significantly better at recalling semantic memory of a particular location with \textit{Rewind} videos than with static street-view images, $\chi^2(1, 356) = 96.987$, $p < 0.01$.
+\subsubsection{Semantic Memory} 
+Within-subject comparison in our study reveals that participants are significantly better at recalling semantic memory of a particular location with \textit{Rewind} videos than with static street-view images, $\chi^2(1, N=356) = 96.987$, $p <.01$.
 When being presented with a street-side image retrieved based on their location data, participants were able to recognize places visited 50\% of the time; yet recognition rate of locations reached 97\% when participants started playing accompanied \textit{Rewind} video, with a significant increase of 47\%.
-It is perhaps not too surprising as cinematic media like \textit{Rewind} video would provide users with more contextual meanings and retrival cues for semantic processing, as more than one participant have expressed their contentment after wathing \textit{Rewind} videos by claiming ``I recognize the photo now!'' when their initial attempts with static images were fruitless.
+It is perhaps not too surprising as cinematic media like \textit{Rewind} video would provide users with more contextual meanings and retrival cues for semantic processing, as three participants (P4, P6 and P10) have once expressed their contentment after watching \textit{Rewind} videos by claiming ``I recognize the photo now!'' when their initial attempts with static images recognition were fruitless.
 
+%
+\subsubsection{Episodic Memory}
 It could possibly be inferred that participants are likely to benefit more from \textit{Rewind} videos than static street-view images at recalling episodic memory.
-Although participants were not explicitly asked about trip rememberance when presented with static images, location rememberance from static images may serve as an upper-bound estimation of how much an individual could recall about a particular trip.
-- tbc
+Although participants were not explicitly asked about trip rememberance when presented with static images as opposed to what they were asked after watchiing \textit{Rewind} videos, location rememberance from static images may serve as an upper-bound estimation of how much an individual could recall about a particular trip; since if participants fail to form any cognitive association with the locations depicted in the images, it is very unlikely that they would be able to associate target itineraries with the locations shown.
+Thus, it is perhaps safe to presume that location rememberance with images bounds above the maximum likelihood of trip rememberance with the same images presented to the participants, and we used location rememberance from image recognition as an upper-limit gauge against trip rememberance from \textit{Rewind} videos thereafter.
+
+% h - add another table, only abt memorability tho
+% explain distance groups in the beginning
+% where is home? need to explain this part in system?
+Using the aforementioned presumption, our study examined effects of \textit{Rewind} videos on episodic processing in metric-specific groups, as well as the performance overall.
+Our study shows that comparing to static street-view images, recollection of event-driven memories using \textit{Rewind} videos is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.
+Our study also suggested that GPS users would benefit more from \textit{Rewind}, even though the difference was mildly significant by an increase about 15\%, $\chi^2(1, N=118) = 2.145$, $p = .0715 (<.1)$.
+% h - prob explain this a little bit more
+
+One plausible explanation of the improvement may be inherent to the encoding of episodic memory in the first place.
+As suggested by the levels-of-processing theory(ref), encoding efficacy is heavily dependent on the levels to which stimuli are being actively or passively processed.
+Not surprisingly, superficial mental engagement would produce weaker, and less enduring cognitive representation which would demand more contextually accurate and abundant cues for memory triggery, and vice versa.
+Oftentimes, the cognitive representation resulted from shallow processing may not even be retrievable at all as it is simply not available for retrieval.
+As previously described, both of the trips revealed in our results, those that were taken farthest away from home and those that were least frequently taken, may not be special enough to engage deep memory encoding nor often enough to reinforce incidental remembrance.
+This means that it would be more difficult for participants to recall these trips if the provided cues are not effective enough.
+Since \textit{Rewind} videos provide richer and more contextually meaningful cues than static street-side images, it is reasonable that \textit{Rewind} significantly outperforms plain images as suggested by our statistical analysis.
+While being asked about location and trip rememberance on one of his least frequently taken route, P7 was not able to identify the location from the static image; yet he recognized the trip from \textit{Rewind} video as ``one street (in the video) helps me (him) remember".
+
+It may appear to be puzzling that participants seem to recall less about specifics of their trips from \textit{Rewind} videos compared to static images when they traveled alone, with a significant decrease around 40\%, $\chi^2(1, N=168) = 33.831$, $p <.01$; when the trips were most frequently taken, with a significant decrease of 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$; and when the trips taken were 10 - 100 meters (33 - 328 feet) away from home, with a mildly significant decrease of 50\%, $\chi^2(1, N=16) = 2.25$, $p <.1$.
+
 \subsubsection{Belivability and Desirability}
@@
 
+%%UPDATE BOTH TABLES AND ADD ONE MORE%%%
+%%%%%%%%%%%percentage to decimal
 \begin{table*}[t]

### 2016-09-20 paper/uist_2016/paper.tex
almost done w/ within-subject memo

@@
 Since \textit{Rewind} videos provide richer and more contextually meaningful cues than static street-side images, it is reasonable that \textit{Rewind} significantly outperforms plain images as suggested by our statistical analysis.
-While being asked about location and trip rememberance on one of his least frequently taken route, P7 was not able to identify the location from the static image; yet he recognized the trip from \textit{Rewind} video as ``one street (in the video) helps me (him) remember".
+While being asked about location and trip rememberance on one of his least frequently taken routes, P7 was not able to identify the location from the static image at first; yet he recognized the trip from \textit{Rewind} video as ``one street (in the video) helps me (him) remember".
+%The Effects of Divided Attention on Encoding and Retrieval Processes in Human Memory 
+% http://www2.psych.ubc.ca/~pgraf/Psy583Readings/Craik%20et%20al%201996.pdf
+% Craik et al. 1996
+
+The extent to which attention is dedicated while taking a trip may be another possible explanation for the observed improvement using Rewinds.
+This is perhaps particularly applicable to explain why participants who were self-identified regular GPS users tend to benefit more from Rewinds with episodic memory recalling.
+Laboratory work done by Craik et al.
+1996 (ref) has demonstrated that the encoding of memory is more effective under full-attention conditions than divided-attention conditions.
+This means that regular GPS users, who are often directed step-by-step on how to navigate through their environments, may be less likely to engage their attention while taking their routes, leading to less available cognitive representation for retrieval.
+P3, a self-identified regular GPS user who had 30\% recalling rate using static images and 80\% trip remembrance rate using Rewinds said ``I really don't pay attention to my surroundings when I'm driving.
+(I am) Focused (focused) on GPS and road"  Under this circumstance, it is almost certain that Rewinds would provide a more successful access to episodic memory as it provides more spatial-temporal cues for memory retrieval, by not only adjusting image attributes to reflect timely and weather changes, but also mimicing the motions of the users when they travel down a particular path.
 

### 2016-09-20 paper/uist_2016/paper.tex
user study pretty much finished

--- 2016-09-20 paper/uist_2016/paper.tex
@@
 To understand what makes a digital memory meaningful to a person, we performed a within-subjects comparison of Rewinds and static photos.
-By comparing Rewinds to today's most prevalent form of digital memory media, we can distill what features make a Rewind meaningful and representative as a memory of a trip.
+By comparing Rewinds to today's most prevalent form of digital memory media, we can distill what features make Rewinds, and digitally-mediated memories in general, meaningful and representative as a memory of a trip.
 
-Our research questions examine the effectiveness of \textit{Rewind} videos through three virtues of a memory: memorability, believability, and desirability.
+Our research questions examine the effectiveness of Rewinds compared to static photos through three virtues of a memory: memorability, believability, and desirability.
 % heather - do we need a reference for the three virtues?
+april - yeah that would be ideal!
 
 % heather - I changed this part...
-\begin{enumerate}
-\item Memorability: How would \textit{Rewind} facilitate the retrival of semantic and episodic memory? What types of users are most likely to recall their memories using \textit{Rewind}?
-\item Believability:  How accurate are \textit{Rewind} artifacts in the eyes of the users' ? 
-\item Desirability: What factors are inherent to users' decisions in preserving artifacts created by \textit{Rewind}?
+\begin{enumerate}% TODO TODO define semantic vs episodic memory
+\item Memorability: How well do Rewinds facilitate the retrieval of semantic and episodic memory? What types of participants are most likely to recall their memories using Rewinds?
+\item Believability:  How accurate are Rewinds in the eyes of the participants? 
+\item Desirability: What factors are inherent to participants' decisions in preserving artifacts created by the Rewind system?
 \end{enumerate}
 
-% heather - where to put this part or do we need a summary like this at all?
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Our user study explored the following five metrics that could potentially influence the aforesaid three measurements of \textit{Rewind} vidoes. These five metrics are:
-\begin{enumerate}
-\item GPS usage: how self-identified regular GPS users and non-regular GPS users differ in their responses to \textit{Rewind} videos.
-\item Traveler type: how self-identified frequent and non-frequent travelers report to the three measurements of \textit{Rewind} videos differently.
-\item Companions: how traveling companionship and solitude affect users' viewpoints on \textit{Rewind} videos.
-\item Distance: how traveling distances influence users' perceptions of \textit{Rewind} videos.
-\item Visit frequency: how visit frequency of a particular place influences users' reporting on \textit{Rewind} videos.
-\end{enumerate}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Participants}
-To recruit a diverse local population, participants for the user study were recruited online through local forums (Craigslist classifieds and local Reddit communities).
-Offline, ads were posted in cafes and other small businesses in the the city.
-Of the 21 total participants, 13 were identified as men and 8 were identified as women, with age ranged from 20 to 50 years old.
+To recruit a diverse local population, participants for the user study were recruited through online forums (Craigslist classifieds and local Reddit communities) and offline ads, which were posted in cafes and other small businesses in the the city.
+Of the 21 total participants, 13 identified themselves as men and 8 identified themselves as women, with ages ranging from 20 to 50 years old.
 Participants were mainly local residents, with occupations including librarian, medical researcher, office worker, IT consultant, student, musician, and comedian.
@@
 \subsection{Procedure}
-Participants underwent a two-week tracking period followed by a mixed-methods user study which investigated the memorability, believability, and desirability of \textit{Rewind} artifacts produced from the two weeks of location data.
+Participants underwent a two-week tracking period followed by a mixed-methods user study which investigated the memorability, believability, and desirability of Rewinds generated from the two weeks of location data.
 
@@
 
-% heather - Rewind of the trip or Rewind video of the trip?
-The participant was then shown a Rewind of the trip that they were on when the previous location was encountered.
+% heather - Rewind of the trip or Rewind video of the trip? april - we say 'rewind' when we mean rewind video, and if we want to refer to the system, we say 'the rewind system'
+The participant was then shown a Rewind of the trip that they were on when the location in the photo was encountered.
 While the Rewind was playing, the participant could hover over the Rewind panel and scrub backwards and forwards horizontally through the images that composed the video.
@@
 
-In addition to asking questions, we observed the users as they examined their generated Rewinds, since they could passively watch the Rewind or actively scrub through the individual images that made up the Rewind.
+In addition to asking questions, we observed the participants as they examined their Rewinds.
+For instance, participants could passively watch the Rewind or actively scrub through the individual images that made up the Rewind.
 The user study took between 30 minutes to an hour for each participant, and participants were compensated \$30 for their time at the end of the study.
 
-% heather - ...that they did not carry the device on their person. - grammatical error?
-Data from three participants was not included in the results of this study.
+% heather - ...that they did not carry the device on their person. - grammatical error? april - nope (maybe out of fashion now though?), their person = their body
+Data from three participants were not included in the results of this study.
 One of the participants' data points consisted of only one location.
-The participant used a mobile device provided by the study, so it is likely that they did not carry the device on their person.
+The participant used a mobile device provided by the study, so it is likely that they did not carry the device on their person throughout the day, but left it in one place.
 Another participant did not complete the in-person interview portion of the user study due to health and scheduling reasons.
@@
 \section{Findings}
-upper-bound estimates of event-related memories. 
-The findings of our user study center on the participants’ relationship to the Rewinds generated from their location data.
+% upper-bound estimates of event-related memories.  <-- april - found this without the beginning of its sentence. where does this fragment belong?
+The findings of our user study center on the participants’ relationship to the Rewinds generated from their location data compared to the static photos.
 We focus on the participants’ judgments of their Rewinds’ memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds.
@@
 Half of the participants identified themselves as frequent travelers.
-Additionally, half of the participants were regular GPS users, that is people who used GPS even in locations already familiar to them.
+Additionally, half of the participants were regular GPS users, which we defined as people who use GPS navigation even in locations already familiar to them.
 
-\subsection{Within-subject study}
+% heather - where to put this part or do we need a summary like this at all?
+% april - moved to findings section from user study section
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Our user study explored the following five metrics as potentially having an effect on memorability, believability, or desirability of digital memory media:
+\begin{enumerate}
+	\item Distance: how does the location's distance away from the participant's home influence the participant's perception of Rewinds and static photos?
+Distances ranged from 0 to 206,155 meters.
+For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 corresponded to a range of 10--100 meters; Group 2 corresponded to a range of 100--1,000 meters; Group 3 corresponded to a range of 1,000--10,000 meters; Group 4 corresponded to a range of 10,000--100,000 meters and Group 5 corresponded to a range of 100,000--1,000,000 meters from the participant's home location.
+	\item Visit frequency: do participants react differently to Rewinds and static photos depicting locations they visit frequently compared to locations they rarely visit?
+We showed locations that were either ``most frequently visited,'' ``least frequently visited,'' or randomly selected.
+	\item GPS usage: do participants who use GPS navigation regularly react differently to Rewinds and static photos compared to participants who don't use GPS navigation regularly?
+	\item Traveler type: do attitudes toward Rewinds and static photos differ depending on whether the participant identifies as a frequent traveler?
+	\item Companions: how does the presence of a traveling companion affect the participant's attitude toward Rewinds or static photos?
+\end{enumerate}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Within-Subject Study}
 \subsubsection{Memorability}
-Within-subject comparison in our study reveals that participants are significantly better at recalling semantic memory of a particular location with \textit{Rewind} videos than with static street-view images, $\chi^2(1, 356) = 96.987$, $p < 0.01$.
-When being presented with a street-side image retrieved based on their location data, participants were able to recognize places visited 50\% of the time; yet recognition rate of locations reached 97\% when participants started playing accompanied \textit{Rewind} video, with a significant increase of 47\%.
-It is perhaps not too surprising as cinematic media like \textit{Rewind} video would provide users with more contextual meanings and retrival cues for semantic processing, as more than one participant have expressed their contentment after wathing \textit{Rewind} videos by claiming ``I recognize the photo now!'' when their initial attempts with static images were fruitless.
+Within-subject comparison in our study reveals that participants are significantly better at recalling semantic memory of a particular location with Rewinds than with static street-view photos, $\chi^2(1, 356) = 96.987$, $p < 0.01$.
+When being presented with a street-side photo, participants were able to recognize places visited 50\% of the time; yet recognition rate of locations reached 97\% when participants played accompanying Rewinds.
+It should not be too surprising that cinematic media like a Rewind would provide participants with more contextual meanings and retrival cues for semantic processing, as more than one participant have expressed their contentment after wathing \textit{Rewind} videos by claiming ``I recognize the photo now!'' when their initial attempts with static images were fruitless.
 
 It could possibly be inferred that participants are likely to benefit more from \textit{Rewind} videos than static street-view images at recalling episodic memory.
-Although participants were not explicitly asked about trip rememberance when presented with static images, location rememberance from static images may serve as an upper-bound estimation of how much an individual could recall about a particular trip.
-- tbc
-\subsubsection{Belivability and Desirability}
-Although not statistically significant,
+Although participants were not explicitly asked about trip remembrance when presented with static images, location rememberance from static images may serve as an upper-bound estimation of how much an individual could recall about a particular trip.
+%- tbc
+\subsubsection{Believability and Desirability}
+Although not statistically significant, %TODO TODO TODO TODO TODO
 
-\subsection{Between-subject study}
-
+\subsection{Between-Subject Study}
 \begin{table*}[t]
@@
 % shall we change photo/rewind video rememberance to location/trip rememberance?
+april - i define photo/rewind remembrance below.
+a photo and a rewind can have both location and trip remembrance.
+for instance from a photo you might remember the location but not the trip.
 \subsection{Memorability}
-Rewinds are meant to engage a person's memory.
-To find out more about what features make a digital memory memorable, we examined participant responses to whether or not they were able to remember the location shown in a photo or recall the trip portrayed by a Rewind.
+Rewinds, and digitally-mediated memories in general, are meant to engage a person's memory.
+To find out what features make a digital memory memorable, we examined participant responses to whether or not they were able to remember the location shown in a photo (semantic memory) or recall the trip portrayed by a Rewind (episodic memory).
 Photo memorability is determined by whether or not the participant remembered the location depicted in a photo.
-Because a Rewind contains many locations, it would be unfair to consider the memorability of Rewind based on whether participant remembers any locations in the Rewind.
+Because a Rewind contains many locations, it would be unfair to consider the memorability of Rewind based on whether the participant remembers any locations in the Rewind.
 So, Rewind memorability is determined by whether or not the participant remembered and could distinguish the particular trip portrayed in a Rewind.
-In this section, we will look at differences in photo and Rewind memorability based on the variables of distance from the participant's home, visit frequency, presence of travel companions, regular GPS usage, and whether the participant considered themselves a frequent traveler.
+In this section, we will look at differences in photo and Rewind memorability based on the five metrics discussed previously.
 
-% heather - didn't do the stats for video location vs photo locations, not sure if it is necessary? - photo vs video stats?
-% will add this part back in within-group comparison
+%TODO heather - didn't do the stats for video location vs photo locations, not sure if it is necessary? - photo vs video stats?
+%TODO will add this part back in within-group comparison
 
@@
 More than one participant exclaimed after watching a Rewind, ``I recognize the photo now!''
+
+\subsubsection{Distance}
+% only affect location rememberance
+% 0 - 100%, 1 - 75%, 2 - 72%, 3 - 44%, 4 - 52%, 5 - 10%, $\chi^2(5,179) = 18.106$, p < 0.01
+The distance away from the participant’s home had differing effects on photo memorability and Rewind memorability (Figure~\ref{fig:distancememory}).
+
+Photo memorability and distance had a clear linear relationship.
+As the distance increased, photo memorability decreased, suggesting that locations further away from home were less likely to be remembered.
+Remembrance was 100\% for Distance Group 0, or home.
+One participant recognized a photo because her ``husband's car is in the driveway.'' Remembrance dropped to 75\% for Distance Group 1, then down to 10\% for Distance Group 5, which represented the locations furthest away from home.
+These percentages are statistically significant, with a p-value of 0.0028.
+
+There was no statistical significance for Rewind remembrance.
+Our data does show, however, that Rewind remembrance was largely the same for most distance groups, except for distances that were close to home.
+While remembrance for almost all distance groups was on average near 60\%, remembrance for Rewinds in Distance Group 1 was 25\%.
+This data suggests that participants often did not remember or could not distinguish the exact trips occurring in locations close to their home, where most trips happen.
 
@@
 Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching a \textit{Rewind} video, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.
-
-\subsubsection{Distance}
-% only affect location rememberance
-% 0 - 100%, 1 - 75%, 2 - 72%, 3 - 44%, 4 - 52%, 5 - 10%, $\chi^2(5,179) = 18.106$, p < 0.01
-The distance away from the participant’s home had differing effects on photo memorability and Rewind memorability (Figure~\ref{fig:distancememory}).
-Distances ranged from 0 to 206,155 meters.
-For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 corresponded to a range of 10--100 meters; Group 2 corresponded to a range of 100--1,000 meters; Group 3 corresponded to a range of 1,000--10,000 meters; Group 4 corresponded to a range of 10,000--100,000 meters and Group 5 corresponded to a range of 100,000--1,000,000 meters from the participant's home location.
-
-Photo memorability and distance had a clear linear relationship.
-As the distance increased, photo memorability decreased, suggesting that locations further away from home were less likely to be remembered.
-Remembrance was 100\% for Distance Group 0, or home.
-One participant recognized a photo because her ``husband's car is in the driveway.'' Remembrance dropped to 75\% for Distance Group 1, then down to 10\% for Distance Group 5, which represented the locations furthest away from home.
-These percentages are statistically significant, with a p-value of 0.0028.
-
-There was no statistical significance for Rewind remembrance.
-Our data does show, however, that Rewind remembrance was largely the same for most distance groups, except for distances that were close to home.
-While remembrance for almost all distance groups was on average near 60\%, remembrance for Rewinds in Distance Group 1 was 25\%.
-This data suggests that participants often did not remember or could not distinguish the exact trips occurring in locations close to their home, where most trips happen.
 

### 2016-09-20 paper/uist_2016/paper.tex

@@
 % semantic vs episodic memory
+% mention distance categories in the beginning (up up up) + everything else 
 \section{Findings}
-% upper-bound estimates of event-related memories.  <-- april - found this without the beginning of its sentence. where does this fragment belong?
 The findings of our user study center on the participants’ relationship to the Rewinds generated from their location data compared to the static photos.
@@
 
-\subsection{Within-Subject Study}
-\subsubsection{Memorability}
-Within-subject comparison in our study reveals that participants are significantly better at recalling semantic memory of a particular location with Rewinds than with static street-view photos, $\chi^2(1, 356) = 96.987$, $p < 0.01$.
-When being presented with a street-side photo, participants were able to recognize places visited 50\% of the time; yet recognition rate of locations reached 97\% when participants played accompanying Rewinds.
-It should not be too surprising that cinematic media like a Rewind would provide participants with more contextual meanings and retrival cues for semantic processing, as more than one participant have expressed their contentment after wathing \textit{Rewind} videos by claiming ``I recognize the photo now!'' when their initial attempts with static images were fruitless.
+\subsection{Within-subject study}
+\subsubsection{Semantic Memory} 
+Within-subject comparison in our study reveals that participants are significantly better at recalling semantic memory of a particular location with \textit{Rewind} videos than with static street-view images, $\chi^2(1, N=356) = 96.987$, $p <.01$.
+When being presented with a street-side image retrieved based on their location data, participants were able to recognize places visited 50\% of the time; yet recognition rate of locations reached 97\% when participants started playing accompanied \textit{Rewind} video, with a significant increase of 47\%.
+It is perhaps not too surprising as cinematic media like \textit{Rewind} video would provide users with more contextual meanings and retrival cues for semantic processing, as three participants (P4, P6 and P10) have once expressed their contentment after watching \textit{Rewind} videos by claiming ``I recognize the photo now!'' when their initial attempts with static images recognition were fruitless.
+
+%
+\subsubsection{Episodic Memory}
+It could possibly be inferred that participants are likely to benefit more from \textit{Rewind} videos than static street-view images at recalling episodic memory.
+Although participants were not explicitly asked about trip rememberance when presented with static images as opposed to what they were asked after watchiing \textit{Rewind} videos, location rememberance from static images may serve as an upper-bound estimation of how much an individual could recall about a particular trip; since if participants fail to form any cognitive association with the locations depicted in the images, it is very unlikely that they would be able to associate target itineraries with the locations shown.
+Thus, it is perhaps safe to presume that location rememberance with images bounds above the maximum likelihood of trip rememberance with the same images presented to the participants, and we used location rememberance from image recognition as an upper-limit gauge against trip rememberance from \textit{Rewind} videos thereafter.
+
+% h - add another table, only abt memorability tho
+% explain distance groups in the beginning
+% where is home? need to explain this part in system?
+Using the aforementioned presumption, our study examined effects of \textit{Rewind} videos on episodic processing in metric-specific groups, as well as the performance overall.
+Our study shows that comparing to static street-view images, recollection of event-driven memories using \textit{Rewind} videos is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.
+Our study also suggested that GPS users would benefit more from \textit{Rewind}, even though the difference was mildly significant by an increase about 15\%, $\chi^2(1, N=118) = 2.145$, $p = .0715 (<.1)$.
+% h - prob explain this a little bit more
+
+One plausible explanation of the improvement may be inherent to the encoding of episodic memory in the first place.
+As suggested by the levels-of-processing theory(ref), encoding efficacy is heavily dependent on the levels to which stimuli are being actively or passively processed.
+Not surprisingly, superficial mental engagement would produce weaker, and less enduring cognitive representation which would demand more contextually accurate and abundant cues for memory triggery, and vice versa.
+Oftentimes, the cognitive representation resulted from shallow processing may not even be retrievable at all as it is simply not available for retrieval.
+As previously described, both of the trips revealed in our results, those that were taken farthest away from home and those that were least frequently taken, may not be special enough to engage deep memory encoding nor often enough to reinforce incidental remembrance.
+This means that it would be more difficult for participants to recall these trips if the provided cues are not effective enough.
+Since \textit{Rewind} videos provide richer and more contextually meaningful cues than static street-side images, it is reasonable that \textit{Rewind} significantly outperforms plain images as suggested by our statistical analysis.
+While being asked about location and trip rememberance on one of his least frequently taken routes, P7 was not able to identify the location from the static image at first; yet he recognized the trip from \textit{Rewind} video as ``one street (in the video) helps me (him) remember".
+%The Effects of Divided Attention on Encoding and Retrieval Processes in Human Memory 
+% http://www2.psych.ubc.ca/~pgraf/Psy583Readings/Craik%20et%20al%201996.pdf
+% Craik et al. 1996
+
+The extent to which attention is dedicated while taking a trip may be another possible explanation for the observed improvement using Rewinds.
+This is perhaps particularly applicable to explain why participants who were self-identified regular GPS users tend to benefit more from Rewinds with episodic memory recalling.
+Laboratory work done by Craik et al.
+1996 (ref) has demonstrated that the encoding of memory is more effective under full-attention conditions than divided-attention conditions.
+This means that regular GPS users, who are often directed step-by-step on how to navigate through their environments, may be less likely to engage their attention while taking their routes, leading to less available cognitive representation for retrieval.
+P3, a self-identified regular GPS user who had 30\% recalling rate using static images and 80\% trip remembrance rate using Rewinds said ``I really don't pay attention to my surroundings when I'm driving.
+(I am) Focused (focused) on GPS and road"  Under this circumstance, it is almost certain that Rewinds would provide a more successful access to episodic memory as it provides more spatial-temporal cues for memory retrieval, by not only adjusting image attributes to reflect timely and weather changes, but also mimicing the motions of the users when they travel down a particular path.
+
+It may appear to be puzzling that participants seem to recall less about specifics of their trips from \textit{Rewind} videos compared to static images when they traveled alone, with a significant decrease around 40\%, $\chi^2(1, N=168) = 33.831$, $p <.01$; when the trips were most frequently taken, with a significant decrease of 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$; and when the trips taken were 10 - 100 meters (33 - 328 feet) away from home, with a mildly significant decrease of 50\%, $\chi^2(1, N=16) = 2.25$, $p <.1$.
 
@@
 %- tbc
+
 \subsubsection{Believability and Desirability}
@@
 \subsection{Between-Subject Study}
+%%UPDATE BOTH TABLES AND ADD ONE MORE%%%
+%%%%%%%%%%%percentage to decimal
 \begin{table*}[t]
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Believability}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Desirability}

### 2016-09-21 paper/uist_2016/paper.tex
memory

@@
 Within-subject comparison in our study reveals that participants are significantly better at recalling semantic memory of a particular location with \textit{Rewind} videos than with static street-view images, $\chi^2(1, N=356) = 96.987$, $p <.01$.
-When being presented with a street-side image retrieved based on their location data, participants were able to recognize places visited 50\% of the time; yet recognition rate of locations reached 97\% when participants started playing accompanied \textit{Rewind} video, with a significant increase of 47\%.
-It is perhaps not too surprising as cinematic media like \textit{Rewind} video would provide users with more contextual meanings and retrival cues for semantic processing, as three participants (P4, P6 and P10) have once expressed their contentment after watching \textit{Rewind} videos by claiming ``I recognize the photo now!'' when their initial attempts with static images recognition were fruitless.
+When being presented with a street-side image retrieved based on their location data, participants were able to recognize places visited 50\% of the time; yet recognition rate of locations reached 97\% when participants started playing accompanied Rewinds, with a significant increase of 47\%.
+It is perhaps not too surprising as cinematic media like Rewinds would provide users with more contextual meanings and retrival cues for semantic processing, as three participants (P4, P6 and P10) have once expressed their contentment after watching Rewinds by claiming ``I recognize the photo now!'' when their initial attempts with static images recognition were fruitless.
 
@@
 \subsubsection{Episodic Memory}
-It could possibly be inferred that participants are likely to benefit more from \textit{Rewind} videos than static street-view images at recalling episodic memory.
-Although participants were not explicitly asked about trip rememberance when presented with static images as opposed to what they were asked after watchiing \textit{Rewind} videos, location rememberance from static images may serve as an upper-bound estimation of how much an individual could recall about a particular trip; since if participants fail to form any cognitive association with the locations depicted in the images, it is very unlikely that they would be able to associate target itineraries with the locations shown.
-Thus, it is perhaps safe to presume that location rememberance with images bounds above the maximum likelihood of trip rememberance with the same images presented to the participants, and we used location rememberance from image recognition as an upper-limit gauge against trip rememberance from \textit{Rewind} videos thereafter.
+It could possibly be inferred that participants are likely to benefit more from Rewinds than static street-view images at recalling episodic memory.
+Although participants were not explicitly asked about trip rememberance when presented with static images as opposed to what they were asked after watchiing Rewinds, location rememberance from static images may serve as an upper-bound estimation of how much an individual could recall about a particular trip; since if participants fail to form any cognitive association with the locations depicted in the images, it is very unlikely that they would be able to associate target itineraries with the locations shown.
+Thus, it is perhaps safe to presume that location rememberance with images bounds above the maximum likelihood of trip rememberance with the same images presented to the participants, and we used location rememberance from image recognition as an upper-limit gauge against trip rememberance from Rewinds thereafter.
 
@@
 % where is home? need to explain this part in system?
-Using the aforementioned presumption, our study examined effects of \textit{Rewind} videos on episodic processing in metric-specific groups, as well as the performance overall.
+Using the aforementioned presumption, our study examined effects of Rewinds videos on episodic processing in metric-specific groups, as well as the performance overall.
 Our study shows that comparing to static street-view images, recollection of event-driven memories using \textit{Rewind} videos is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.
-Our study also suggested that GPS users would benefit more from \textit{Rewind}, even though the difference was mildly significant by an increase about 15\%, $\chi^2(1, N=118) = 2.145$, $p = .0715 (<.1)$.
+Our study also suggested that GPS users would benefit more from Rewinds, even though the difference was mildly significant by an increase about 15\%, $\chi^2(1, N=118) = 2.145$, $p = .0715 (<.1)$.
 % h - prob explain this a little bit more
@@
 This means that it would be more difficult for participants to recall these trips if the provided cues are not effective enough.
-Since \textit{Rewind} videos provide richer and more contextually meaningful cues than static street-side images, it is reasonable that \textit{Rewind} significantly outperforms plain images as suggested by our statistical analysis.
-While being asked about location and trip rememberance on one of his least frequently taken routes, P7 was not able to identify the location from the static image at first; yet he recognized the trip from \textit{Rewind} video as ``one street (in the video) helps me (him) remember".
-%The Effects of Divided Attention on Encoding and Retrieval Processes in Human Memory 
+Since Rewinds provide richer and more contextually meaningful cues than static street-side images, it is reasonable that Rewinds significantly outperforms plain images as suggested by our statistical analysis.
+While being asked about location and trip rememberance on one of his least frequently taken routes, P7 was not able to identify the location from the static image at first; yet he recognized the trip from Rewinds as ``one street (in the video) helps me (him) remember".
+% The Effects of Divided Attention on Encoding and Retrieval Processes in Human Memory 
 % http://www2.psych.ubc.ca/~pgraf/Psy583Readings/Craik%20et%20al%201996.pdf
@@
 P3, a self-identified regular GPS user who had 30\% recalling rate using static images and 80\% trip remembrance rate using Rewinds said ``I really don't pay attention to my surroundings when I'm driving.
-(I am) Focused (focused) on GPS and road"  Under this circumstance, it is almost certain that Rewinds would provide a more successful access to episodic memory as it provides more spatial-temporal cues for memory retrieval, by not only adjusting image attributes to reflect timely and weather changes, but also mimicing the motions of the users when they travel down a particular path.
+(I am) Focused (focused) on GPS and road"  Under this circumstance, it is almost certain that Rewinds would provide a more successful access to episodic memory as it provides more spatial-temporal cues for memory retrieval, not only by adjusting image attributes to reflect timely and weather changes, but also by mimicing the motions of the users\' when they travel down a particular path.
 
-It may appear to be puzzling that participants seem to recall less about specifics of their trips from \textit{Rewind} videos compared to static images when they traveled alone, with a significant decrease around 40\%, $\chi^2(1, N=168) = 33.831$, $p <.01$; when the trips were most frequently taken, with a significant decrease of 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$; and when the trips taken were 10 - 100 meters (33 - 328 feet) away from home, with a mildly significant decrease of 50\%, $\chi^2(1, N=16) = 2.25$, $p <.1$.
+It may appear to be puzzling that participants seem to recall less about specifics of their trips from Rewinds compared to static imageries when they traveled alone, with a significant decrease around 40\%, $\chi^2(1, N=168) = 33.831$, $p <.01$; when the trips were most frequently taken, with a significant decrease of 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$; and when the trips taken were 10 - 100 meters (33 - 328 feet) away from home, with a mildly significant decrease of 50\%, $\chi^2(1, N=16) = 2.25$, $p <.1$.
+One possible reason for this would be it is hard for participants to tie a repeatedly taken trip with a specific instance in time, and trips taken near home could also be the ones that are most frequently taken.
+However, since our study was using location rememberance from images as an upper-limit estimation about participants' trip rememberance from the images, it is also likely that the actual trip rememberance from images could be lower.
 
-It could possibly be inferred that participants are likely to benefit more from \textit{Rewind} videos than static street-view images at recalling episodic memory.
-Although participants were not explicitly asked about trip remembrance when presented with static images, location rememberance from static images may serve as an upper-bound estimation of how much an individual could recall about a particular trip.
-%- tbc
+Overall, trip rememberance from Rewinds is about 4\% higher than that from static street-view images.
+Although chi-squared one-tailed test did not reveal this difference to be statistically significant, $\chi^2(1, N=356) = 0.41$, $p >.1$, we are positive that the actual difference would be more significant since the trip rememberance from images was a best possible estimation from location rememberance.
 

### 2016-09-21 paper/uist_2016/paper.tex
about to work on memorability findings

@@
 Our research questions examine the effectiveness of Rewinds compared to static photos through three virtues of a memory: memorability, believability, and desirability.
-% heather - do we need a reference for the three virtues?
-april - yeah that would be ideal!
+% TODO cite why we choose these three topics
 
-% heather - I changed this part...
-\begin{enumerate}% TODO TODO define semantic vs episodic memory
-\item Memorability: How well do Rewinds facilitate the retrieval of semantic and episodic memory? What types of participants are most likely to recall their memories using Rewinds?
+\begin{enumerate}
+\item Memorability: How well do Rewinds facilitate the retrieval of a memory? What types of participants are most likely to recall their memories using Rewinds?
 \item Believability:  How accurate are Rewinds in the eyes of the participants? 
@@
 \subsection{Participants}
-To recruit a diverse local population, participants for the user study were recruited through online forums (Craigslist classifieds and local Reddit communities) and offline ads, which were posted in cafes and other small businesses in the the city.
+To recruit a diverse local population, participants for the user study were recruited through online forums on Craigslist classifieds and local Reddit communities, and through offline ads, which were posted in cafes and other small businesses in the the city.
 Of the 21 total participants, 13 identified themselves as men and 8 identified themselves as women, with ages ranging from 20 to 50 years old.
 Participants were mainly local residents, with occupations including librarian, medical researcher, office worker, IT consultant, student, musician, and comedian.
-% Jeff notes, comment this out because it's not remarkable
 % A fifth of the participants were undergraduate or graduate students.
@@
 At the beginning of the study, participants were asked to identify their gender, whether they considered themselves a frequent traveler, and whether they tended to use GPS in places they were already familiar with.
-Then, questions about the photos and Rewinds investigated their memorability, believability, and desirability.
+Then, questions were asked about photos and Rewinds to evaluate their memorability, believability, and desirability.
 
-%Participants who used GPS in familiar locations were considered regular GPS users, and participants who did not were considered non-regular GPS users.
 For each photo-Rewind pair, the participant was first shown a photo of one of the locations found in their geolocation data.
@@
 
-% heather - Rewind of the trip or Rewind video of the trip? april - we say 'rewind' when we mean rewind video, and if we want to refer to the system, we say 'the rewind system'
 The participant was then shown a Rewind of the trip that they were on when the location in the photo was encountered.
@@
 
-% heather - ...that they did not carry the device on their person. - grammatical error? april - nope (maybe out of fashion now though?), their person = their body
 Data from three participants were not included in the results of this study.
@@
 \section{Findings}
-The findings of our user study center on the participants’ relationship to the Rewinds generated from their location data compared to the static photos.
+The findings of our user study center on the participants’ relationships to the Rewinds generated from their location data compared to the static photos.
 We focus on the participants’ judgments of their Rewinds’ memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds.
@@
 
-% heather - where to put this part or do we need a summary like this at all?
-% april - moved to findings section from user study section
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Our user study explored the following five metrics as potentially having an effect on memorability, believability, or desirability of digital memory media:
@@
 We showed locations that were either ``most frequently visited,'' ``least frequently visited,'' or randomly selected.
-	\item GPS usage: do participants who use GPS navigation regularly react differently to Rewinds and static photos compared to participants who don't use GPS navigation regularly?
+	\item Companions: how does the presence of a traveling companion affect the participant's attitude toward Rewinds or static photos?
 	\item Traveler type: do attitudes toward Rewinds and static photos differ depending on whether the participant identifies as a frequent traveler?
-	\item Companions: how does the presence of a traveling companion affect the participant's attitude toward Rewinds or static photos?
+	\item GPS usage: do participants who are regular users of GPS navigation react differently to Rewinds and static photos compared to participants who don't use GPS navigation regularly?
 \end{enumerate}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsection{Within-subject study}
+% TODO explain tables
+\begin{table*}[t]
+	\centering
+	\caption{My caption}
+	\small
+	\label{within-subject-table}
+	\begin{tabular}{c|c|c|c|c|c|c|c|c|}
+		\cline{2-9}
+		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Belivability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
+		& \begin{tabular}[c]{@{}c@{}}video\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}video\\ trip\end{tabular} & photo & video & photo & video \\ \hline
+		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
+		\multicolumn{1}{|c|}{\%} & 96.61\% & \multicolumn{2}{c|}{49.72\%} & 53.67\% & 77.91\% & 79.69\% & 10.61\% & 14.69\% \\ \hline
+		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
+	\end{tabular}
+\end{table*}
+
+% 2nd table %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table*}[t]
+	\centering
+	\caption{My caption}
+	\begin{adjustbox}{width=1\textwidth}
+		\small
+		\label{between-subject-table}
+		\begin{tabular}{ccccccccccccccccc}
+			\cline{4-17}
+			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{2}{c|}{GPS usage}                                                                                       & \multicolumn{2}{c|}{Traveller type}                                                                                  & \multicolumn{2}{c|}{Companions}                                                                                               & \multicolumn{6}{c|}{Distance}                                                                                                                                                                                                                                                                                                            & \multicolumn{2}{c|}{Visit frequency}                                                                                 \\ \cline{4-17}
+			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{1}{c|}{GPS user}                             & \multicolumn{1}{c|}{non-GPS user}                        & \multicolumn{1}{c|}{Frequent}                             & \multicolumn{1}{c|}{Non-frequent}                        & \multicolumn{1}{c|}{Alone}                                     & \multicolumn{1}{c|}{Not alone}                              & \multicolumn{1}{c|}{0}                                & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{2}                               & \multicolumn{1}{c|}{3}                               & \multicolumn{1}{c|}{4}                               & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{Most}                                 & \multicolumn{1}{c|}{Least}                               \\ \hline
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}60}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}74}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}47}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81}          \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}33.33\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57.98\%}     & \multicolumn{1}{c|}{50.83\%}                              & \multicolumn{1}{c|}{47.46\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}55.00\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.22\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}43.66\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}51.56\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.34\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}35.80\%}     \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{l|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$\\ p =0.0016\end{tabular}}  & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$\\ p = 0.3953\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 31.812$\\ p \textless0.0001\end{tabular}}  & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$\\ p = 0.0028\end{tabular}}                                                                                                                                                                                                                   & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$\\ p = 0.0001\end{tabular}} \\ \cline{2-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{58}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{57}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{64}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{48.28\%}                              & \multicolumn{1}{c|}{56.30\%}                             & \multicolumn{1}{c|}{53.33\%}                              & \multicolumn{1}{c|}{54.39\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}61.70\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89.74\%}        & \multicolumn{1}{c|}{60.00\%}                          & \multicolumn{1}{c|}{25.00\%}                         & \multicolumn{1}{c|}{55.56\%}                         & \multicolumn{1}{c|}{59.15\%}                         & \multicolumn{1}{c|}{50.00\%}                         & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{52.17\%}                              & \multicolumn{1}{c|}{56.25\%}                             \\ \cline{3-17}
+			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Memorability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$\\ p =0.1992\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$\\ p = 0.4478\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,  133) = 9.016$\\ p = 0.0013\end{tabular}}        & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$\\ p = 0.4467\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$\\ p =  0.3987\end{tabular}}                        \\ \hline
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{19}                                   & \multicolumn{1}{c|}{67}                                  & \multicolumn{1}{c|}{61}                                   & \multicolumn{1}{c|}{25}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{13}                              & \multicolumn{1}{c|}{30}                              & \multicolumn{1}{c|}{32}                              & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}34}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}27}          \\ \cline{3-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{68.42\%}                              & \multicolumn{1}{c|}{80.60\%}                             & \multicolumn{1}{c|}{77.05\%}                              & \multicolumn{1}{c|}{80.00\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81.69\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.00\%}        & \multicolumn{1}{c|}{80.00\%}                          & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{69.23\%}                         & \multicolumn{1}{c|}{90.00\%}                         & \multicolumn{1}{c|}{75.00\%}                         & \multicolumn{1}{c|}{0.00\%}                          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70.59\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88.89\%}     \\ \cline{3-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$\\ p = 0.2073\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$\\ p = 0.4947\end{tabular}}                          & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 20.956$\\ p \textless 0.0001\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$\\ p= 0.1709\end{tabular}}                                                                                                                                                                                                                                               & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$\\ p =0.078\end{tabular}}    \\ \cline{2-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}91}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}37}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}53}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}49}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}6}       & \multicolumn{1}{c|}{33}                                   & \multicolumn{1}{c|}{58}                                  \\ \cline{3-17}
+			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}69.23\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}84.27\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}85.71\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.86\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.09\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}71.79\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.91\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}79.59\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}33.33\%} & \multicolumn{1}{c|}{69.70\%}                              & \multicolumn{1}{c|}{81.03\%}                             \\ \cline{3-17}
+			\multicolumn{1}{|l|}{\multirow{-6}{*}{\rotatebox{90}{Believability}}} & \multicolumn{1}{l|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$\\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$\\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$\\ p =0.086\end{tabular}}           & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$\\ p = 0.0726\end{tabular}}                                                                                                                                                                                                                    & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$\\ p = 0.1647\end{tabular}}                          \\ \hline
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{60}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{74}                                        & \multicolumn{1}{c|}{20}                                     & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{67}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{47}                                   & \multicolumn{1}{c|}{81}                                  \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{13.33\%}                              & \multicolumn{1}{c|}{9.24\%}                              & \multicolumn{1}{c|}{12.50\%}                              & \multicolumn{1}{c|}{6.78\%}                              & \multicolumn{1}{c|}{12.16\%}                                   & \multicolumn{1}{c|}{10.00\%}                                & \multicolumn{1}{c|}{20.00\%}                          & \multicolumn{1}{c|}{37.50\%}                         & \multicolumn{1}{c|}{5.56\%}                          & \multicolumn{1}{c|}{7.04\%}                          & \multicolumn{1}{c|}{13.43\%}                         & \multicolumn{1}{c|}{10.00\%}                         & \multicolumn{1}{c|}{14.89\%}                              & \multicolumn{1}{c|}{9.88\%}                              \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$\\ p = 0.2804\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$\\ p = 0.3948\end{tabular}}                                  & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$\\ p = 0.1492\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$\\ p = 0.2858\end{tabular}}                           \\ \cline{2-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}58}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}120}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}66}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10}      & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17}
+			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.86\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}9.24\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20.83\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}1.75\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12.77\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}25.64\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}   & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}11.11\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}19.70\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}40.00\%} & \multicolumn{1}{c|}{10.87\%}                              & \multicolumn{1}{c|}{17.50\%}                             \\ \cline{3-17}
+			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Desirability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$\\ p = 0.0034\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$\\ p = 0.059\end{tabular}}          & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$\\ p= 0.0729\end{tabular}}                                                                                                                                                                                                                     & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$\\ p = 0.2288\end{tabular}}                         \\ \hline
+		\end{tabular}
+	\end{adjustbox}
+\end{table*}
+
+\section{Memorability}
+Rewinds, and digitally-mediated memories in general, are meant to engage a person's memory.
+To find out what features make a digital memory memorable, we examined participant responses to whether or not they were able to remember the location shown in a photo (semantic memory) or recall the trip portrayed by a Rewind (episodic memory).
+Photo memorability is determined by whether or not the participant remembered the location depicted in a photo.
+Because a Rewind contains many locations, it would be unfair to consider the memorability of Rewind based on whether the participant remembers any locations in the Rewind.
+So, Rewind memorability is determined by whether or not the participant remembered and could distinguish the particular trip portrayed in a Rewind.
+In this section, we will look at differences in photo and Rewind memorability based on the five metrics discussed.
+
 \subsubsection{Semantic Memory} 
@@
 
-\subsection{Between-Subject Study}
-%%UPDATE BOTH TABLES AND ADD ONE MORE%%%
-%%%%%%%%%%%percentage to decimal
-\begin{table*}[t]
-	\centering
-	\caption{My caption}
-	\small
-	\label{within-subject-table}
-	\begin{tabular}{c|c|c|c|c|c|c|c|c|}
-		\cline{2-9}
-		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Belivability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
-		& \begin{tabular}[c]{@{}c@{}}video\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}video\\ trip\end{tabular} & photo & video & photo & video \\ \hline
-		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
-		\multicolumn{1}{|c|}{\%} & 96.61\% & \multicolumn{2}{c|}{49.72\%} & 53.67\% & 77.91\% & 79.69\% & 10.61\% & 14.69\% \\ \hline
-		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
-	\end{tabular}
-\end{table*}
-% 2nd table %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{table*}[t]
-	\centering
-	\caption{My caption}
-	\begin{adjustbox}{width=1\textwidth}
-		\small
-		\label{between-subject-table}
-		\begin{tabular}{ccccccccccccccccc}
-			\cline{4-17}
-			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{2}{c|}{GPS usage}                                                                                       & \multicolumn{2}{c|}{Traveller type}                                                                                  & \multicolumn{2}{c|}{Companions}                                                                                               & \multicolumn{6}{c|}{Distance}                                                                                                                                                                                                                                                                                                            & \multicolumn{2}{c|}{Visit frequency}                                                                                 \\ \cline{4-17}
-			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{1}{c|}{GPS user}                             & \multicolumn{1}{c|}{non-GPS user}                        & \multicolumn{1}{c|}{Frequent}                             & \multicolumn{1}{c|}{Non-frequent}                        & \multicolumn{1}{c|}{Alone}                                     & \multicolumn{1}{c|}{Not alone}                              & \multicolumn{1}{c|}{0}                                & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{2}                               & \multicolumn{1}{c|}{3}                               & \multicolumn{1}{c|}{4}                               & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{Most}                                 & \multicolumn{1}{c|}{Least}                               \\ \hline
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}60}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}74}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}47}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81}          \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}33.33\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57.98\%}     & \multicolumn{1}{c|}{50.83\%}                              & \multicolumn{1}{c|}{47.46\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}55.00\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.22\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}43.66\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}51.56\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.34\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}35.80\%}     \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{l|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$\\ p =0.0016\end{tabular}}  & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$\\ p = 0.3953\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 31.812$\\ p \textless0.0001\end{tabular}}  & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$\\ p = 0.0028\end{tabular}}                                                                                                                                                                                                                   & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$\\ p = 0.0001\end{tabular}} \\ \cline{2-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{58}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{57}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{64}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{48.28\%}                              & \multicolumn{1}{c|}{56.30\%}                             & \multicolumn{1}{c|}{53.33\%}                              & \multicolumn{1}{c|}{54.39\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}61.70\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89.74\%}        & \multicolumn{1}{c|}{60.00\%}                          & \multicolumn{1}{c|}{25.00\%}                         & \multicolumn{1}{c|}{55.56\%}                         & \multicolumn{1}{c|}{59.15\%}                         & \multicolumn{1}{c|}{50.00\%}                         & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{52.17\%}                              & \multicolumn{1}{c|}{56.25\%}                             \\ \cline{3-17}
-			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Memorability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$\\ p =0.1992\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$\\ p = 0.4478\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,  133) = 9.016$\\ p = 0.0013\end{tabular}}        & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$\\ p = 0.4467\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$\\ p =  0.3987\end{tabular}}                        \\ \hline
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{19}                                   & \multicolumn{1}{c|}{67}                                  & \multicolumn{1}{c|}{61}                                   & \multicolumn{1}{c|}{25}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{13}                              & \multicolumn{1}{c|}{30}                              & \multicolumn{1}{c|}{32}                              & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}34}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}27}          \\ \cline{3-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{68.42\%}                              & \multicolumn{1}{c|}{80.60\%}                             & \multicolumn{1}{c|}{77.05\%}                              & \multicolumn{1}{c|}{80.00\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81.69\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.00\%}        & \multicolumn{1}{c|}{80.00\%}                          & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{69.23\%}                         & \multicolumn{1}{c|}{90.00\%}                         & \multicolumn{1}{c|}{75.00\%}                         & \multicolumn{1}{c|}{0.00\%}                          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70.59\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88.89\%}     \\ \cline{3-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$\\ p = 0.2073\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$\\ p = 0.4947\end{tabular}}                          & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 20.956$\\ p \textless 0.0001\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$\\ p= 0.1709\end{tabular}}                                                                                                                                                                                                                                               & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$\\ p =0.078\end{tabular}}    \\ \cline{2-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}91}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}37}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}53}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}49}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}6}       & \multicolumn{1}{c|}{33}                                   & \multicolumn{1}{c|}{58}                                  \\ \cline{3-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}69.23\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}84.27\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}85.71\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.86\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.09\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}71.79\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.91\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}79.59\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}33.33\%} & \multicolumn{1}{c|}{69.70\%}                              & \multicolumn{1}{c|}{81.03\%}                             \\ \cline{3-17}
-			\multicolumn{1}{|l|}{\multirow{-6}{*}{\rotatebox{90}{Believability}}} & \multicolumn{1}{l|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$\\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$\\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$\\ p =0.086\end{tabular}}           & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$\\ p = 0.0726\end{tabular}}                                                                                                                                                                                                                    & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$\\ p = 0.1647\end{tabular}}                          \\ \hline
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{60}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{74}                                        & \multicolumn{1}{c|}{20}                                     & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{67}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{47}                                   & \multicolumn{1}{c|}{81}                                  \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{13.33\%}                              & \multicolumn{1}{c|}{9.24\%}                              & \multicolumn{1}{c|}{12.50\%}                              & \multicolumn{1}{c|}{6.78\%}                              & \multicolumn{1}{c|}{12.16\%}                                   & \multicolumn{1}{c|}{10.00\%}                                & \multicolumn{1}{c|}{20.00\%}                          & \multicolumn{1}{c|}{37.50\%}                         & \multicolumn{1}{c|}{5.56\%}                          & \multicolumn{1}{c|}{7.04\%}                          & \multicolumn{1}{c|}{13.43\%}                         & \multicolumn{1}{c|}{10.00\%}                         & \multicolumn{1}{c|}{14.89\%}                              & \multicolumn{1}{c|}{9.88\%}                              \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$\\ p = 0.2804\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$\\ p = 0.3948\end{tabular}}                                  & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$\\ p = 0.1492\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$\\ p = 0.2858\end{tabular}}                           \\ \cline{2-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}58}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}120}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}66}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10}      & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.86\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}9.24\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20.83\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}1.75\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12.77\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}25.64\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}   & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}11.11\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}19.70\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}40.00\%} & \multicolumn{1}{c|}{10.87\%}                              & \multicolumn{1}{c|}{17.50\%}                             \\ \cline{3-17}
-			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Desirability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$\\ p = 0.0034\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$\\ p = 0.059\end{tabular}}          & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$\\ p= 0.0729\end{tabular}}                                                                                                                                                                                                                     & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$\\ p = 0.2288\end{tabular}}                         \\ \hline
-		\end{tabular}
-	\end{adjustbox}
-\end{table*}
-
 % shall we change photo/rewind video rememberance to location/trip rememberance?
@@
 \subsection{Memorability}
-Rewinds, and digitally-mediated memories in general, are meant to engage a person's memory.
-To find out what features make a digital memory memorable, we examined participant responses to whether or not they were able to remember the location shown in a photo (semantic memory) or recall the trip portrayed by a Rewind (episodic memory).
-Photo memorability is determined by whether or not the participant remembered the location depicted in a photo.
-Because a Rewind contains many locations, it would be unfair to consider the memorability of Rewind based on whether the participant remembers any locations in the Rewind.
-So, Rewind memorability is determined by whether or not the participant remembered and could distinguish the particular trip portrayed in a Rewind.
-In this section, we will look at differences in photo and Rewind memorability based on the five metrics discussed previously.
 

### 2016-09-21 paper/uist_2016/paper.tex
memorability 1/6

@@
 Photo memorability is determined by whether or not the participant remembered the location depicted in a photo.
-Because a Rewind contains many locations, it would be unfair to consider the memorability of Rewind based on whether the participant remembers any locations in the Rewind.
+Because a Rewind contains many locations, it would be unfair to evaluate the memorability of Rewind based on whether the participant remembers any locations in the Rewind.
+If participants do not recognize some depicted locations, they still have many other chances to pick out locations they remember.
 So, Rewind memorability is determined by whether or not the participant remembered and could distinguish the particular trip portrayed in a Rewind.
-In this section, we will look at differences in photo and Rewind memorability based on the five metrics discussed.
+In this section, we will look at differences in photo and Rewind memorability based on the five metrics discussed previously.
 
-\subsubsection{Semantic Memory} 
-Within-subject comparison in our study reveals that participants are significantly better at recalling semantic memory of a particular location with \textit{Rewind} videos than with static street-view images, $\chi^2(1, N=356) = 96.987$, $p <.01$.
-When being presented with a street-side image retrieved based on their location data, participants were able to recognize places visited 50\% of the time; yet recognition rate of locations reached 97\% when participants started playing accompanied Rewinds, with a significant increase of 47\%.
-It is perhaps not too surprising as cinematic media like Rewinds would provide users with more contextual meanings and retrival cues for semantic processing, as three participants (P4, P6 and P10) have once expressed their contentment after watching Rewinds by claiming ``I recognize the photo now!'' when their initial attempts with static images recognition were fruitless.
+\subsubsection{Rewinds vs. Static Photos} 
+Our study reveals that participants have higher semantic memory of locations when presented with Rewinds than with static street-view photos ($\chi^2(1, N=356) = 96.987$, $p <.01$).
+When presented with a street-view photo generated from the participant's location data, participants were able to recognize the depicted location 49.7\% of the time.
+Recognition rate of locations reached 96.6\% when participants were shown the accompanying Rewind.
+As discussed above, this can be expected because cinematic media like Rewinds provide more context and retrieval cues.
+Three participants (P4, P6, and P10) who were unable to recall a location from a static photo actually recognized the location after seeing the accompanying Rewind.
+They expressed their contentment after watching the Rewind, proclaiming ``I recognize the photo now!'' When we evaluate Rewind memorability based on episodic memory rather than semantic memory, the results show that participants recalled the exact trip depicted by the Rewind 53.7\% of the time.
+%TODO make sure episodic memory is discussed in discussion section--visit frequency diminishes episodic memory
 
-%
-\subsubsection{Episodic Memory}
-It could possibly be inferred that participants are likely to benefit more from Rewinds than static street-view images at recalling episodic memory.
-Although participants were not explicitly asked about trip rememberance when presented with static images as opposed to what they were asked after watchiing Rewinds, location rememberance from static images may serve as an upper-bound estimation of how much an individual could recall about a particular trip; since if participants fail to form any cognitive association with the locations depicted in the images, it is very unlikely that they would be able to associate target itineraries with the locations shown.
-Thus, it is perhaps safe to presume that location rememberance with images bounds above the maximum likelihood of trip rememberance with the same images presented to the participants, and we used location rememberance from image recognition as an upper-limit gauge against trip rememberance from Rewinds thereafter.
-
-% h - add another table, only abt memorability tho
-% explain distance groups in the beginning
-% where is home? need to explain this part in system?
-Using the aforementioned presumption, our study examined effects of Rewinds videos on episodic processing in metric-specific groups, as well as the performance overall.
-Our study shows that comparing to static street-view images, recollection of event-driven memories using \textit{Rewind} videos is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.
-Our study also suggested that GPS users would benefit more from Rewinds, even though the difference was mildly significant by an increase about 15\%, $\chi^2(1, N=118) = 2.145$, $p = .0715 (<.1)$.
-% h - prob explain this a little bit more
-
-One plausible explanation of the improvement may be inherent to the encoding of episodic memory in the first place.
-As suggested by the levels-of-processing theory(ref), encoding efficacy is heavily dependent on the levels to which stimuli are being actively or passively processed.
-Not surprisingly, superficial mental engagement would produce weaker, and less enduring cognitive representation which would demand more contextually accurate and abundant cues for memory triggery, and vice versa.
-Oftentimes, the cognitive representation resulted from shallow processing may not even be retrievable at all as it is simply not available for retrieval.
-As previously described, both of the trips revealed in our results, those that were taken farthest away from home and those that were least frequently taken, may not be special enough to engage deep memory encoding nor often enough to reinforce incidental remembrance.
-This means that it would be more difficult for participants to recall these trips if the provided cues are not effective enough.
-Since Rewinds provide richer and more contextually meaningful cues than static street-side images, it is reasonable that Rewinds significantly outperforms plain images as suggested by our statistical analysis.
-While being asked about location and trip rememberance on one of his least frequently taken routes, P7 was not able to identify the location from the static image at first; yet he recognized the trip from Rewinds as ``one street (in the video) helps me (him) remember".
-% The Effects of Divided Attention on Encoding and Retrieval Processes in Human Memory 
-% http://www2.psych.ubc.ca/~pgraf/Psy583Readings/Craik%20et%20al%201996.pdf
-% Craik et al. 1996
-
-The extent to which attention is dedicated while taking a trip may be another possible explanation for the observed improvement using Rewinds.
-This is perhaps particularly applicable to explain why participants who were self-identified regular GPS users tend to benefit more from Rewinds with episodic memory recalling.
-Laboratory work done by Craik et al.
-1996 (ref) has demonstrated that the encoding of memory is more effective under full-attention conditions than divided-attention conditions.
-This means that regular GPS users, who are often directed step-by-step on how to navigate through their environments, may be less likely to engage their attention while taking their routes, leading to less available cognitive representation for retrieval.
-P3, a self-identified regular GPS user who had 30\% recalling rate using static images and 80\% trip remembrance rate using Rewinds said ``I really don't pay attention to my surroundings when I'm driving.
-(I am) Focused (focused) on GPS and road"  Under this circumstance, it is almost certain that Rewinds would provide a more successful access to episodic memory as it provides more spatial-temporal cues for memory retrieval, not only by adjusting image attributes to reflect timely and weather changes, but also by mimicing the motions of the users\' when they travel down a particular path.
-
-It may appear to be puzzling that participants seem to recall less about specifics of their trips from Rewinds compared to static imageries when they traveled alone, with a significant decrease around 40\%, $\chi^2(1, N=168) = 33.831$, $p <.01$; when the trips were most frequently taken, with a significant decrease of 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$; and when the trips taken were 10 - 100 meters (33 - 328 feet) away from home, with a mildly significant decrease of 50\%, $\chi^2(1, N=16) = 2.25$, $p <.1$.
-One possible reason for this would be it is hard for participants to tie a repeatedly taken trip with a specific instance in time, and trips taken near home could also be the ones that are most frequently taken.
-However, since our study was using location rememberance from images as an upper-limit estimation about participants' trip rememberance from the images, it is also likely that the actual trip rememberance from images could be lower.
-
-Overall, trip rememberance from Rewinds is about 4\% higher than that from static street-view images.
-Although chi-squared one-tailed test did not reveal this difference to be statistically significant, $\chi^2(1, N=356) = 0.41$, $p >.1$, we are positive that the actual difference would be more significant since the trip rememberance from images was a best possible estimation from location rememberance.
-
-\subsubsection{Believability and Desirability}
-Although not statistically significant, %TODO TODO TODO TODO TODO
-
-% shall we change photo/rewind video rememberance to location/trip rememberance?
-april - i define photo/rewind remembrance below.
-a photo and a rewind can have both location and trip remembrance.
-for instance from a photo you might remember the location but not the trip.
-\subsection{Memorability}
-
-%TODO heather - didn't do the stats for video location vs photo locations, not sure if it is necessary? - photo vs video stats?
-%TODO will add this part back in within-group comparison
-
-% \subsubsection{Rewinds versus Photos}
-% When participants were shown a street side photo from their location history, they were asked whether they recognized the location in the photo.
-In 50\% of cases, participants said they did.
-When they were shown the Rewind associated with that photo, nearly every case had recognizable locations---97\%.
-This result is expected since Rewinds contain more location information than static photos, so if participants do not recognize some depicted locations, they still have many other chances to pick out locations they remember.
-Rewind memorability as calculated by whether participants could identify the particular trip they were on from watching the Rewind was 54\%.
-However, there were cases where the participant would only remember the photo after seeing its accompanying Rewind, which provided a context.
-More than one participant exclaimed after watching a Rewind, ``I recognize the photo now!''
-
+%TODO h - add another table, only abt memorability tho
+%TODO  where is home? need to explain this part in system? make sure this is explained
 \subsubsection{Distance}
@@
 
+Our study examined episodic processing in metric-specific groups, as well as the performance overall.
+Our study shows that comparing to static street-view images, recollection of event-driven memories using \textit{Rewind} videos is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.
+
 \subsubsection{GPS Usage}
+Our study also suggested that GPS users would benefit more from Rewinds, even though the difference was mildly significant by an increase about 15\%, $\chi^2(1, N=118) = 2.145$, $p = .0715 (<.1)$. 
+% h - prob explain this a little bit more
+
 % Our findings show that GPS usage significantly affect the rememberance of locations $\chi^2(1,179) = 8.734$, p < 0.01, but does not impose a siginificant effect on trip rememberance.
@@
 
+%TODO where to put this????  maybe split discussion into three sections on mem/believ/desir
+\subsubsection{Episodic Memory}
+It could possibly be inferred that participants are likely to benefit more from Rewinds than static street-view images at recalling episodic memory.
+Although participants were not explicitly asked about trip rememberance when presented with static images as opposed to what they were asked after watchiing Rewinds, location rememberance from static images may serve as an upper-bound estimation of how much an individual could recall about a particular trip; since if participants fail to form any cognitive association with the locations depicted in the images, it is very unlikely that they would be able to associate target itineraries with the locations shown.
+Thus, it is perhaps safe to presume that location rememberance with images bounds above the maximum likelihood of trip rememberance with the same images presented to the participants, and we used location rememberance from image recognition as an upper-limit gauge against trip rememberance from Rewinds thereafter.
+
+One plausible explanation of the improvement may be inherent to the encoding of episodic memory in the first place.
+As suggested by the levels-of-processing theory(ref), encoding efficacy is heavily dependent on the levels to which stimuli are being actively or passively processed.
+Not surprisingly, superficial mental engagement would produce weaker, and less enduring cognitive representation which would demand more contextually accurate and abundant cues for memory triggery, and vice versa.
+Oftentimes, the cognitive representation resulted from shallow processing may not even be retrievable at all as it is simply not available for retrieval.
+As previously described, both of the trips revealed in our results, those that were taken farthest away from home and those that were least frequently taken, may not be special enough to engage deep memory encoding nor often enough to reinforce incidental remembrance.
+This means that it would be more difficult for participants to recall these trips if the provided cues are not effective enough.
+Since Rewinds provide richer and more contextually meaningful cues than static street-side images, it is reasonable that Rewinds significantly outperforms plain images as suggested by our statistical analysis.
+While being asked about location and trip rememberance on one of his least frequently taken routes, P7 was not able to identify the location from the static image at first; yet he recognized the trip from Rewinds as ``one street (in the video) helps me (him) remember".
+% The Effects of Divided Attention on Encoding and Retrieval Processes in Human Memory 
+% http://www2.psych.ubc.ca/~pgraf/Psy583Readings/Craik%20et%20al%201996.pdf
+% Craik et al. 1996
+
+The extent to which attention is dedicated while taking a trip may be another possible explanation for the observed improvement using Rewinds.
+This is perhaps particularly applicable to explain why participants who were self-identified regular GPS users tend to benefit more from Rewinds with episodic memory recalling.
+Laboratory work done by Craik et al.
+1996 (ref) has demonstrated that the encoding of memory is more effective under full-attention conditions than divided-attention conditions.
+This means that regular GPS users, who are often directed step-by-step on how to navigate through their environments, may be less likely to engage their attention while taking their routes, leading to less available cognitive representation for retrieval.
+P3, a self-identified regular GPS user who had 30\% recalling rate using static images and 80\% trip remembrance rate using Rewinds said ``I really don't pay attention to my surroundings when I'm driving.
+(I am) Focused (focused) on GPS and road"  Under this circumstance, it is almost certain that Rewinds would provide a more successful access to episodic memory as it provides more spatial-temporal cues for memory retrieval, not only by adjusting image attributes to reflect timely and weather changes, but also by mimicing the motions of the users\' when they travel down a particular path.
+
+It may appear to be puzzling that participants seem to recall less about specifics of their trips from Rewinds compared to static imageries when they traveled alone, with a significant decrease around 40\%, $\chi^2(1, N=168) = 33.831$, $p <.01$; when the trips were most frequently taken, with a significant decrease of 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$; and when the trips taken were 10 - 100 meters (33 - 328 feet) away from home, with a mildly significant decrease of 50\%, $\chi^2(1, N=16) = 2.25$, $p <.1$.
+One possible reason for this would be it is hard for participants to tie a repeatedly taken trip with a specific instance in time, and trips taken near home could also be the ones that are most frequently taken.
+However, since our study was using location rememberance from images as an upper-limit estimation about participants' trip rememberance from the images, it is also likely that the actual trip rememberance from images could be lower.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% end where to put this???
+
 There are some inherent limitations to Rewind due to today's technologies.

### 2016-09-21 paper/uist_2016/paper.tex
memorability 2/6 distance

@@
 % 0 - 100%, 1 - 75%, 2 - 72%, 3 - 44%, 4 - 52%, 5 - 10%, $\chi^2(5,179) = 18.106$, p < 0.01
-The distance away from the participant’s home had differing effects on photo memorability and Rewind memorability (Figure~\ref{fig:distancememory}).
+The depicted location's distance away from the participant’s home had differing effects on photo memorability and Rewind memorability.
+Photo memorability and distance had a clearly linear relationship, while the relationship between Rewind memorability and distance was more nuanced.
 
-Photo memorability and distance had a clear linear relationship.
-As the distance increased, photo memorability decreased, suggesting that locations further away from home were less likely to be remembered.
-Remembrance was 100\% for Distance Group 0, or home.
-One participant recognized a photo because her ``husband's car is in the driveway.'' Remembrance dropped to 75\% for Distance Group 1, then down to 10\% for Distance Group 5, which represented the locations furthest away from home.
+For photos, as the distance increased, memorability decreased, suggesting that locations further away from home were less likely to be remembered.
+In Distance Group 0, or the participant's home location, location recall was 100\%.
+One participant, upon recognition, explained that she knew the location because ``my husband's car is in the driveway.'' Further away in Distance Group 1, remembrance dropped to 75\%, then later down to 10\% for Distance Group 5, which represented the locations furthest away from home.
 These percentages are statistically significant, with a p-value of 0.0028.
 
-There was no statistical significance for Rewind remembrance.
-Our data does show, however, that Rewind remembrance was largely the same for most distance groups, except for distances that were close to home.
-While remembrance for almost all distance groups was on average near 60\%, remembrance for Rewinds in Distance Group 1 was 25\%.
-This data suggests that participants often did not remember or could not distinguish the exact trips occurring in locations close to their home, where most trips happen.
+%TODO find citation that humans travel most within x km of their home/work nodes
+%TODO memory competition--similar memories compete for significance
+For Rewind memorability, there was no statistical significance.
+Our data does show, however, that Rewind remembrance was largely the same for most distance groups, except for distances that were close to home in Distance Group 1.
+While remembrance for all distance groups was between 50-60\%, remembrance for Rewinds in Distance Group 1 was 25\%.
+This data suggests that participants often did not remember or could not distinguish the exact trips that occurred in locations close to their home.
+This is where most trips happen, and therefore competition between similar memories would make it harder for a person to distinguish the specific trip they were on that generated the Rewind.
+
+\subsubsection{Visit Frequency}
+% only affect location rememberance
+% trip rememberance $\chi^2(1,126) = 0.066$, p = 0.3987 (> 0.05)
+% most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
+Location memorability and trip memorability are affected differently by frequency of visits (Figure~\ref{fig:frequencymemory}).
+Location memorability is highest for places that are most frequently visited by the participant, while trip memorability is highest for places that are least frequently visited.
+The more frequently a place was visited, the more likely it was that the participant remembered the location when it was shown to them at the study.
+In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places, with a significance at $\chi^2(1,128) = 14.458$, p < 0.01.
+This effect does not occur for trip memorability.
+In the most frequently visited places, trips are remembered 51\% of the time.
+Instead of seeing trip memorability decrease for least frequently visited places, this factor increases to 56\%.
 
@@
 
-\subsubsection{Visit Frequency}
-% only affect location rememberance
-% trip rememberance $\chi^2(1,126) = 0.066$, p = 0.3987 (> 0.05)
-% most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
-Location memorability and trip memorability are affected differently by frequency of visits (Figure~\ref{fig:frequencymemory}).
-Location memorability is highest for places that are most frequently visited by the participant, while trip memorability is highest for places that are least frequently visited.
-The more frequently a place was visited, the more likely it was that the participant remembered the location when it was shown to them at the study.
-In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places, with a significance at $\chi^2(1,128) = 14.458$, p < 0.01.
-This effect does not occur for trip memorability.
-In the most frequently visited places, trips are remembered 51\% of the time.
-Instead of seeing trip memorability decrease for least frequently visited places, this factor increases to 56\%.
-
 % \begin{figure}
@@
 % \end{figure}
-
-\subsubsection{Other Variables}
-% needs to be filled?
 

### 2016-09-21 paper/uist_2016/paper.tex
fixed some values in the table; % -> number

@@
 		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
-		\multicolumn{1}{|c|}{\%} & 96.61\% & \multicolumn{2}{c|}{49.72\%} & 53.67\% & 77.91\% & 79.69\% & 10.61\% & 14.69\% \\ \hline
+		\multicolumn{1}{|c|}{\%} & 0.97 & \multicolumn{2}{c|}{0.50} & 0.54 & 0.78 & 0.80 & 0.11 & 0.15 \\ \hline
 		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
@@
 		\label{between-subject-table}
-		\begin{tabular}{ccccccccccccccccc}
+\begin{tabular}{ccc|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
 \cline{4-17}
-			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{2}{c|}{GPS usage}                                                                                       & \multicolumn{2}{c|}{Traveller type}                                                                                  & \multicolumn{2}{c|}{Companions}                                                                                               & \multicolumn{6}{c|}{Distance}                                                                                                                                                                                                                                                                                                            & \multicolumn{2}{c|}{Visit frequency}                                                                                 \\ \cline{4-17}
-			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{1}{c|}{GPS user}                             & \multicolumn{1}{c|}{non-GPS user}                        & \multicolumn{1}{c|}{Frequent}                             & \multicolumn{1}{c|}{Non-frequent}                        & \multicolumn{1}{c|}{Alone}                                     & \multicolumn{1}{c|}{Not alone}                              & \multicolumn{1}{c|}{0}                                & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{2}                               & \multicolumn{1}{c|}{3}                               & \multicolumn{1}{c|}{4}                               & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{Most}                                 & \multicolumn{1}{c|}{Least}                               \\ \hline
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}60}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}74}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}47}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81}          \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}33.33\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57.98\%}     & \multicolumn{1}{c|}{50.83\%}                              & \multicolumn{1}{c|}{47.46\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}55.00\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.22\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}43.66\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}51.56\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.34\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}35.80\%}     \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{l|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$\\ p =0.0016\end{tabular}}  & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$\\ p = 0.3953\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 31.812$\\ p \textless0.0001\end{tabular}}  & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$\\ p = 0.0028\end{tabular}}                                                                                                                                                                                                                   & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$\\ p = 0.0001\end{tabular}} \\ \cline{2-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{58}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{57}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{64}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{48.28\%}                              & \multicolumn{1}{c|}{56.30\%}                             & \multicolumn{1}{c|}{53.33\%}                              & \multicolumn{1}{c|}{54.39\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}61.70\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89.74\%}        & \multicolumn{1}{c|}{60.00\%}                          & \multicolumn{1}{c|}{25.00\%}                         & \multicolumn{1}{c|}{55.56\%}                         & \multicolumn{1}{c|}{59.15\%}                         & \multicolumn{1}{c|}{50.00\%}                         & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{52.17\%}                              & \multicolumn{1}{c|}{56.25\%}                             \\ \cline{3-17}
-			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Memorability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$\\ p =0.1992\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$\\ p = 0.4478\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,  133) = 9.016$\\ p = 0.0013\end{tabular}}        & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$\\ p = 0.4467\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$\\ p =  0.3987\end{tabular}}                        \\ \hline
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{19}                                   & \multicolumn{1}{c|}{67}                                  & \multicolumn{1}{c|}{61}                                   & \multicolumn{1}{c|}{25}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{13}                              & \multicolumn{1}{c|}{30}                              & \multicolumn{1}{c|}{32}                              & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}34}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}27}          \\ \cline{3-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{68.42\%}                              & \multicolumn{1}{c|}{80.60\%}                             & \multicolumn{1}{c|}{77.05\%}                              & \multicolumn{1}{c|}{80.00\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81.69\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.00\%}        & \multicolumn{1}{c|}{80.00\%}                          & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{69.23\%}                         & \multicolumn{1}{c|}{90.00\%}                         & \multicolumn{1}{c|}{75.00\%}                         & \multicolumn{1}{c|}{0.00\%}                          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70.59\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88.89\%}     \\ \cline{3-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$\\ p = 0.2073\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$\\ p = 0.4947\end{tabular}}                          & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 20.956$\\ p \textless 0.0001\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$\\ p= 0.1709\end{tabular}}                                                                                                                                                                                                                                               & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$\\ p =0.078\end{tabular}}    \\ \cline{2-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}91}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}37}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}53}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}49}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}6}       & \multicolumn{1}{c|}{33}                                   & \multicolumn{1}{c|}{58}                                  \\ \cline{3-17}
-			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}69.23\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}84.27\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}85.71\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.86\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.09\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}71.79\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.91\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}79.59\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}33.33\%} & \multicolumn{1}{c|}{69.70\%}                              & \multicolumn{1}{c|}{81.03\%}                             \\ \cline{3-17}
-			\multicolumn{1}{|l|}{\multirow{-6}{*}{\rotatebox{90}{Believability}}} & \multicolumn{1}{l|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$\\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$\\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$\\ p =0.086\end{tabular}}           & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$\\ p = 0.0726\end{tabular}}                                                                                                                                                                                                                    & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$\\ p = 0.1647\end{tabular}}                          \\ \hline
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{60}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{74}                                        & \multicolumn{1}{c|}{20}                                     & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{67}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{47}                                   & \multicolumn{1}{c|}{81}                                  \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{13.33\%}                              & \multicolumn{1}{c|}{9.24\%}                              & \multicolumn{1}{c|}{12.50\%}                              & \multicolumn{1}{c|}{6.78\%}                              & \multicolumn{1}{c|}{12.16\%}                                   & \multicolumn{1}{c|}{10.00\%}                                & \multicolumn{1}{c|}{20.00\%}                          & \multicolumn{1}{c|}{37.50\%}                         & \multicolumn{1}{c|}{5.56\%}                          & \multicolumn{1}{c|}{7.04\%}                          & \multicolumn{1}{c|}{13.43\%}                         & \multicolumn{1}{c|}{10.00\%}                         & \multicolumn{1}{c|}{14.89\%}                              & \multicolumn{1}{c|}{9.88\%}                              \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$\\ p = 0.2804\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}}                         & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$\\ p = 0.3948\end{tabular}}                                  & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$\\ p = 0.1492\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$\\ p = 0.2858\end{tabular}}                           \\ \cline{2-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}58}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}120}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}66}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10}      & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17}
-			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.86\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}9.24\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20.83\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}1.75\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12.77\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}25.64\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}   & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}0.00\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}11.11\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}19.70\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}40.00\%} & \multicolumn{1}{c|}{10.87\%}                              & \multicolumn{1}{c|}{17.50\%}                             \\ \cline{3-17}
-			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Desirability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$\\ p = 0.0034\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$\\ p = 0.059\end{tabular}}          & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$\\ p= 0.0729\end{tabular}}                                                                                                                                                                                                                     & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$\\ p = 0.2288\end{tabular}}                         \\ \hline
+ &  &  & \multicolumn{2}{c|}{GPS usage} & \multicolumn{2}{c|}{Traveller type} & \multicolumn{2}{c|}{Accompany} & \multicolumn{6}{c|}{Distance} & \multicolumn{2}{c|}{Visit frequency} \\ \cline{4-17} 
+ &  &  & GPS user & non-GPS user & Frequent & Non-frequent & Alone & Not alone & 0 & 1 & 2 & 3 & 4 & 5 & Most & Least \\ \hline
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 60} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 119} & 120 & 59 & 74 & 11 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 5} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 8} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 18} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 71} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 64} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 10} & \cellcolor[HTML]{ACDDAA}47 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 81} \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.33} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.58} & 0.51 & 0.47 & 1.00 & 1.00 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 1.00} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.75} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.72} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.44} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.52} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.10} & \cellcolor[HTML]{ACDDAA}0.72 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.36} \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$ \\ p =0.0016\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$ \\ p = 0.3953\end{tabular}} & \multicolumn{2}{c|}{N/A} & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$ \\ p = 0.0028\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$ \\ p = 0.0001\end{tabular}} \\ \cline{2-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 58 & 119 & 120 & 57 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 94} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 39} & 5 & 8 & 18 & 71 & 64 & 10 & 46 & 80 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.48 & 0.56 & 0.53 & 0.54 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.62} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.90} & 0.60 & 0.25 & 0.56 & 0.59 & 0.50 & 0.60 & 0.52 & 0.56 \\ \cline{3-17}
+\multicolumn{1}{|c|}{\multirow{-6}{*}{Memorability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$ \\ p =0.1992\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$ \\ p = 0.4478\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 9.016$ \\ p = 0.0013\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$ \\ p = 0.4467\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$ \\ p = 0.3987\end{tabular}} \\ \hline
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 19 & 67 & 61 & 25 & \cellcolor[HTML]{ACDDAA}71 & \cellcolor[HTML]{ACDDAA}11 & 5 & 5 & 13 & 30 & 32 & 1 & \cellcolor[HTML]{FFFFC7}34 & \cellcolor[HTML]{FFFFC7}27 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.68 & 0.81 & 0.77 & 0.80 & \cellcolor[HTML]{ACDDAA}0.82 & \cellcolor[HTML]{ACDDAA}0.45 & 0.80 & 0.60 & 0.69 & 0.90 & 0.75 & 0.00 & \cellcolor[HTML]{FFFFC7}0.71 & \cellcolor[HTML]{FFFFC7}0.89 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$ \\ p = 0.2073\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$ \\ p = 0.4947\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 82) = 5.137$ \\ p = 0.0117\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$ \\ p= 0.1709\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$ \\ p =0.078\end{tabular}} \\ \cline{2-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}39 & \cellcolor[HTML]{ACDDAA}89 & \cellcolor[HTML]{ACDDAA}91 & \cellcolor[HTML]{ACDDAA}37 & \cellcolor[HTML]{FFFFC7}88 & \cellcolor[HTML]{FFFFC7}39 & \cellcolor[HTML]{FFFFC7}4 & \cellcolor[HTML]{FFFFC7}4 & \cellcolor[HTML]{FFFFC7}12 & \cellcolor[HTML]{FFFFC7}53 & \cellcolor[HTML]{FFFFC7}49 & \cellcolor[HTML]{FFFFC7}6 & 33 & 58 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & \cellcolor[HTML]{FFFFC7}0.84 & \cellcolor[HTML]{FFFFC7}0.72 & \cellcolor[HTML]{FFFFC7}1.00 & \cellcolor[HTML]{FFFFC7}0.75 & \cellcolor[HTML]{FFFFC7}0.75 & \cellcolor[HTML]{FFFFC7}0.85 & \cellcolor[HTML]{FFFFC7}0.80 & \cellcolor[HTML]{FFFFC7}0.33 & 0.70 & 0.81 \\ \cline{3-17}
+\multicolumn{1}{|c|}{\multirow{-6}{*}{Belivability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 60 & 119 & 120 & 59 & 74 & 11 & 5 & 8 & 18 & 71 & 67 & 10 & 47 & 81 \\ \cline{3-17} 
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.13 & 0.92 & 0.13 & 0.07 & 0.12 & 0.18 & 0.20 & 0.38 & 0.06 & 0.07 & 0.13 & 0.10 & 0.15 & 0.10 \\ \cline{3-17} 
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$ \\ p = 0.2804\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$ \\ p = 0.3948\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$ \\ p = 0.1492\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$ \\ p = 0.2858\end{tabular}} \\ \cline{2-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 58} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 119} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 120} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 57} & \cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} 94} & \cellcolor[HTML]{FFFFC7}39 & \cellcolor[HTML]{FFFFC7}5 & \cellcolor[HTML]{FFFFC7}8 & \cellcolor[HTML]{FFFFC7}18 & \cellcolor[HTML]{FFFFC7}70 & \cellcolor[HTML]{FFFFC7}66 & \cellcolor[HTML]{FFFFC7}10 & 46 & 80 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.09} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.02} & \cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} 0.13} & \cellcolor[HTML]{FFFFC7}0.26 & \cellcolor[HTML]{FFFFC7}0.00 & \cellcolor[HTML]{FFFFC7}0.00 & \cellcolor[HTML]{FFFFC7}0.11 & \cellcolor[HTML]{FFFFC7}0.10 & \cellcolor[HTML]{FFFFC7}0.20 & \cellcolor[HTML]{FFFFC7}0.40 & 0.11 & 0.18 \\ \cline{3-17}
+\multicolumn{1}{|c|}{\multirow{-6}{*}{Desirability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$ \\ p = 0.0034\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$ \\ p = 0.059\end{tabular}}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$ \\ p= 0.0729\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$ \\ p = 0.2288\end{tabular}} \\ \hline
 		\end{tabular}

### 2016-09-21 paper/uist_2016/paper.tex
memorability 3/6 visit frequency

--- 2016-09-21 paper/uist_2016/paper.tex
@@
 Three participants (P4, P6, and P10) who were unable to recall a location from a static photo actually recognized the location after seeing the accompanying Rewind.
-They expressed their contentment after watching the Rewind, proclaiming ``I recognize the photo now!'' When we evaluate Rewind memorability based on episodic memory rather than semantic memory, the results show that participants recalled the exact trip depicted by the Rewind 53.7\% of the time.
-%TODO make sure episodic memory is discussed in discussion section--visit frequency diminishes episodic memory
+They expressed their contentment after watching the Rewind, proclaiming ``I recognize the photo now!'' Further differences between Rewinds and static photos are discussed in the following sections.
 
 %TODO h - add another table, only abt memorability tho
+
+\subsubsection{Distance}
 %TODO  where is home? need to explain this part in system? make sure this is explained
-\subsubsection{Distance}
 % only affect location rememberance
@@
 
+When comparing photo memorability and Rewind memorability based on distance, our study shows that for trips close to home (Distance Group 1), photo remembrance was higher by 50\%, $\chi^2(1, 16) = 2.25$, $p = 0.067$.
+For trips far from home (Distance Group 5), Rewind remembrance was higher by 50\%, $\chi^2(1, 20) = 3.516$, $p < 0.05$.
+This suggests that the suitability of photos or Rewinds as memory media may differ depending on how far away from home a person is when they want to document a location.
+%TODO expand on this in discussion
+
 \subsubsection{Visit Frequency}
@@
 % most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
-Location memorability and trip memorability are affected differently by frequency of visits (Figure~\ref{fig:frequencymemory}).
-Location memorability is highest for places that are most frequently visited by the participant, while trip memorability is highest for places that are least frequently visited.
-The more frequently a place was visited, the more likely it was that the participant remembered the location when it was shown to them at the study.
-In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places, with a significance at $\chi^2(1,128) = 14.458$, p < 0.01.
-This effect does not occur for trip memorability.
-In the most frequently visited places, trips are remembered 51\% of the time.
-Instead of seeing trip memorability decrease for least frequently visited places, this factor increases to 56\%.
+Differences in photo memorability due to visit frequency were statistically significant, while differences in location memorability were not.
+Photo memorability is higher for locations that are most frequently visited by the participant, with a remembrance rate of 72.3\%.
+Photo remembrance rate for the least frequently visited locations is 35.8\%.
+This is statistically significant at $\chi^2(1,128) = 14.458$, $p < 0.01$.
 
-Our study examined episodic processing in metric-specific groups, as well as the performance overall.
-Our study shows that comparing to static street-view images, recollection of event-driven memories using \textit{Rewind} videos is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.
+Between photos and Rewinds, photos had a higher remembrance rate for most frequently visited locations, with a difference of 20.2\% $\chi^2(1, N=20) = 3.215$, $p <.05$; and for least frequently visited locations Rewinds had a higher remembrance rate with a difference of 20.5\%, $\chi^2(1, N=161) = 5.977$, $p <.01$, suggesting again that photos and Rewinds may have different suitabilities as memory media.
 
@@
 
+Our results show that GPS usage influences what features participants pick out when deciding whether Rewinds are accurate reflections of their own memories of their trips.
+When we split the responses of regular GPS users from the other participants' responses, we saw that GPS users looked at signs in the Rewind the most to determine accuracy.
+Participants who were not regular GPS users cited the route and surrounding landmarks as features which made the Rewind believable as memories.
+
 \subsubsection{Frequent Travelers}
@@
 Trips with a location that was visited least frequently had a higher accuracy rating of 82\%.
+
+\subsubsection{Other Variables}
+To get a better understanding of what the important features of locational memories are, we looked at participants' responses to why they thought a Rewind was or was not accurate to their memory.
+Participants attributed the accuracy of a Rewind to the presence of different man-made structures.
+The most highly occurring answers to why a Rewind was accurate were: the route, the highways, roads, and streets, the signs, the landmarks, and the buildings.
+The reasons why a Rewind did not seem accurate to participants' memories included more temporal and environmental features.
+When participants responded that a Rewind was not accurate to their memory, they cited the streets, the season and foliage, the time of day, and the angle the Rewind viewed the world at as factors of inaccuracy.
 
@@
 
-\subsubsection{Features}
-To get a better understanding of what the important features of locational memories are, we looked at participants' responses to why they thought a Rewind was or was not accurate to their memory.
-Participants attributed the accuracy of a Rewind to the presence of different man-made structures.
-The most highly occurring answers to why a Rewind was accurate were: the route, the highways, roads, and streets, the signs, the landmarks, and the buildings.
-The reasons why a Rewind did not seem accurate to participants' memories included more temporal and environmental features.
-When participants responded that a Rewind was not accurate to their memory, they cited the streets, the season and foliage, the time of day, and the angle the Rewind viewed the world at as factors of inaccuracy.
-
-Our results show that GPS usage influences what features participants pick out when deciding whether Rewinds are accurate reflections of their own memories of their trips.
-When we split the responses of regular GPS users from the other participants' responses, we saw that GPS users looked at signs in the Rewind the most to determine accuracy.
-Participants who were not regular GPS users cited the route and surrounding landmarks as features which made the Rewind believable as memories.
-
 % \begin{figure}
@@
 % \end{figure}
-
-\subsubsection{Participant Responses}
-When asked why they wanted to keep or not keep a photo or Rewind, patterns emerged in the participants' answers.
-Participants didn't want to keep anything that was ``no use'' or had ``no meaning or significance.'' One participant said they ``didn't need any more memories of work.'' Some participants acknowledged the ``good composition,'' and one said, ``It's not a bad photo but it wasn't taken by me.'' Participants were most likely to keep photos that reminded them of good memories,
-
-\subsection{Participant Reactions}
-There was a range of behaviors and attitudes toward Rewinds from the participants.
-One participant called Rewinds ``creepy, eerie,'' and said they might ``show them to a friend who's a conspiracy theorist.'' Another participant proclaimed that they weren't ``paranoid about technology.'' Many participants, especially regular GPS users, examined signs in Rewinds intensely, looking at highway exit signs to try to remember their trip.
-Other participants did not feel positive after watching their Rewinds, saying that they ``just realized how often [they] take the same route,'' or that they felt like they ``needed to switch up [their] routine.'' One participant was amazed, and exclaimed, ``It's like it's happening!'' But the most important responses were from participants who changed their responses after recognizing an image in their Rewind: ``I recognize the photo now.'' The Rewind had helped them remember the location of the original image.
 

### 2016-09-21 paper/uist_2016/paper.tex
add captions for tables, fix typos

--- 2016-09-21 paper/uist_2016/paper.tex
@@
 	\centering
-	\caption{My caption}
+	\caption{Participant responses about the memorability, believability, and desirability or Rewinds and photos. The aggregate responses for the two mediums are compared.}
 	\small
@@
 		\cline{2-9}
-		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Belivability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
+		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Believability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
 		& \begin{tabular}[c]{@{}c@{}}video\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}video\\ trip\end{tabular} & photo & video & photo & video \\ \hline
@@
 	\centering
-	\caption{My caption}
+	\caption{Differences in memorability, believability, and desirability for different conditions of the trip or traveller.
+A green background denotes cases where there was a statistically significant difference within that condition.}
 	\begin{adjustbox}{width=1\textwidth}
@@
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & \cellcolor[HTML]{FFFFC7}0.84 & \cellcolor[HTML]{FFFFC7}0.72 & \cellcolor[HTML]{FFFFC7}1.00 & \cellcolor[HTML]{FFFFC7}0.75 & \cellcolor[HTML]{FFFFC7}0.75 & \cellcolor[HTML]{FFFFC7}0.85 & \cellcolor[HTML]{FFFFC7}0.80 & \cellcolor[HTML]{FFFFC7}0.33 & 0.70 & 0.81 \\ \cline{3-17}
-\multicolumn{1}{|c|}{\multirow{-6}{*}{Belivability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
+\multicolumn{1}{|c|}{\multirow{-6}{*}{Believability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 60 & 119 & 120 & 59 & 74 & 11 & 5 & 8 & 18 & 71 & 67 & 10 & 47 & 81 \\ \cline{3-17} 

### 2016-09-21 paper/uist_2016/paper.tex
added explaination of yellow bg in table

@@
 	\caption{Differences in memorability, believability, and desirability for different conditions of the trip or traveller.
-A green background denotes cases where there was a statistically significant difference within that condition.}
+A green background denotes cases where there was a statistically significant difference within that condition where $\alpha = 0.05$, and a yellow background denotes cases where $\alpha = 0.1$}
 	\begin{adjustbox}{width=1\textwidth}

### 2016-09-21 paper/uist_2016/paper.tex
removed yellow bg

--- 2016-09-21 paper/uist_2016/paper.tex
@@
 \begin{abstract}
-We introduce \textit{Rewind}, a system that assists in the recall of semantic and episodic memory by automatically recreating interactive sceneries of past trips.
-\textit{Rewind} uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images.
-Since the effectiveness of memory cues is determined by their level of integration with the target memory, images used in \textit{Rewind} are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience.
+We introduce Rewind system which assists in the recall of semantic and episodic memory by automatically recreating interactive sceneries of past trips.
+Rewind system uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images.
+Since the effectiveness of memory cues is determined by their level of integration with the target memory, images used in Rewind system are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience.
 Users can interactively go back and forth in time by scrubbing over the video.
-Together, the composed \textit{Rewind} videos offer users a window into past travels.
+Together, the composed video offer users a window into past travels.
 We report the results of a user study with eighteen participants conducted to collect location data over two weeks.
-Trips taken in groups were more likely to be recalled using \textit{Rewind} videos than trips taken alone.
-\textit{Rewind} also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still preserve believable representations that capture the past.
+Trips taken in groups were more likely to be recalled using Rewinds than trips taken alone.
+Rewind also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still preserve believable representations that capture the past.
 \end{abstract}
@@
 \multicolumn{1}{|c|}{\multirow{-6}{*}{Memorability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$ \\ p =0.1992\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$ \\ p = 0.4478\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 9.016$ \\ p = 0.0013\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$ \\ p = 0.4467\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$ \\ p = 0.3987\end{tabular}} \\ \hline
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 19 & 67 & 61 & 25 & \cellcolor[HTML]{ACDDAA}71 & \cellcolor[HTML]{ACDDAA}11 & 5 & 5 & 13 & 30 & 32 & 1 & \cellcolor[HTML]{FFFFC7}34 & \cellcolor[HTML]{FFFFC7}27 \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.68 & 0.81 & 0.77 & 0.80 & \cellcolor[HTML]{ACDDAA}0.82 & \cellcolor[HTML]{ACDDAA}0.45 & 0.80 & 0.60 & 0.69 & 0.90 & 0.75 & 0.00 & \cellcolor[HTML]{FFFFC7}0.71 & \cellcolor[HTML]{FFFFC7}0.89 \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$ \\ p = 0.2073\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$ \\ p = 0.4947\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 82) = 5.137$ \\ p = 0.0117\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$ \\ p= 0.1709\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$ \\ p =0.078\end{tabular}} \\ \cline{2-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}39 & \cellcolor[HTML]{ACDDAA}89 & \cellcolor[HTML]{ACDDAA}91 & \cellcolor[HTML]{ACDDAA}37 & \cellcolor[HTML]{FFFFC7}88 & \cellcolor[HTML]{FFFFC7}39 & \cellcolor[HTML]{FFFFC7}4 & \cellcolor[HTML]{FFFFC7}4 & \cellcolor[HTML]{FFFFC7}12 & \cellcolor[HTML]{FFFFC7}53 & \cellcolor[HTML]{FFFFC7}49 & \cellcolor[HTML]{FFFFC7}6 & 33 & 58 \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & \cellcolor[HTML]{FFFFC7}0.84 & \cellcolor[HTML]{FFFFC7}0.72 & \cellcolor[HTML]{FFFFC7}1.00 & \cellcolor[HTML]{FFFFC7}0.75 & \cellcolor[HTML]{FFFFC7}0.75 & \cellcolor[HTML]{FFFFC7}0.85 & \cellcolor[HTML]{FFFFC7}0.80 & \cellcolor[HTML]{FFFFC7}0.33 & 0.70 & 0.81 \\ \cline{3-17}
-\multicolumn{1}{|c|}{\multirow{-6}{*}{Believability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 19 & 67 & 61 & 25 & \cellcolor[HTML]{ACDDAA}71 & \cellcolor[HTML]{ACDDAA}11 & 5 & 5 & 13 & 30 & 32 & 1 & 34 & 27 \\ \cline{3-17} 
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.68 & 0.81 & 0.77 & 0.80 & \cellcolor[HTML]{ACDDAA}0.82 & \cellcolor[HTML]{ACDDAA}0.45 & 0.80 & 0.60 & 0.69 & 0.90 & 0.75 & 0.00 & 0.71 & 0.89 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$ \\ p = 0.2073\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$ \\ p = 0.4947\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 82) = 5.137$ \\ p = 0.0117\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$ \\ p= 0.1709\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$ \\ p =0.078\end{tabular}} \\ \cline{2-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}39 & \cellcolor[HTML]{ACDDAA}89 & \cellcolor[HTML]{ACDDAA}91 & \cellcolor[HTML]{ACDDAA}37 & 88 & 39 & 4 & 4 & 12 & 53 & 49 & 6 & 33 & 58 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & 0.84 & 0.72 & 1.00 & 0.75 & 0.75 & 0.85 & 0.80 & 0.33 & 0.70 & 0.81 \\ \cline{3-17}
+\multicolumn{1}{|c|}{\multirow{-6}{*}{Belivability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 60 & 119 & 120 & 59 & 74 & 11 & 5 & 8 & 18 & 71 & 67 & 10 & 47 & 81 \\ \cline{3-17} 
@@
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$ \\ p = 0.2804\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$ \\ p = 0.3948\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$ \\ p = 0.1492\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$ \\ p = 0.2858\end{tabular}} \\ \cline{2-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 58} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 119} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 120} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 57} & \cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} 94} & \cellcolor[HTML]{FFFFC7}39 & \cellcolor[HTML]{FFFFC7}5 & \cellcolor[HTML]{FFFFC7}8 & \cellcolor[HTML]{FFFFC7}18 & \cellcolor[HTML]{FFFFC7}70 & \cellcolor[HTML]{FFFFC7}66 & \cellcolor[HTML]{FFFFC7}10 & 46 & 80 \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.09} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.02} & \cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} 0.13} & \cellcolor[HTML]{FFFFC7}0.26 & \cellcolor[HTML]{FFFFC7}0.00 & \cellcolor[HTML]{FFFFC7}0.00 & \cellcolor[HTML]{FFFFC7}0.11 & \cellcolor[HTML]{FFFFC7}0.10 & \cellcolor[HTML]{FFFFC7}0.20 & \cellcolor[HTML]{FFFFC7}0.40 & 0.11 & 0.18 \\ \cline{3-17}
-\multicolumn{1}{|c|}{\multirow{-6}{*}{Desirability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$ \\ p = 0.0034\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$ \\ p = 0.059\end{tabular}}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$ \\ p= 0.0729\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$ \\ p = 0.2288\end{tabular}} \\ \hline
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 58} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 119} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 120} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 57} & 94 & 39 & 5 & 8 & 18 & 70 & 66 & 10 & 46 & 80 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.09} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.02} & 0.13 & 0.26 & 0.00 & 0.00 & 0.11 & 0.10 & 0.20 & 0.40 & 0.11 & 0.18 \\ \cline{3-17}
+\multicolumn{1}{|c|}{\multirow{-6}{*}{Desirability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$ \\ p = 0.0034\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$ \\ p = 0.059\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$ \\ p= 0.0729\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$ \\ p = 0.2288\end{tabular}} \\ \hline
 \end{tabular}
@@
 Our study examined episodic processing in metric-specific groups, as well as the performance overall.
-Our study shows that comparing to static street-view images, recollection of event-driven memories using \textit{Rewind} videos is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.
+Our study shows that comparing to static street-view images, recollection of event-driven memories using Rewinds is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.
 
@@
 On the other hand, trip details tend to be more easily remembered during accompanied visits.
-Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching a \textit{Rewind} video, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.
+Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.
 

### 2016-09-21 paper/uist_2016/paper.tex
fixed rewind naming; fixed believability typo in table

@@
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & 0.84 & 0.72 & 1.00 & 0.75 & 0.75 & 0.85 & 0.80 & 0.33 & 0.70 & 0.81 \\ \cline{3-17}
-\multicolumn{1}{|c|}{\multirow{-6}{*}{Belivability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
+\multicolumn{1}{|c|}{\multirow{-6}{*}{Believability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 60 & 119 & 120 & 59 & 74 & 11 & 5 & 8 & 18 & 71 & 67 & 10 & 47 & 81 \\ \cline{3-17} 

### 2016-09-21 paper/uist_2016/paper.tex
naming 2nd time

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\textit{Rewind} recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved from location-tracking apps, including the default tracking behavior on Android phones.
+Rewind system recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved from location-tracking apps, including the default tracking behavior on Android phones.
 Differing from previously studied hyperlapse creation techniques, such as the studies by Kopft et al.
-and Joshi et al \cite{Kopf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight.
-\textit{Rewind} inputs geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images (although other street side photo services may be used).
+and Joshi et al \cite{Kopf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, Rewind system does not require any cinematic archives from the users, and it is computationally lightweight.
+Rewind inputs geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images (although other street side photo services may be used).
 The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues.
-The current version of \textit{Rewind} is a open-sourced, web-based application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store them.
-\textit{Rewind} can be accessed at [anonymized: url to rewind].
+The current version of Rewind system is a open-sourced, web-based application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store them.
+Rewind can be accessed at [anonymized: url to rewind].
 %\ref{fig:flowchart}
@@
 A user's geolocation tracking data includes latitude and longitude coordinates, and timestamps of when the user was at given coordinates.
-\textit{Rewind} expects JSON formatted data, and is also compatible with other location-based formats such as GPX.
+Rewind expects JSON formatted data, and is also compatible with other location-based formats such as GPX.
 Rewind generates location points for the user, using smart filtering based on visit frequencies to decrease the data noise and diversify the locations shown to the user.
@@
 \subsection{Sequence Creation}
-Each video recollection created by \textit{Rewind} is composed of two hundred Google Street View image sequences of the chosen route being stitched together using StreetViewSequence \cite{streetviewsequence}.
+Each video recollection created by Rewind is composed of two hundred Google Street View image sequences of the chosen route being stitched together using StreetViewSequence \cite{streetviewsequence}.
 Each incoming Google Street View image has been retrieved with the same dimensions (640 px by 640 px) with similar spatial orientation (FOV, pitch and heading values).
@@
 Previous work done by \cite{laffont2014transient,shih2013data} have successfully reconstructed images with varying diurnal and seasonal cycles, yet it would be computationally expensive to replicate the proposed techniques in real-time on large sets of images.
-Considering each \textit{Rewind} sequence of images would contain two hundred frames, this process would take many hours per route, and it would be challenging to incorporate a large training dataset into the rendering pipeline.
+Considering each Rewind sequence of images would contain two hundred frames, this process would take many hours per route, and it would be challenging to incorporate a large training dataset into the rendering pipeline.
 Due to the timing constraint, Rewind instead adopts a simplified approach of color space mapping for object segmentation and color adjustment, with the facilitation of CamanJS \cite{caman}.

### 2016-09-21 paper/uist_2016/paper.tex
trim related work

--- 2016-09-21 paper/uist_2016/paper.tex
@@
 \begin{abstract}
-We introduce Rewind system which assists in the recall of semantic and episodic memory by automatically recreating interactive sceneries of past trips.
-Rewind system uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images.
-Since the effectiveness of memory cues is determined by their level of integration with the target memory, images used in Rewind system are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience.
+We introduce \textit{Rewind}, a system that assists in the recall of semantic and episodic memory by automatically recreating interactive sceneries of past trips.
+\textit{Rewind} uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images.
+Since the effectiveness of memory cues is determined by their level of integration with the target memory, images used in \textit{Rewind} are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience.
 Users can interactively go back and forth in time by scrubbing over the video.
-Together, the composed video offer users a window into past travels.
+Together, the composed \textit{Rewind} videos offer users a window into past travels.
 We report the results of a user study with eighteen participants conducted to collect location data over two weeks.
-Trips taken in groups were more likely to be recalled using Rewinds than trips taken alone.
-Rewind also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still preserve believable representations that capture the past.
+Trips taken in groups were more likely to be recalled using \textit{Rewind} videos than trips taken alone.
+\textit{Rewind} also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still preserve believable representations that capture the past.
 \end{abstract}
@@
 \subsection{Location History}
-A project that also leverages location data to capture the essence of a trip is by Thudt et al., who discuss the creation and investigation into the challenges and limits of visual mementos \cite{thudt2016visual}.
-The authors define visual mementos as ``visualizations of personally relevant data for the purpose of reminiscing, and sharing of life experiences.'' They present one implementation example of visual mementos that involves GPS location histories.
-This common goal of providing a way for people to reminisce about their trips reinforces the purpose of Rewind.
-Another reinforcement can be found in the way that their system is enhanced with geotagged photos from Flickr.
-The three main challenges presented in Thudt et al.'s paper are: 1) evoking familiarity, 2) expressing subjectivity, and 3) obscuring sensitive data.
-The authors attempt to address those challenges in the tool they built, called Visits, and their findings from the case study show that there is benefit to the visualization of personal mementos.
-Rewind builds on their work by breaking a trip down into smaller sequences and recreating the visual experience, whereas Visits relies on a more traditional top-down map view and timeline.
-
-Another project by de Silva and Aizawa has also relied on geolocation data to provide a visual examination of interested traveling routes by linking geo-tagging metadata with online imageries, specifically Google Street View images \cite{deSilva:2009:RMT:1631272.1631414}.
+Silva and Aizawa build on location data to provide a visual examination of interested traveling routes by linking geo-tagging metadata with online imageries, specifically Google Street View images \cite{deSilva:2009:RMT:1631272.1631414}.
 The authors proposed a sketch-based interface that would perform spatial and temporal queries on line drawings specified by the users.
@@
 However, Rewind differs in that the mapping is finalized with geolocation data provided by users tracked using smartphones.
-This means that Rewind serves more of a getaway for recalling episodic memory rather than reviewing a potential travelling itinerary, aiming to provide a mechanism for reminiscence and sharing of past experience while exploring users' behavioral patterns.
-Moreover, the reconstruction techniques used in Rewind would differentiate the same retrieved image with various temporal cues such as changes in seasons; yet the immediate results from the temporal queries suggested by de Silva and Aizawa have not been fully revealed.
+This means that Rewind serves more of a geteway for recalling episodic memory rather than reviewing a potential travelling itinerary, aiming to provide a mechanism for reminiscence and sharing of past experience while exploring users' behavioral patterns.
+Moreover, the reconstruction techniques used in Rewind would differentiate the same retrieved image with various temporal cues such as changes in seasons.
+%; yet the immediate results from the temporal queries suggested by de Silva and Aizawa have not been fully revealed.
 
-Other research has used location history not to create a new interface for the user, but for other applications.
+Larsen et al.
+use a spiral chart for a user to see the continuity of their locations, where days are placed around the spiral \cite{larsen2013qs}.
+This visualization allows users to explore and discover patterns in their daily lives.
+An early implementation of Visits by Thudt et al.
+focuses on the map and timeline views of location, interleaving them together \cite{thudt2013visits}.
+In their visualization, users can move from location to location using their pointer, which at the same time moves back and forth in time.
+This partially inspired the scrubbing technique in Rewind of traveling back and forth in time by scrubbing left and right, at the same time changing the image of what was seen at that time.
+
+Later, Thudt et al.
+expand on the idea of visual mementos based on location history data and geotagged photos from Flickr~\cite{thudt2016visual}.
+The authors define visual mementos as ``visualizations of personally relevant data for the purpose of reminiscing, and sharing of life experiences.'' This common goal of providing a way for people to reminisce about their trips reinforces the purpose of Rewind.
+% Another reinforcement can be found in the way that their system is enhanced with geotagged photos from Flickr.
+The three main challenges presented in Thudt et al.'s paper are: 1) evoking familiarity, 2) expressing subjectivity, and 3) obscuring sensitive data.
+The authors attempt to address those challenges in Visits, and their findings from the case study show that there is benefit to the visualization of personal mementos.
+Rewind builds on their work by breaking a trip down into smaller sequences and recreating the visual experience, whereas Visits relies on a more traditional top-down map view and timeline.
+
+% Other research has used location history not to create a new interface for the user, but for other applications.
 Neuhaus's UrbanDiary project \cite{neuhaus2010urbandiary} uses GPS devices to create and visualize ``personal tracks'' as well as collective tracks for a city.
@@
 The researchers focused on comparing the different visualization techniques used to portray data from a two-month study involved twenty participants wearing GPS devices.
-Using geotagged images from Flickr, Becker et al.'s work has shown that movement trajactories in metropolian areas tend to converge at Points of Interests(POIs) \cite{Becker2015}.
+Using geotagged images from Flickr, Becker et al.'s work has shown that movement trajactories in metropolian areas tend to converge at Points of Interests \cite{Becker2015}.
 The data from these studies show each person's location data can be used as a unique fingerprint.
@@
 They found that ``the GPS disconnects the drivers from the external environment.'' As a result of the drivers' disengagement with their surroundings, ``the process of interpreting the world, adding value to it, and turning space into place is reduced to a certain extent and drivers remain detached from the indifferent environments that surround them.'' Since Rewind touches on the topic of travel, it also inherently deals with car travel and GPS.
-We imagine that regular GPS users will interact with Rewinds differently.
+We imagine that regular GPS users will interact with Rewinds differently, and examine this in our study.
 
-A common thing to do with location history data is to develop a visualization of it.
-Larsen et al.
-use a spiral chart for a user to see the continuity of their locations, where days are put around the spiral \cite{larsen2013qs}.
-This visualization allows users to explore and discover patterns in their daily lives.
-An early implementation of Visits by Thudt et al.
-focuses on the map and timeline views of location, interleaving them together \cite{thudt2013visits}.
-In their visualization, users can move from location to location using their pointer, which at the same time moves back and forth in time.
-This partially inspired the scrubbing technique in Rewind of traveling back and forth in time by scrubbing left and right, at the same time changing the image of what was seen at that time.
-
-Finally, as location reveals where a person was at certain times, and is often a comprehensive view of someone's routes, there are substantial privacy concerns for this type of data.
+Finally, location data reveals where a person was at certain times and the routes they take, so there are substantial privacy concerns.
 Not only can it reveal a person's home location, but it can also be used to forecast where they might be at a certain time in the future, or where they might not be.
@@
 \multicolumn{1}{|c|}{\multirow{-6}{*}{Memorability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$ \\ p =0.1992\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$ \\ p = 0.4478\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 9.016$ \\ p = 0.0013\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$ \\ p = 0.4467\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$ \\ p = 0.3987\end{tabular}} \\ \hline
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 19 & 67 & 61 & 25 & \cellcolor[HTML]{ACDDAA}71 & \cellcolor[HTML]{ACDDAA}11 & 5 & 5 & 13 & 30 & 32 & 1 & 34 & 27 \\ \cline{3-17} 
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.68 & 0.81 & 0.77 & 0.80 & \cellcolor[HTML]{ACDDAA}0.82 & \cellcolor[HTML]{ACDDAA}0.45 & 0.80 & 0.60 & 0.69 & 0.90 & 0.75 & 0.00 & 0.71 & 0.89 \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$ \\ p = 0.2073\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$ \\ p = 0.4947\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 82) = 5.137$ \\ p = 0.0117\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$ \\ p= 0.1709\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$ \\ p =0.078\end{tabular}} \\ \cline{2-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}39 & \cellcolor[HTML]{ACDDAA}89 & \cellcolor[HTML]{ACDDAA}91 & \cellcolor[HTML]{ACDDAA}37 & 88 & 39 & 4 & 4 & 12 & 53 & 49 & 6 & 33 & 58 \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & 0.84 & 0.72 & 1.00 & 0.75 & 0.75 & 0.85 & 0.80 & 0.33 & 0.70 & 0.81 \\ \cline{3-17}
-\multicolumn{1}{|c|}{\multirow{-6}{*}{Belivability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 19 & 67 & 61 & 25 & \cellcolor[HTML]{ACDDAA}71 & \cellcolor[HTML]{ACDDAA}11 & 5 & 5 & 13 & 30 & 32 & 1 & \cellcolor[HTML]{FFFFC7}34 & \cellcolor[HTML]{FFFFC7}27 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.68 & 0.81 & 0.77 & 0.80 & \cellcolor[HTML]{ACDDAA}0.82 & \cellcolor[HTML]{ACDDAA}0.45 & 0.80 & 0.60 & 0.69 & 0.90 & 0.75 & 0.00 & \cellcolor[HTML]{FFFFC7}0.71 & \cellcolor[HTML]{FFFFC7}0.89 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$ \\ p = 0.2073\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$ \\ p = 0.4947\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 82) = 5.137$ \\ p = 0.0117\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$ \\ p= 0.1709\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$ \\ p =0.078\end{tabular}} \\ \cline{2-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}39 & \cellcolor[HTML]{ACDDAA}89 & \cellcolor[HTML]{ACDDAA}91 & \cellcolor[HTML]{ACDDAA}37 & \cellcolor[HTML]{FFFFC7}88 & \cellcolor[HTML]{FFFFC7}39 & \cellcolor[HTML]{FFFFC7}4 & \cellcolor[HTML]{FFFFC7}4 & \cellcolor[HTML]{FFFFC7}12 & \cellcolor[HTML]{FFFFC7}53 & \cellcolor[HTML]{FFFFC7}49 & \cellcolor[HTML]{FFFFC7}6 & 33 & 58 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & \cellcolor[HTML]{FFFFC7}0.84 & \cellcolor[HTML]{FFFFC7}0.72 & \cellcolor[HTML]{FFFFC7}1.00 & \cellcolor[HTML]{FFFFC7}0.75 & \cellcolor[HTML]{FFFFC7}0.75 & \cellcolor[HTML]{FFFFC7}0.85 & \cellcolor[HTML]{FFFFC7}0.80 & \cellcolor[HTML]{FFFFC7}0.33 & 0.70 & 0.81 \\ \cline{3-17}
+\multicolumn{1}{|c|}{\multirow{-6}{*}{Believability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 60 & 119 & 120 & 59 & 74 & 11 & 5 & 8 & 18 & 71 & 67 & 10 & 47 & 81 \\ \cline{3-17} 
@@
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$ \\ p = 0.2804\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$ \\ p = 0.3948\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$ \\ p = 0.1492\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$ \\ p = 0.2858\end{tabular}} \\ \cline{2-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 58} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 119} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 120} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 57} & 94 & 39 & 5 & 8 & 18 & 70 & 66 & 10 & 46 & 80 \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.09} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.02} & 0.13 & 0.26 & 0.00 & 0.00 & 0.11 & 0.10 & 0.20 & 0.40 & 0.11 & 0.18 \\ \cline{3-17}
-\multicolumn{1}{|c|}{\multirow{-6}{*}{Desirability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$ \\ p = 0.0034\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$ \\ p = 0.059\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$ \\ p= 0.0729\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$ \\ p = 0.2288\end{tabular}} \\ \hline
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 58} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 119} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 120} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 57} & \cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} 94} & \cellcolor[HTML]{FFFFC7}39 & \cellcolor[HTML]{FFFFC7}5 & \cellcolor[HTML]{FFFFC7}8 & \cellcolor[HTML]{FFFFC7}18 & \cellcolor[HTML]{FFFFC7}70 & \cellcolor[HTML]{FFFFC7}66 & \cellcolor[HTML]{FFFFC7}10 & 46 & 80 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.09} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.02} & \cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} 0.13} & \cellcolor[HTML]{FFFFC7}0.26 & \cellcolor[HTML]{FFFFC7}0.00 & \cellcolor[HTML]{FFFFC7}0.00 & \cellcolor[HTML]{FFFFC7}0.11 & \cellcolor[HTML]{FFFFC7}0.10 & \cellcolor[HTML]{FFFFC7}0.20 & \cellcolor[HTML]{FFFFC7}0.40 & 0.11 & 0.18 \\ \cline{3-17}
+\multicolumn{1}{|c|}{\multirow{-6}{*}{Desirability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$ \\ p = 0.0034\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$ \\ p = 0.059\end{tabular}}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$ \\ p= 0.0729\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$ \\ p = 0.2288\end{tabular}} \\ \hline
 		\end{tabular}
@@
 Our study examined episodic processing in metric-specific groups, as well as the performance overall.
-Our study shows that comparing to static street-view images, recollection of event-driven memories using Rewinds is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.
+Our study shows that comparing to static street-view images, recollection of event-driven memories using \textit{Rewind} videos is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.
 
@@
 On the other hand, trip details tend to be more easily remembered during accompanied visits.
-Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.
+Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching a \textit{Rewind} video, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.
 

### 2016-09-21 paper/uist_2016/paper.tex
writing edits

@@
 \item Memorability: How well do Rewinds facilitate the retrieval of a memory? What types of participants are most likely to recall their memories using Rewinds?
-\item Believability:  How accurate are Rewinds in the eyes of the participants? 
+\item Believability:  How accurately do Rewinds reflect a person's memory in the eyes of the participants? 
 \item Desirability: What factors are inherent to participants' decisions in preserving artifacts created by the Rewind system?
@@
 Distances ranged from 0 to 206,155 meters.
-For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 corresponded to a range of 10--100 meters; Group 2 corresponded to a range of 100--1,000 meters; Group 3 corresponded to a range of 1,000--10,000 meters; Group 4 corresponded to a range of 10,000--100,000 meters and Group 5 corresponded to a range of 100,000--1,000,000 meters from the participant's home location.
+For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 was 10--100 meters; Group 2 was 100--1,000 meters; Group 3 was 1,000--10,000 meters; Group 4 was 10,000--100,000 meters and Group 5 was 100,000--1,000,000 meters from the participant's home location.
 	\item Visit frequency: do participants react differently to Rewinds and static photos depicting locations they visit frequently compared to locations they rarely visit?
@@
 Our data does show, however, that Rewind remembrance was largely the same for most distance groups, except for distances that were close to home in Distance Group 1.
-While remembrance for all distance groups was between 50-60\%, remembrance for Rewinds in Distance Group 1 was 25\%.
+While remembrance for all distance groups was between 50--60\%, remembrance for Rewinds in Distance Group 1 was 25\%.
 This data suggests that participants often did not remember or could not distinguish the exact trips that occurred in locations close to their home.
@@
 %TODO where to put this????  maybe split discussion into three sections on mem/believ/desir
-\subsubsection{Episodic Memory}
+% Jeff thinks that the discussion is already a bit long. It's fine in here, but maybe shorten it. Don't add more sections
+\subsection{Episodic Memory}
 It could possibly be inferred that participants are likely to benefit more from Rewinds than static street-view images at recalling episodic memory.

### 2016-09-21 paper/uist_2016/paper.tex
minor edits

@@
 
-Our user study explored the following five metrics as potentially having an effect on memorability, believability, or desirability of digital memory media:
+Our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media:
 \begin{enumerate}
@@
 	\end{adjustbox}
+\label{table:betweensubjects}
 \end{table*}
@@
 % most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
-Location memorability and trip memorability are affected differently by frequency of visits (Figure~\ref{fig:frequencymemory}).
+Location memorability and trip memorability are affected differently by frequency of visits (Table~\ref{table:betweensubjects}).
 Location memorability is highest for places that are most frequently visited by the participant, while trip memorability is highest for places that are least frequently visited.

### 2016-09-21 paper/uist_2016/paper.tex
minor edit with some added quotes

@@
 
+% h - deleted participants # for consistencies - P4, P6 and P10 for future reference
 \subsubsection{Rewinds vs. Static Photos} 
@@
 As discussed above, this can be expected because cinematic media like Rewinds provide more context and retrieval cues.
-Three participants (P4, P6, and P10) who were unable to recall a location from a static photo actually recognized the location after seeing the accompanying Rewind.
+Three participants who were unable to recall a location from a static photo actually recognized the location after seeing the accompanying Rewind.
 They expressed their contentment after watching the Rewind, proclaiming ``I recognize the photo now!'' When we evaluate Rewind memorability based on episodic memory rather than semantic memory, the results show that participants recalled the exact trip depicted by the Rewind 53.7\% of the time.
@@
 The more frequently a place was visited, the more likely it was that the participant remembered the location when it was shown to them at the study.
-In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places, with a significance at $\chi^2(1,128) = 14.458$, p < 0.01.
+In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places, with a significance at $\chi^2(1,128) = 14.458$, $p < 0.01$.
 This effect does not occur for trip memorability.
@@
 Instead of seeing trip memorability decrease for least frequently visited places, this factor increases to 56\%.
+Our study also shows that comparing to static street-view images, recollection of trip memories using Rewinds is significantly improved for least frequently taken trips by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.
 
-Our study examined episodic processing in metric-specific groups, as well as the performance overall.
+% Our study examined episodic processing in metric-specific groups, as well as the performance overall.
 Our study shows that comparing to static street-view images, recollection of event-driven memories using Rewinds is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.
@@
 Although the difference between non-regular and regular GPS users' trip remembrance is not statistically significance, the between-subject percentage values still lean towards the observation that it is perhaps easier for non-GPS users to recall episodic memories from external memory cues, given that the total trip remembrance rate for non-GPS users is 48\% and that of GPS users is 56\%.
-Since regular GPS users are frequently directed step-by-step on how to navigate through their environment, regular GPS users may not need to pay as much attention to their surroundings, leading to potentially diminished locational awareness which could be the reason why regular GPS users had a lower remembrance rate for their ambience, particularly locations.
+Since regular GPS users are frequently directed step-by-step on how to navigate through their environment, they may not need to pay as much attention to their surroundings, leading to potentially diminished locational awareness which could be the reason why regular GPS users had a lower remembrance rate for their ambience, particularly locations.
+One non-regular GPS user mentioned that ``I identify by landmarks'', yet this is something that regular GPS users may pay less attention to.
 \\
@@
 For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1,94) = 31.812$, $p < 0.00001$.
-On the other hand, trip details tend to be more easily remembered during accompanied visits.
+On the other hand, trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and i walked a certain way -- I don't usually take this route".
 Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.
@@
 % Jeff thinks that the discussion is already a bit long. It's fine in here, but maybe shorten it. Don't add more sections
-\subsection{Episodic Memory}
-It could possibly be inferred that participants are likely to benefit more from Rewinds than static street-view images at recalling episodic memory.
+% h - work on integrating this part or just deleting it
+% \subsection{Episodic Memory}
+% It could possibly be inferred that participants are likely to benefit more from Rewinds than static street-view images at recalling episodic memory.
 Although participants were not explicitly asked about trip rememberance when presented with static images as opposed to what they were asked after watchiing Rewinds, location rememberance from static images may serve as an upper-bound estimation of how much an individual could recall about a particular trip; since if participants fail to form any cognitive association with the locations depicted in the images, it is very unlikely that they would be able to associate target itineraries with the locations shown.
@@
 
-One plausible explanation of the improvement may be inherent to the encoding of episodic memory in the first place.
+% One plausible explanation of the improvement may be inherent to the encoding of episodic memory in the first place.
 As suggested by the levels-of-processing theory(ref), encoding efficacy is heavily dependent on the levels to which stimuli are being actively or passively processed.
@@
 
-The extent to which attention is dedicated while taking a trip may be another possible explanation for the observed improvement using Rewinds.
+% The extent to which attention is dedicated while taking a trip may be another possible explanation for the observed improvement using Rewinds.
 This is perhaps particularly applicable to explain why participants who were self-identified regular GPS users tend to benefit more from Rewinds with episodic memory recalling.
@@
 
-It may appear to be puzzling that participants seem to recall less about specifics of their trips from Rewinds compared to static imageries when they traveled alone, with a significant decrease around 40\%, $\chi^2(1, N=168) = 33.831$, $p <.01$; when the trips were most frequently taken, with a significant decrease of 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$; and when the trips taken were 10 - 100 meters (33 - 328 feet) away from home, with a mildly significant decrease of 50\%, $\chi^2(1, N=16) = 2.25$, $p <.1$.
+% h - I'll comment it back if it is necessary
+% It may appear to be puzzling that participants seem to recall less about specifics of their trips from Rewinds compared to static imageries when they traveled alone, with a significant decrease around 40\%, $\chi^2(1, N=168) = 33.831$, $p <.01$; when the trips were most frequently taken, with a significant decrease of 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$; and when the trips taken were 10 - 100 meters (33 - 328 feet) away from home, with a mildly significant decrease of 50\%, $\chi^2(1, N=16) = 2.25$, $p <.1$.
 One possible reason for this would be it is hard for participants to tie a repeatedly taken trip with a specific instance in time, and trips taken near home could also be the ones that are most frequently taken.

### 2016-09-21 paper/uist_2016/paper.tex
more quotes

@@
 For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1,94) = 31.812$, $p < 0.00001$.
-On the other hand, trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and i walked a certain way -- I don't usually take this route".
+On the other hand, trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and i walked a certain way -- don't usually take this route".
 Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.
@@
 We measured the value of photos and Rewinds by asking participants if they would want to keep the photo or Rewind after seeing it.
+One participant expressed his interestes in Rewind, saying ``Would keep photos that I know/can place in context, but would keep every single video...
+cool to look back on where you were, what you did/as a record".
 Overall, participants wished to keep 11\% of the photos they were shown and 15\% of the Rewinds they were shown.
@@
 Rewinds containing a location visited most frequently by the participant are kept 8\% of the time.
+Reactions from the participants were experience-dependent.
+Some expressed that they ``Didn't need any more memories of work"; the others felt ``I used to work here, good memories, good vibes, good experience'', ``Nostalgic, reminds me of where i grew up".
 This percentage increases significantly if the Rewind contains the location visited least frequently by the participant.

### 2016-09-21 paper/uist_2016/paper.tex
fixed memory naming consistency

@@
 \begin{abstract}
-We introduce Rewind system which assists in the recall of semantic and episodic memory by automatically recreating interactive sceneries of past trips.
+We introduce Rewind system which assists in the recall of memory by automatically recreating interactive sceneries of past trips.
 Rewind system uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images.
@@
 Rewinds, and digitally-mediated memories in general, are meant to engage a person's memory.
-To find out what features make a digital memory memorable, we examined participant responses to whether or not they were able to remember the location shown in a photo (semantic memory) or recall the trip portrayed by a Rewind (episodic memory).
+To find out what features make a digital memory memorable, we examined participant responses to whether or not they were able to remember the location shown in a photo or recall the trip portrayed by a Rewind.
 Photo memorability is determined by whether or not the participant remembered the location depicted in a photo.
@@
 \subsubsection{Rewinds vs. Static Photos} 
-Our study reveals that participants have higher semantic memory of locations when presented with Rewinds than with static street-view photos ($\chi^2(1, N=356) = 96.987$, $p <.01$).
+Our study reveals that participants have higher memory of locations when presented with Rewinds than with static street-view photos ($\chi^2(1, N=356) = 96.987$, $p <.01$).
 When presented with a street-view photo generated from the participant's location data, participants were able to recognize the depicted location 49.7\% of the time.
@@
 Three participants who were unable to recall a location from a static photo actually recognized the location after seeing the accompanying Rewind.
-They expressed their contentment after watching the Rewind, proclaiming ``I recognize the photo now!'' When we evaluate Rewind memorability based on episodic memory rather than semantic memory, the results show that participants recalled the exact trip depicted by the Rewind 53.7\% of the time.
+They expressed their contentment after watching the Rewind, proclaiming ``I recognize the photo now!'' When we evaluate Rewind memorability based on trip memory rather than location memory, the results show that participants recalled the exact trip depicted by the Rewind 53.7\% of the time.
 %TODO make sure episodic memory is discussed in discussion section--visit frequency diminishes episodic memory

### 2016-09-21 paper/uist_2016/paper.tex
added more sig vals; fixed sig format

@@
 \subsubsection{Rewinds vs. Static Photos} 
-Our study reveals that participants have higher memory of locations when presented with Rewinds than with static street-view photos ($\chi^2(1, N=356) = 96.987$, $p <.01$).
+Our study reveals that participants have higher memory of locations when presented with Rewinds than with static street-view photos, $\chi^2(1, N=356) = 96.987$, $p <.01$.
 When presented with a street-view photo generated from the participant's location data, participants were able to recognize the depicted location 49.7\% of the time.
@@
 The more frequently a place was visited, the more likely it was that the participant remembered the location when it was shown to them at the study.
-In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places, with a significance at $\chi^2(1,128) = 14.458$, $p < 0.01$.
+In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places, with a significance at $\chi^2(1,N=128) = 14.458$, $p <.01$.
 This effect does not occur for trip memorability.
@@
 \subsubsection{GPS Usage}
-Our study also suggested that GPS users would benefit more from Rewinds, even though the difference was mildly significant by an increase about 15\%, $\chi^2(1, N=118) = 2.145$, $p = .0715 (<.1)$. 
+Our study also suggested that GPS users would benefit more from Rewinds, even though the difference was mildly significant by an increase about 15\%, $\chi^2(1, N=118) = 2.145$, $p =.0715 (<.1)$. 
 % h - prob explain this a little bit more
-
 % Our findings show that GPS usage significantly affect the rememberance of locations $\chi^2(1,179) = 8.734$, p < 0.01, but does not impose a siginificant effect on trip rememberance.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Our findings show that GPS usage significantly affect participants' remembrance of locations $\chi^2(1,179) = 8.734$, p = 0.0016 ($< 0.01$), but does not impose significant effects on trip remembrance $\chi^2(1,177) = 0.713$, p = 0.1992 ($> 0.05$).
+Our findings show that GPS usage significantly affect participants' remembrance of locations $\chi^2(1, N=179) = 8.734$, $p <.01$), but does not impose significant effects on trip remembrance $\chi^2(1, N=177) = 0.713$, $p >.05$).
 When asked whether they remember the location in a static photo, non-regular GPS users gave a positive answer 58\% of the time whereas regular GPS users gave a positive answer 33\% of the time.
@@
 Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way.
-For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1,94) = 31.812$, $p < 0.00001$.
+For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1, N=94) = 31.812$, $p <.00001$.
 On the other hand, trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and i walked a certain way -- don't usually take this route".
-Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.
+Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1, N=133) = 9.016$, $p <.01)$.
 
@@
 % GPS - 69%, non-GPS - 81%
-Our results show that participants who were non-regular GPS users found photos and Rewinds to be accurate to their memory more often than regular GPS users did.
+Our results show that participants who were non-regular GPS users found photos and Rewinds to be accurate to their memory more often than regular GPS users did in terms of percentage.
+Differences in Rewinds believability is statistically significant $\chi^2(1, N=128) = 2.917$, $p <.05$).
 Photos and Rewinds could only be considered accurate to a participant's memory if the participant first confirmed that they remembered the locations in them.
@@
 Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others.
+This difference is mildly significant $\chi^2(1, N=127) = 1.865$, $p <.1)$.
 The data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.
@@
 But participants who identified as infrequent travelers kept only 7\% of photos and 2\% of Rewinds.
+Although the effect on photo desirability is not siginificant, the difference is significant for Rewinds desirability, $\chi^2(1, N=179) = 9.754$, $p <.01$.
 The results show that those who consider themselves frequent travelers tend to place higher value on digital memories than those who do not identify as frequent travelers.

### 2016-09-21 paper/uist_2016/paper.tex

@@
 \subsubsection{Rewinds vs. Static Photos} 
-Our study reveals that participants have higher memory of locations when presented with Rewinds than with static street-view photos, $\chi^2(1, N=356) = 96.987$, $p <.01$.
+Our study reveals that participants have higher semantic memory of locations when presented with Rewinds than with static street-view photos ($\chi^2(1, N=356) = 96.987$, $p <.01$).
 When presented with a street-view photo generated from the participant's location data, participants were able to recognize the depicted location 49.7\% of the time.
@@
 As discussed above, this can be expected because cinematic media like Rewinds provide more context and retrieval cues.
-Three participants who were unable to recall a location from a static photo actually recognized the location after seeing the accompanying Rewind.
-They expressed their contentment after watching the Rewind, proclaiming ``I recognize the photo now!'' When we evaluate Rewind memorability based on trip memory rather than location memory, the results show that participants recalled the exact trip depicted by the Rewind 53.7\% of the time.
-%TODO make sure episodic memory is discussed in discussion section--visit frequency diminishes episodic memory
+Three participants (P4, P6, and P10) who were unable to recall a location from a static photo actually recognized the location after seeing the accompanying Rewind.
+They expressed their contentment after watching the Rewind, proclaiming ``I recognize the photo now!'' Further differences between Rewinds and static photos are discussed in the following sections.
+%TODO h - add another table, only abt memorability tho
 
-%TODO h - add another table, only abt memorability tho
+\subsubsection{Distance}
 %TODO  where is home? need to explain this part in system? make sure this is explained
-\subsubsection{Distance}
 % only affect location rememberance
@@
 % most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
-Location memorability and trip memorability are affected differently by frequency of visits (Table~\ref{table:betweensubjects}).
-Location memorability is highest for places that are most frequently visited by the participant, while trip memorability is highest for places that are least frequently visited.
-The more frequently a place was visited, the more likely it was that the participant remembered the location when it was shown to them at the study.
-In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places, with a significance at $\chi^2(1,N=128) = 14.458$, $p <.01$.
-This effect does not occur for trip memorability.
-In the most frequently visited places, trips are remembered 51\% of the time.
-Instead of seeing trip memorability decrease for least frequently visited places, this factor increases to 56\%.
-Our study also shows that comparing to static street-view images, recollection of trip memories using Rewinds is significantly improved for least frequently taken trips by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.
+Differences in photo memorability due to visit frequency were statistically significant, while differences in location memorability were not.
+Photo memorability is higher for locations that are most frequently visited by the participant, with a remembrance rate of 72.3\%.
+Photo remembrance rate for the least frequently visited locations is 35.8\%.
+This is statistically significant at $\chi^2(1,128) = 14.458$, $p < 0.01$.
 
-% Our study examined episodic processing in metric-specific groups, as well as the performance overall.
-Our study shows that comparing to static street-view images, recollection of event-driven memories using Rewinds is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.
+Between photos and Rewinds, photos had a higher remembrance rate for most frequently visited locations, with a difference of 20.2\% $\chi^2(1, N=20) = 3.215$, $p <.05$; and for least frequently visited locations Rewinds had a higher remembrance rate with a difference of 20.5\%, $\chi^2(1, N=161) = 5.977$, $p <.01$, suggesting again that photos and Rewinds may have different suitabilities as memory media.
 

### 2016-09-21 paper/uist_2016/paper.tex
added comments from Numair; added chi-squared test

@@
 \begin{abstract}
-We introduce Rewind system which assists in the recall of memory by automatically recreating interactive sceneries of past trips.
-Rewind system uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images.
+We introduce the Rewind system which assists in the recall of memory by automatically recreating interactive sceneries of past trips.
+The Rewind system uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images.
 Since the effectiveness of memory cues is determined by their level of integration with the target memory, images used in Rewind system are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience.
@@
 
+% h - Numair suggested "recall" as another keyword
 \keywords{
-Digital memories, geolocation, streetside images, travel.
+Digital memories, geolocation, streetside images, travel, recall.
 }
@@
 
-Geolocation data that can be automatically tracked and logged on a smartphone can be used to recreate context: to look up the weather at each moment, retrieve street side photos (e.g.
+Geolocation data that can be automatically tracked and logged on a smartphone can be used to recreate context: to look up the weather at each moment,
+% h - retrieve street side photos (for example, from Google Street View) at every step...transportation \cite{zheng2008learning} - suggested by Numair
+retrieve street side photos (e.g.
 from Google Street View) at every step, and compute the mode of transportation (e.g., \cite{zheng2008learning}) and nearby geographical features.
@@
 By picking a start and end location from a particular trip and generating a Rewind between these points, the user relives their memories in a continuous manner.
-Similarly in his famous seminal paper \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through``associative trails'', giving mankind the ability of``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''.
-Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one’s sensory experiences about past visits.
+Similarly in his seminal paper \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through``associative trails'', giving mankind the ability of``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''.
+Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one\’s sensory experiences about past visits.
 
@@
 Additionally, half of the participants were regular GPS users, which we defined as people who use GPS navigation even in locations already familiar to them.
+We used Chi-squared one-tail test for significance analysis.
 
-Our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media:
+Our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media.
 \begin{enumerate}

### 2016-09-21 paper/uist_2016/paper.tex
colon, table and apostrophe

@@
 Similarly in his seminal paper \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through``associative trails'', giving mankind the ability of``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''.
-Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one\’s sensory experiences about past visits.
+Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one’s sensory experiences about past visits.
 
@@
 Additionally, half of the participants were regular GPS users, which we defined as people who use GPS navigation even in locations already familiar to them.
-We used Chi-squared one-tail test for significance analysis.
 
-Our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media.
+Our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media:
 \begin{enumerate}
@@
 		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Believability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
-		& \begin{tabular}[c]{@{}c@{}}video\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}video\\ trip\end{tabular} & photo & video & photo & video \\ \hline
+		& \begin{tabular}[c]{@{}c@{}}Rewinds\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}Photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}Rewinds\\ trip\end{tabular} & Photo & Rewinds & Photo & Rewinds \\ \hline
 		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
@@
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.33} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.58} & 0.51 & 0.47 & 1.00 & 1.00 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 1.00} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.75} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.72} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.44} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.52} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.10} & \cellcolor[HTML]{ACDDAA}0.72 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.36} \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$ \\ p =0.0016\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$ \\ p = 0.3953\end{tabular}} & \multicolumn{2}{c|}{N/A} & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$ \\ p = 0.0028\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$ \\ p = 0.0001\end{tabular}} \\ \cline{2-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{Photo}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$ \\ p =0.0016\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$ \\ p = 0.3953\end{tabular}} & \multicolumn{2}{c|}{N/A} & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$ \\ p = 0.0028\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$ \\ p = 0.0001\end{tabular}} \\ \cline{2-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 58 & 119 & 120 & 57 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 94} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 39} & 5 & 8 & 18 & 71 & 64 & 10 & 46 & 80 \\ \cline{3-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.48 & 0.56 & 0.53 & 0.54 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.62} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.90} & 0.60 & 0.25 & 0.56 & 0.59 & 0.50 & 0.60 & 0.52 & 0.56 \\ \cline{3-17}
-\multicolumn{1}{|c|}{\multirow{-6}{*}{Memorability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$ \\ p =0.1992\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$ \\ p = 0.4478\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 9.016$ \\ p = 0.0013\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$ \\ p = 0.4467\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$ \\ p = 0.3987\end{tabular}} \\ \hline
+\multicolumn{1}{|c|}{\multirow{-6}{*}{Memorability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{Rewinds}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$ \\ p =0.1992\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$ \\ p = 0.4478\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 9.016$ \\ p = 0.0013\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$ \\ p = 0.4467\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$ \\ p = 0.3987\end{tabular}} \\ \hline
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 19 & 67 & 61 & 25 & \cellcolor[HTML]{ACDDAA}71 & \cellcolor[HTML]{ACDDAA}11 & 5 & 5 & 13 & 30 & 32 & 1 & 34 & 27 \\ \cline{3-17} 
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.68 & 0.81 & 0.77 & 0.80 & \cellcolor[HTML]{ACDDAA}0.82 & \cellcolor[HTML]{ACDDAA}0.45 & 0.80 & 0.60 & 0.69 & 0.90 & 0.75 & 0.00 & 0.71 & 0.89 \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$ \\ p = 0.2073\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$ \\ p = 0.4947\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 82) = 5.137$ \\ p = 0.0117\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$ \\ p= 0.1709\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$ \\ p =0.078\end{tabular}} \\ \cline{2-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{Photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$ \\ p = 0.2073\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$ \\ p = 0.4947\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 82) = 5.137$ \\ p = 0.0117\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$ \\ p= 0.1709\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$ \\ p =0.078\end{tabular}} \\ \cline{2-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}39 & \cellcolor[HTML]{ACDDAA}89 & \cellcolor[HTML]{ACDDAA}91 & \cellcolor[HTML]{ACDDAA}37 & 88 & 39 & 4 & 4 & 12 & 53 & 49 & 6 & 33 & 58 \\ \cline{3-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & 0.84 & 0.72 & 1.00 & 0.75 & 0.75 & 0.85 & 0.80 & 0.33 & 0.70 & 0.81 \\ \cline{3-17}
-\multicolumn{1}{|c|}{\multirow{-6}{*}{Believability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
+\multicolumn{1}{|c|}{\multirow{-6}{*}{Believability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{Rewinds}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 60 & 119 & 120 & 59 & 74 & 11 & 5 & 8 & 18 & 71 & 67 & 10 & 47 & 81 \\ \cline{3-17} 
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.13 & 0.92 & 0.13 & 0.07 & 0.12 & 0.18 & 0.20 & 0.38 & 0.06 & 0.07 & 0.13 & 0.10 & 0.15 & 0.10 \\ \cline{3-17} 
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$ \\ p = 0.2804\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$ \\ p = 0.3948\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$ \\ p = 0.1492\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$ \\ p = 0.2858\end{tabular}} \\ \cline{2-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{Photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$ \\ p = 0.2804\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$ \\ p = 0.3948\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$ \\ p = 0.1492\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$ \\ p = 0.2858\end{tabular}} \\ \cline{2-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 58} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 119} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 120} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 57} & 94 & 39 & 5 & 8 & 18 & 70 & 66 & 10 & 46 & 80 \\ \cline{3-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.09} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.02} & 0.13 & 0.26 & 0.00 & 0.00 & 0.11 & 0.10 & 0.20 & 0.40 & 0.11 & 0.18 \\ \cline{3-17}
-\multicolumn{1}{|c|}{\multirow{-6}{*}{Desirability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$ \\ p = 0.0034\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$ \\ p = 0.059\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$ \\ p= 0.0729\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$ \\ p = 0.2288\end{tabular}} \\ \hline
+\multicolumn{1}{|c|}{\multirow{-6}{*}{Desirability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{Rewinds}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$ \\ p = 0.0034\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$ \\ p = 0.059\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$ \\ p= 0.0729\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$ \\ p = 0.2288\end{tabular}} \\ \hline
 \end{tabular}

### 2016-09-21 paper/uist_2016/paper.tex
memorability & believability findings done

--- 2016-09-21 paper/uist_2016/paper.tex
@@
 The findings of our user study center on the participants’ relationships to the Rewinds generated from their location data compared to the static photos.
-We focus on the participants’ judgments of their Rewinds’ memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds.
+We focus on the participants’ judgments of their Rewinds’ memorability, believability, and desirability in comparison to their judgments of the photos.
 We also discuss the participants' interactions with and reactions to their Rewinds.
@@
 Distances ranged from 0 to 206,155 meters.
-For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 was 10--100 meters; Group 2 was 100--1,000 meters; Group 3 was 1,000--10,000 meters; Group 4 was 10,000--100,000 meters and Group 5 was 100,000--1,000,000 meters from the participant's home location.
+For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 was 10--100 meters; Group 2 was 100--1,000 meters; Group 3 was 1,000--10,000 meters; Group 4 was 10,000--100,000 meters; and Group 5 was 100,000--1,000,000 meters from the participant's home location.
 	\item Visit frequency: do participants react differently to Rewinds and static photos depicting locations they visit frequently compared to locations they rarely visit?
@@
 Rewinds, and digitally-mediated memories in general, are meant to engage a person's memory.
-To find out what features make a digital memory memorable, we examined participant responses to whether or not they were able to remember the location shown in a photo or recall the trip portrayed by a Rewind.
-Photo memorability is determined by whether or not the participant remembered the location depicted in a photo.
-Because a Rewind contains many locations, it would be unfair to evaluate the memorability of Rewind based on whether the participant remembers any locations in the Rewind.
-If participants do not recognize some depicted locations, they still have many other chances to pick out locations they remember.
-So, Rewind memorability is determined by whether or not the participant remembered and could distinguish the particular trip portrayed in a Rewind.
-In this section, we will look at differences in photo and Rewind memorability based on the five metrics discussed previously.
+To find out what features make a digital memory memorable, we examined participant responses to whether they were able to remember the location in a photo or recall the trip in a Rewind.
+Photo memorability is determined by whether or not the participant remembered the location depicted.
+Because a Rewind contains many locations, it would be unfair to evaluate its memorability based on whether the participant remembers any locations portrayed.
+So, Rewind memorability is determined by whether the participant remembered and could distinguish the particular trip taken.
+In this section, we look at differences in photo and Rewind memorability based on our five metrics.
 
@@
 \subsubsection{Rewinds vs. Static Photos} 
-Our study reveals that participants have higher semantic memory of locations when presented with Rewinds than with static street-view photos ($\chi^2(1, N=356) = 96.987$, $p <.01$).
-When presented with a street-view photo generated from the participant's location data, participants were able to recognize the depicted location 49.7\% of the time.
-Recognition rate of locations reached 96.6\% when participants were shown the accompanying Rewind.
+Our study reveals that participants have higher semantic memory of locations when presented with Rewinds than with static street-view photos ($\chi^2(1, N=356) = 96.987$, $p < .01$).
+When presented with a photo, participants were able to recognize the depicted location 49.7\% of the time.
+Recognition rate of locations reached 96.6\% when participants were shown Rewinds.
 As discussed above, this can be expected because cinematic media like Rewinds provide more context and retrieval cues.
-Three participants (P4, P6, and P10) who were unable to recall a location from a static photo actually recognized the location after seeing the accompanying Rewind.
-They expressed their contentment after watching the Rewind, proclaiming ``I recognize the photo now!'' Further differences between Rewinds and static photos are discussed in the following sections.
+Three participants (P4, P6, and P10) who were unable to recall a location from a static photo remembered the location only after seeing the accompanying Rewind.
+They expressed contentment after watching the Rewind, proclaiming ``I recognize the photo now!''
 %TODO h - add another table, only abt memorability tho
@@
 % 0 - 100%, 1 - 75%, 2 - 72%, 3 - 44%, 4 - 52%, 5 - 10%, $\chi^2(5,179) = 18.106$, p < 0.01
-The depicted location's distance away from the participant’s home had differing effects on photo memorability and Rewind memorability.
 Photo memorability and distance had a clearly linear relationship, while the relationship between Rewind memorability and distance was more nuanced.
 
-For photos, as the distance increased, memorability decreased, suggesting that locations further away from home were less likely to be remembered.
+For photos, as the distance increased, memorability decreased, suggesting that locations farther away from home were less likely to be remembered.
 In Distance Group 0, or the participant's home location, location recall was 100\%.
-One participant, upon recognition, explained that she knew the location because ``my husband's car is in the driveway.'' Further away in Distance Group 1, remembrance dropped to 75\%, then later down to 10\% for Distance Group 5, which represented the locations furthest away from home.
+One participant, upon recognition, explained that she knew the location because ``my husband's car is in the driveway.'' By Distance Group 5, which represented the locations farthest away from home, remembrance was down to 10\%.
 These percentages are statistically significant, with a p-value of 0.0028.
@@
 For Rewind memorability, there was no statistical significance.
-Our data does show, however, that Rewind remembrance was largely the same for most distance groups, except for distances that were close to home in Distance Group 1.
-While remembrance for all distance groups was between 50--60\%, remembrance for Rewinds in Distance Group 1 was 25\%.
-This data suggests that participants often did not remember or could not distinguish the exact trips that occurred in locations close to their home.
-This is where most trips happen, and therefore competition between similar memories would make it harder for a person to distinguish the specific trip they were on that generated the Rewind.
+Our data does show, however, that Rewind remembrance was largely the same for most distance groups, except in Distance Group 1.
+Remembrance for all distance groups was between 50--60\%, but was 25\% in Distance Group 1.
+This data suggests that participants often could not distinguish the exact trips that occurred in locations close to their home.
+This is where most trips happen, so competition between similar memories would make it harder to distinguish the specific trip that generated the Rewind.
 
@@
 % most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
-Differences in photo memorability due to visit frequency were statistically significant, while differences in location memorability were not.
+% Differences in photo memorability due to visit frequency were statistically significant, while differences in location memorability were not.
 Photo memorability is higher for locations that are most frequently visited by the participant, with a remembrance rate of 72.3\%.
@@
 
-Between photos and Rewinds, photos had a higher remembrance rate for most frequently visited locations, with a difference of 20.2\% $\chi^2(1, N=20) = 3.215$, $p <.05$; and for least frequently visited locations Rewinds had a higher remembrance rate with a difference of 20.5\%, $\chi^2(1, N=161) = 5.977$, $p <.01$, suggesting again that photos and Rewinds may have different suitabilities as memory media.
+Between photos and Rewinds, photos had a higher remembrance rate for most frequently visited locations, with a difference of 20.2\%, $\chi^2(1, N=20) = 3.215$, $p < .05$.
+In least frequently visited locations, Rewinds had a higher remembrance rate with a difference of 20.5\%, $\chi^2(1, N=161) = 5.977$, $p < .01$, suggesting again that photos and Rewinds may have different suitabilities as memory media.
+
+\subsubsection{Travel Companions}
+% trip accompanies have siginificant effects on both location and trip rememberance. 
+% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
+% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
+Our findings suggest that the presence of travel companions increases likelihood of Rewind remembrance.
+Rewinds depicting trips where participants believed they were traveling alone had a remembrance rate of 62\%, while trips where participants had a traveling companion were remembered 90\% of the time, $\chi^2(1, N=133) = 9.016$, $p < .01)$.
+One participant recalled a particular trip because ``I remembered my friend and I walked a certain way--I don't usually take this route.'' Another participant recalled that ``I went out with roommates to a bar.
+We took a weird route, different from my usual route."
+
+\subsubsection{Frequent Travelers}
+% has no siginifant effects on location no trip rememberance
+% needing explaination perhaps?
+We found no statistically significant effect on photo and Rewind memorability from participants' identification as frequent travelers.
 
 \subsubsection{GPS Usage}
-Our study also suggested that GPS users would benefit more from Rewinds, even though the difference was mildly significant by an increase about 15\%, $\chi^2(1, N=118) = 2.145$, $p =.0715 (<.1)$. 
+Our findings suggests that Rewinds, rather than photos, may be a more suitable form of digital memory for GPS users.
+Remembrance of Rewinds was higher than remembrance of photos for regular GPS users by a difference of 15\%, $\chi^2(1, N=118) = 2.145$, $p = .0715 (<.1)$.
+There was no significant difference between photo remembrance and Rewind remembrance in non-regular GPS users.
 % h - prob explain this a little bit more
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Our findings show that GPS usage significantly affect participants' remembrance of locations $\chi^2(1, N=179) = 8.734$, $p <.01$), but does not impose significant effects on trip remembrance $\chi^2(1, N=177) = 0.713$, $p >.05$).
-When asked whether they remember the location in a static photo, non-regular GPS users gave a positive answer 58\% of the time whereas regular GPS users gave a positive answer 33\% of the time.
-Although the difference between non-regular and regular GPS users' trip remembrance is not statistically significance, the between-subject percentage values still lean towards the observation that it is perhaps easier for non-GPS users to recall episodic memories from external memory cues, given that the total trip remembrance rate for non-GPS users is 48\% and that of GPS users is 56\%.
-Since regular GPS users are frequently directed step-by-step on how to navigate through their environment, they may not need to pay as much attention to their surroundings, leading to potentially diminished locational awareness which could be the reason why regular GPS users had a lower remembrance rate for their ambience, particularly locations.
-One non-regular GPS user mentioned that ``I identify by landmarks'', yet this is something that regular GPS users may pay less attention to.
-\\
 
-\subsubsection{Frequent Travelers}
-% has no siginifant effects on location no trip rememberance
-% needing explaination perhaps?
-Although location rememberance is slightly higher for frequent traveler (51\% for frequent and 48\% for non-frequent), and trip rememberance is slightly higher for non-frequent traveler (53\% for frequent and 54\% for non-frequent), our study has not found these variances statistically significant.
-
-\subsubsection{Travel Companions}
-% trip accompanies have siginificant effects on both location and trip rememberance. 
-% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
-% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
-Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way.
-For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1, N=94) = 31.812$, $p <.00001$.
-On the other hand, trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and i walked a certain way -- don't usually take this route".
-Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1, N=133) = 9.016$, $p <.01)$.
+Our findings show that GPS usage significantly affected photo remembrance (Table 2), but not Rewind remembrance.
+Non-regular GPS users recalled the location in a photo 58\% of the time whereas regular GPS users recalled the location 33\% of the time.
+A regular GPS user mentioned during the study that ``I don't really pay attention to my surroundings when I'm driving.
+I'm focused on the GPS and the road.''
 
@@
 \subsection{Believability}
-Rewinds should be believable as memories, and be able to serve as digitally-sourced memories of locations and trips.
-For that purpose, we define the believability of a Rewind as its accuracy to the participant's memories.
-Here we will look at how GPS usage and visit frequency affect participants' believability judgments, and discuss the features that participants pointed out as either contributing to or detracting from a Rewind's believability.
+Rewinds should be believable as digitally-sourced memories, so we define the believability of a Rewind as its accuracy to the participant's memories.
+For distance and visit frequency, we found no statistically significant results, but in addition to our five metrics, we solicited other factors that affected a photo or Rewind's believability from participants.
 
-\subsubsection{GPS Usage}
-% no significant effects on location belivability $\chi^2(1,86) = 0.666$, p = 0.2073(> 0.05)
-% signifant effects on trip belivability $\chi^2(1,128) = 2.917$, p = 0.0483(< 0.05)
-% GPS - 69%, non-GPS - 81%
-Our results show that participants who were non-regular GPS users found photos and Rewinds to be accurate to their memory more often than regular GPS users did in terms of percentage.
-Differences in Rewinds believability is statistically significant $\chi^2(1, N=128) = 2.917$, $p <.05$).
-Photos and Rewinds could only be considered accurate to a participant's memory if the participant first confirmed that they remembered the locations in them.
-The results in this section reflect percentages from a total pool of only photos and Rewinds that have remembered locations.
-Regular GPS users found 65\% of photos and 45\% of Rewinds accurate to their memory out of the photos and Rewinds in which they remembered the locations.
-Participants who did not regularly use GPS found 78\% of photos and 63\% of Rewinds accurate to their memory.
-So far, our findings show that regular GPS users remembered the locations in their digital memories less often, and from the locations they did remember, they were less likely to find a photo or Rewind accurate to their memory.
-One participant who identified as a regular GPS user said, ``I really don't pay attention to my surroundings when I'm driving.
-I'm focused on the GPS and the road,'' when asked about the accuracy of a trip.
+%\subsubsection{Distance}
+% no ignificant effects on photo/location belivability $\chi^2(5,86) = 7.745$, p = 0.1709 (> 0.05)
+% significant effects on video/trip belivability if we use alpha = 0.1 - $\chi^2(5,128) = 10.093$, p = 0.0726(< 0.1)
+% 0 - 100%, 1 - 75%, 2 - 75%, 3 - 85%, 4 - 80%, 5 - 33%
 
-Our results show that GPS usage influences what features participants pick out when deciding whether Rewinds are accurate reflections of their own memories of their trips.
-When we split the responses of regular GPS users from the other participants' responses, we saw that GPS users looked at signs in the Rewind the most to determine accuracy.
-Participants who were not regular GPS users cited the route and surrounding landmarks as features which made the Rewind believable as memories.
-
-\subsubsection{Frequent Travelers}
-% no significant effects on photo belivability $\chi^2(1,86) = 0$, p = 0.4947(> 0.05)
-% significant effects on video belivability $\chi^2(1,128) = 5.837$, p = 0.0079 (< 0.01)
-% frequent - 86%, non-frequent - 65%
+%\subsubsection{Visit Frequency}
+% significant effects on photo belivability if we use alpha = 0.1 - $\chi^2(1,61) = 2.012$, p = 0.078(< 0.1)
+% most frequently visited location - 71%, least frequently visited location - 89%
+% no significant effects on video/trip belivability $\chi^2(1,91) = 0.951$, p = 0.1647(> 0.05)
+% trip that include most frequently visited locations  -  70%, trip that include least frequently visited locations - 81%
+%We found that the more visits a location had, the less likely it was for the Rewind associated with it to be judged as accurate by the participant.
+Trips with a location that was visited most frequently by the participant were said to be accurate 75\% of the time.
+The more a person visits a location, the more they may notice inconsistencies between the actual place and a digitally-fabricated memory of it.
+Trips with a location that was visited least frequently had a higher accuracy rating of 82\%.
 
@@
 % traveling alone - 84%, not alone - 72%
-Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept.
-Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep.
-Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others.
-This difference is mildly significant $\chi^2(1, N=127) = 1.865$, $p <.1)$.
-The data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.
+Our findings show that in both photos and Rewinds, believability was higher when participants were traveling alone.
+For photos, the difference in believability between those traveling alone and those traveling with company was 37\%, $\chi^2(1, N=82) = 5.137$, $p < .05$.
+For Rewinds, the difference was 12\%, $\chi^2(1, 127) = 1.865$, $p = 0.086 (<.1)$.
+The smaller difference suggests that Rewinds are more believable than photos for trips taken with company.
 
-\subsubsection{Distance}
-% no ignificant effects on photo/location belivability $\chi^2(5,86) = 7.745$, p = 0.1709 (> 0.05)
-% significant effects on video/trip belivability if we use alpha = 0.1 - $\chi^2(5,128) = 10.093$, p = 0.0726(< 0.1)
-% 0 - 100%, 1 - 75%, 2 - 75%, 3 - 85%, 4 - 80%, 5 - 33%
+\subsubsection{Frequent Travelers}
+% no significant effects on photo belivability $\chi^2(1,86) = 0$, p = 0.4947(> 0.05)
+% significant effects on video belivability $\chi^2(1,128) = 5.837$, p = 0.0079 (< 0.01)
+% frequent - 86%, non-frequent - 65%
+Participants who identified as frequent travelers found 86\% of Rewinds believable and accurate to their memory, while non-frequent travelers found 65\% of Rewinds believable, $\chi^2(1, 128) = 5.835$
+$p < .05$. This suggests that Rewinds would be more suitable for a particular type of person.
 
-\subsubsection{Visit Frequency}
-% significant effects on photo belivability if we use alpha = 0.1 - $\chi^2(1,61) = 2.012$, p = 0.078(< 0.1)
-% most frequently visited location - 71%, least frequently visited location - 89%
-% no significant effects on video/trip belivability $\chi^2(1,91) = 0.951$, p = 0.1647(> 0.05)
-% trip that include most frequently visited locations  -  70%, trip that include least frequently visited locations - 81%
-We found that the more visits a location had, the less likely it was for the Rewind associated with it to be judged as accurate by the participant.
-Trips with a location that was visited most frequently by the participant were said to be accurate 75\% of the time.
-The more a person visits a location, the more they may notice inconsistencies between the actual place and a digitally-fabricated memory of it.
-Trips with a location that was visited least frequently had a higher accuracy rating of 82\%.
+\subsubsection{GPS Usage}
+% no significant effects on location belivability $\chi^2(1,86) = 0.666$, p = 0.2073(> 0.05)
+% signifant effects on trip belivability $\chi^2(1,128) = 2.917$, p = 0.0483(< 0.05)
+% GPS - 69%, non-GPS - 81%
+Our results show that participants who were non-regular GPS users found Rewinds believable more often than regular GPS users, suggesting the appropriate audience for Rewinds.
+Regular GPS users found Rewinds believable 69\% of the time, while non-regular users found Rewinds believable 84\% of the time, $\chi^2(1, 128) = 2.917$, $p < .05$.
 
-\subsubsection{Other Variables}
-To get a better understanding of what the important features of locational memories are, we looked at participants' responses to why they thought a Rewind was or was not accurate to their memory.
+\subsubsection{Other factors}
 Participants attributed the accuracy of a Rewind to the presence of different man-made structures.
 The most highly occurring answers to why a Rewind was accurate were: the route, the highways, roads, and streets, the signs, the landmarks, and the buildings.
-The reasons why a Rewind did not seem accurate to participants' memories included more temporal and environmental features.
-When participants responded that a Rewind was not accurate to their memory, they cited the streets, the season and foliage, the time of day, and the angle the Rewind viewed the world at as factors of inaccuracy.
+The reasons why a Rewind did not seem accurate to participants' memories included more temporal and environmental features: the season and foliage, the time of day, and the angle of view.
+One participant said that ``things look a little odd.
+It's too bright for the time of day,'' and another insisted ``it should be night.''
 
@@
 % alone - 13%, not alone - 26%
+Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept.
+Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep.
+Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others.
+This difference is mildly significant $\chi^2(1, N=127) = 1.865$, $p <.1)$.
+The data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.
 

### 2016-09-21 paper/uist_2016/paper.tex

@@
 By picking a start and end location from a particular trip and generating a Rewind between these points, the user relives their memories in a continuous manner.
-Similarly in his famous seminal paper \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through``associative trails'', giving mankind the ability of``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''.
+Similarly in his seminal paper \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through``associative trails'', giving mankind the ability of``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''.
 Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one’s sensory experiences about past visits.

### 2016-09-21 paper/uist_2016/paper.tex
edits in findings and later

--- 2016-09-21 paper/uist_2016/paper.tex
@@
 By picking a start and end location from a particular trip and generating a Rewind between these points, the user relives their memories in a continuous manner.
-Similarly in his seminal paper \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through``associative trails'', giving mankind the ability of``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''.
-Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one’s sensory experiences about past visits.
+Similarly in his seminal paper \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through ``associative trails'', giving mankind the ability of ``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''.
+Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one's sensory experiences about past visits.
 
@@
 \section{Findings}
-The findings of our user study center on the participants’ relationships to the Rewinds generated from their location data compared to the static photos.
-We focus on the participants’ judgments of their Rewinds’ memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds.
-We also discuss the participants' interactions with and reactions to their Rewinds.
+The findings of our user study center on the participants' relationships to the Rewinds generated from their location data compared to the static photos.
+We focus on the participants' judgments of their Rewinds' memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds (Table \ref{table:Rewindvsphotos}).
+%We also discuss the participants' interactions with and reactions to their Rewinds.
 The results use data from the user studies conducted with 12 men and 6 women.
-Half of the participants identified themselves as frequent travelers.
+Half identified themselves as frequent travelers, and half said they were regular GPS users, which we defined as people who use GPS navigation even in locations already familiar to them.
+%Half of the participants identified themselves as frequent travelers.
 Additionally, half of the participants were regular GPS users, which we defined as people who use GPS navigation even in locations already familiar to them.
+%We used Chi-squared one-tail test for significance analysis.
 
-Our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media:
+Besides a comparison between Rewinds and photos, our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media (Table \ref{table:betweensubjects}).
 \begin{enumerate}
@@
 		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Believability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
-		& \begin{tabular}[c]{@{}c@{}}Rewinds\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}Photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}Rewinds\\ trip\end{tabular} & Photo & Rewinds & Photo & Rewinds \\ \hline
+		& \begin{tabular}[c]{@{}c@{}}video\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}video\\ trip\end{tabular} & photo & video & photo & video \\ \hline
 		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
@@
 	\end{tabular}
+\label{table:Rewindvsphotos}
 \end{table*}
@@
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.33} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.58} & 0.51 & 0.47 & 1.00 & 1.00 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 1.00} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.75} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.72} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.44} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.52} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.10} & \cellcolor[HTML]{ACDDAA}0.72 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.36} \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{Photo}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$ \\ p =0.0016\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$ \\ p = 0.3953\end{tabular}} & \multicolumn{2}{c|}{N/A} & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$ \\ p = 0.0028\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$ \\ p = 0.0001\end{tabular}} \\ \cline{2-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$ \\ p =0.0016\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$ \\ p = 0.3953\end{tabular}} & \multicolumn{2}{c|}{N/A} & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$ \\ p = 0.0028\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$ \\ p = 0.0001\end{tabular}} \\ \cline{2-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 58 & 119 & 120 & 57 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 94} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 39} & 5 & 8 & 18 & 71 & 64 & 10 & 46 & 80 \\ \cline{3-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.48 & 0.56 & 0.53 & 0.54 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.62} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.90} & 0.60 & 0.25 & 0.56 & 0.59 & 0.50 & 0.60 & 0.52 & 0.56 \\ \cline{3-17}
-\multicolumn{1}{|c|}{\multirow{-6}{*}{Memorability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{Rewinds}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$ \\ p =0.1992\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$ \\ p = 0.4478\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 9.016$ \\ p = 0.0013\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$ \\ p = 0.4467\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$ \\ p = 0.3987\end{tabular}} \\ \hline
+\multicolumn{1}{|c|}{\multirow{-6}{*}{Memorability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$ \\ p =0.1992\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$ \\ p = 0.4478\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 9.016$ \\ p = 0.0013\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$ \\ p = 0.4467\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$ \\ p = 0.3987\end{tabular}} \\ \hline
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 19 & 67 & 61 & 25 & \cellcolor[HTML]{ACDDAA}71 & \cellcolor[HTML]{ACDDAA}11 & 5 & 5 & 13 & 30 & 32 & 1 & 34 & 27 \\ \cline{3-17} 
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.68 & 0.81 & 0.77 & 0.80 & \cellcolor[HTML]{ACDDAA}0.82 & \cellcolor[HTML]{ACDDAA}0.45 & 0.80 & 0.60 & 0.69 & 0.90 & 0.75 & 0.00 & 0.71 & 0.89 \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{Photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$ \\ p = 0.2073\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$ \\ p = 0.4947\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 82) = 5.137$ \\ p = 0.0117\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$ \\ p= 0.1709\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$ \\ p =0.078\end{tabular}} \\ \cline{2-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$ \\ p = 0.2073\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$ \\ p = 0.4947\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 82) = 5.137$ \\ p = 0.0117\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$ \\ p= 0.1709\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$ \\ p =0.078\end{tabular}} \\ \cline{2-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}39 & \cellcolor[HTML]{ACDDAA}89 & \cellcolor[HTML]{ACDDAA}91 & \cellcolor[HTML]{ACDDAA}37 & 88 & 39 & 4 & 4 & 12 & 53 & 49 & 6 & 33 & 58 \\ \cline{3-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & 0.84 & 0.72 & 1.00 & 0.75 & 0.75 & 0.85 & 0.80 & 0.33 & 0.70 & 0.81 \\ \cline{3-17}
-\multicolumn{1}{|c|}{\multirow{-6}{*}{Believability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{Rewinds}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
+\multicolumn{1}{|c|}{\multirow{-6}{*}{Believability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 60 & 119 & 120 & 59 & 74 & 11 & 5 & 8 & 18 & 71 & 67 & 10 & 47 & 81 \\ \cline{3-17} 
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.13 & 0.92 & 0.13 & 0.07 & 0.12 & 0.18 & 0.20 & 0.38 & 0.06 & 0.07 & 0.13 & 0.10 & 0.15 & 0.10 \\ \cline{3-17} 
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{Photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$ \\ p = 0.2804\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$ \\ p = 0.3948\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$ \\ p = 0.1492\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$ \\ p = 0.2858\end{tabular}} \\ \cline{2-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$ \\ p = 0.2804\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$ \\ p = 0.3948\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$ \\ p = 0.1492\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$ \\ p = 0.2858\end{tabular}} \\ \cline{2-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 58} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 119} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 120} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 57} & 94 & 39 & 5 & 8 & 18 & 70 & 66 & 10 & 46 & 80 \\ \cline{3-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.09} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.02} & 0.13 & 0.26 & 0.00 & 0.00 & 0.11 & 0.10 & 0.20 & 0.40 & 0.11 & 0.18 \\ \cline{3-17}
-\multicolumn{1}{|c|}{\multirow{-6}{*}{Desirability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{Rewinds}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$ \\ p = 0.0034\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$ \\ p = 0.059\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$ \\ p= 0.0729\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$ \\ p = 0.2288\end{tabular}} \\ \hline
+\multicolumn{1}{|c|}{\multirow{-6}{*}{Desirability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$ \\ p = 0.0034\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$ \\ p = 0.059\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$ \\ p= 0.0729\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$ \\ p = 0.2288\end{tabular}} \\ \hline
 \end{tabular}
@@
 
-\section{Memorability}
+\subsection{Memorability}
 Rewinds, and digitally-mediated memories in general, are meant to engage a person's memory.
-To find out what features make a digital memory memorable, we examined participant responses to whether or not they were able to remember the location shown in a photo or recall the trip portrayed by a Rewind.
+To identify what features make a digital memory memorable, we examined participant responses to whether or not they were able to remember the location shown in a photo or recall the trip portrayed by a Rewind.
 Photo memorability is determined by whether or not the participant remembered the location depicted in a photo.
@@
 % h - deleted participants # for consistencies - P4, P6 and P10 for future reference
-\subsubsection{Rewinds vs. Static Photos} 
+%\subsubsection{Rewinds vs. Static Photos} 
 Our study reveals that participants have higher semantic memory of locations when presented with Rewinds than with static street-view photos ($\chi^2(1, N=356) = 96.987$, $p <.01$).
@@
 % 0 - 100%, 1 - 75%, 2 - 72%, 3 - 44%, 4 - 52%, 5 - 10%, $\chi^2(5,179) = 18.106$, p < 0.01
-The depicted location's distance away from the participant’s home had differing effects on photo memorability and Rewind memorability.
+The depicted location's distance away from the participant's home had differing effects on photo memorability and Rewind memorability.
 Photo memorability and distance had a clearly linear relationship, while the relationship between Rewind memorability and distance was more nuanced.
@@
 One participant, upon recognition, explained that she knew the location because ``my husband's car is in the driveway.'' Further away in Distance Group 1, remembrance dropped to 75\%, then later down to 10\% for Distance Group 5, which represented the locations furthest away from home.
-These percentages are statistically significant, with a p-value of 0.0028.
+These percentages are statistically significant ($p < 0.01$).%, with a p-value of 0.0028.
 
@@
 
-When comparing photo memorability and Rewind memorability based on distance, our study shows that for trips close to home (Distance Group 1), photo remembrance was higher by 50\%, $\chi^2(1, 16) = 2.25$, $p = 0.067$.
+When comparing photo and Rewind memorability based on distance, our study shows that for trips close to home (Distance Group 1), photo remembrance was higher by 50\%, $\chi^2(1, 16) = 2.25$, $p = 0.067$.
 For trips far from home (Distance Group 5), Rewind remembrance was higher by 50\%, $\chi^2(1, 20) = 3.516$, $p < 0.05$.
@@
 
-Between photos and Rewinds, photos had a higher remembrance rate for most frequently visited locations, with a difference of 20.2\% $\chi^2(1, N=20) = 3.215$, $p <.05$; and for least frequently visited locations Rewinds had a higher remembrance rate with a difference of 20.5\%, $\chi^2(1, N=161) = 5.977$, $p <.01$, suggesting again that photos and Rewinds may have different suitabilities as memory media.
+Between photos and Rewinds, users were most likely to remember photos for most frequently visited locations, with a difference of 20.2\% $\chi^2(1, N=20) = 3.215$, $p <.05$; and for least frequently visited locations Rewinds had a higher remembrance rate with a difference of 20.5\%, $\chi^2(1, N=161) = 5.977$, $p <.01$, suggesting again that photos and Rewinds may have different suitabilities as memory media.
 
@@
 Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way.
-For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1, N=94) = 31.812$, $p <.00001$.
-On the other hand, trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and i walked a certain way -- don't usually take this route".
+For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compared to 55\% reported by participants who believed that they traveled in groups, with $\chi^2(1, N=94) = 31.812$, $p <.00001$.
+On the other hand, trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and I walked a certain way -- don't usually take this route".
 Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1, N=133) = 9.016$, $p <.01)$.
@@
 \subsection{Believability}
-Rewinds should be believable as memories, and be able to serve as digitally-sourced memories of locations and trips.
-For that purpose, we define the believability of a Rewind as its accuracy to the participant's memories.
+%Rewinds should be believable as memories, and be able to serve as digitally-sourced memories of locations and trips. For that purpose,
+We define the believability of a Rewind as its accuracy to the participant's memories.
+Overall, users were more likely to believe a Rewind was part of their memory (80\% to 78\%), but this was not statistically significnat.
 Here we will look at how GPS usage and visit frequency affect participants' believability judgments, and discuss the features that participants pointed out as either contributing to or detracting from a Rewind's believability.
@@
 % GPS - 69%, non-GPS - 81%
-Our results show that participants who were non-regular GPS users found photos and Rewinds to be accurate to their memory more often than regular GPS users did in terms of percentage.
-Differences in Rewinds believability is statistically significant $\chi^2(1, N=128) = 2.917$, $p <.05$).
+When splitting users between GPS users and non-GPS users, participants who were non-regular GPS users found photos and Rewinds to be accurate to their memory more often than regular GPS users did in terms of percentage ($\chi^2(1, N=128) = 2.917$, $p <.05$).
 Photos and Rewinds could only be considered accurate to a participant's memory if the participant first confirmed that they remembered the locations in them.
-The results in this section reflect percentages from a total pool of only photos and Rewinds that have remembered locations.
+% The results in this section reflect percentages from a total pool of only photos and Rewinds that have remembered locations.
 Regular GPS users found 65\% of photos and 45\% of Rewinds accurate to their memory out of the photos and Rewinds in which they remembered the locations.
 Participants who did not regularly use GPS found 78\% of photos and 63\% of Rewinds accurate to their memory.
-So far, our findings show that regular GPS users remembered the locations in their digital memories less often, and from the locations they did remember, they were less likely to find a photo or Rewind accurate to their memory.
+%So far, our findings show that
+So regular GPS users remembered the locations in their digital memories less often, and from the locations they did remember, they were less likely to find a photo or Rewind accurate to their memory.
 One participant who identified as a regular GPS user said, ``I really don't pay attention to my surroundings when I'm driving.
 I'm focused on the GPS and the road,'' when asked about the accuracy of a trip.
-
-Our results show that GPS usage influences what features participants pick out when deciding whether Rewinds are accurate reflections of their own memories of their trips.
+%Our results show that GPS usage influences what features participants pick out when deciding whether Rewinds are accurate reflections of their own memories of their trips.
 When we split the responses of regular GPS users from the other participants' responses, we saw that GPS users looked at signs in the Rewind the most to determine accuracy.
@@
 
-\subsubsection{Frequent Travelers}
+%\subsubsection{Frequent Travelers}
 % no significant effects on photo belivability $\chi^2(1,86) = 0$, p = 0.4947(> 0.05)
@@
 % traveling alone - 84%, not alone - 72%
-Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept.
+Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind was desired to be kept.
 Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep.
@@
 
-\subsubsection{Distance}
-% no ignificant effects on photo/location belivability $\chi^2(5,86) = 7.745$, p = 0.1709 (> 0.05)
+%\subsubsection{Distance}
+% no significant effects on photo/location belivability $\chi^2(5,86) = 7.745$, p = 0.1709 (> 0.05)
 % significant effects on video/trip belivability if we use alpha = 0.1 - $\chi^2(5,128) = 10.093$, p = 0.0726(< 0.1)
@@
 \subsection{Desirability}
-For Rewinds to be useful, they need to have value to their owners.
+For memories to be useful, they need to have value to their owners.
 We measured the value of photos and Rewinds by asking participants if they would want to keep the photo or Rewind after seeing it.
@@
 
-\subsubsection{GPS usage}
+%\subsubsection{GPS usage}
 % no significant effects on photo desirability $\chi^2(1,179) = 0.338$, p = 0.2804(> 0.05)
@@
 
-\subsection{Frequent Travellers}
+\subsubsection{Frequent Travelers}
 % no significant effects on photo desirability $\chi^2(1,179) = 0.828$, p = 0.1814(> 0.05)
@@
 
-\subsubsection{Travel Companions}
+%\subsubsection{Travel Companions}
 % no significant effects on photo desirability $\chi^2(1,94) = 0.071$, p = 0.3948(> 0.05)
@@
 
-\subsubsection{Distance}
+%\subsubsection{Distance}
 % no significant effects on photo desirability $\chi^2(1,179) = 8.131$, p = 0.1492(> 0.05)

### 2016-09-21 paper/uist_2016/paper.tex

--- 2016-09-21 paper/uist_2016/paper.tex
@@
 By picking a start and end location from a particular trip and generating a Rewind between these points, the user relives their memories in a continuous manner.
-Similarly in his seminal paper \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through``associative trails'', giving mankind the ability of``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''.
+Similarly in his seminal paper, \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through ``associative trails'', giving mankind the ability of ``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''.
 Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one’s sensory experiences about past visits.
@@
 \section{Findings}
-The findings of our user study center on the participants’ relationships to the Rewinds generated from their location data compared to the static photos.
-We focus on the participants’ judgments of their Rewinds’ memorability, believability, and desirability in comparison to their judgments of the photos.
-We also discuss the participants' interactions with and reactions to their Rewinds.
+The findings of our user study center on the participants' relationships to the Rewinds generated from their location data compared to the static photos.
+We focus on the participants' judgments of their Rewinds' memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds (Table \ref{table:Rewindvsphotos}).
+%We also discuss the participants' interactions with and reactions to their Rewinds.
 The results use data from the user studies conducted with 12 men and 6 women.
-Half of the participants identified themselves as frequent travelers.
+Half identified themselves as frequent travelers, and half said they were regular GPS users, which we defined as people who use GPS navigation even in locations already familiar to them.
+%Half of the participants identified themselves as frequent travelers.
 Additionally, half of the participants were regular GPS users, which we defined as people who use GPS navigation even in locations already familiar to them.
+%We used Chi-squared one-tail test for significance analysis.
 
-Our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media:
+Besides a comparison between Rewinds and photos, our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media (Table \ref{table:betweensubjects}).
 \begin{enumerate}
@@
 % h - deleted participants # for consistencies - P4, P6 and P10 for future reference
-\subsubsection{Rewinds vs. Static Photos} 
 Our study reveals that participants have higher semantic memory of locations when presented with Rewinds than with static street-view photos ($\chi^2(1, N=356) = 96.987$, $p < .01$).
@@
 One participant, upon recognition, explained that she knew the location because ``my husband's car is in the driveway.'' By Distance Group 5, which represented the locations farthest away from home, remembrance was down to 10\%.
-These percentages are statistically significant, with a p-value of 0.0028.
+These percentages are statistically significant ($p < 0.01$).
 
@@
 
-Between photos and Rewinds, photos had a higher remembrance rate for most frequently visited locations, with a difference of 20.2\%, $\chi^2(1, N=20) = 3.215$, $p < .05$.
+Between photos and Rewinds, users were most likely to remember photos for most frequently visited locations, with a difference of 20.2\%, $\chi^2(1, N=20) = 3.215$, $p < .05$.
 In least frequently visited locations, Rewinds had a higher remembrance rate with a difference of 20.5\%, $\chi^2(1, N=161) = 5.977$, $p < .01$, suggesting again that photos and Rewinds may have different suitabilities as memory media.
@@
 
-\subsubsection{Frequent Travelers}
+% \subsubsection{Frequent Travelers}
 % has no siginifant effects on location no trip rememberance
 % needing explaination perhaps?
-We found no statistically significant effect on photo and Rewind memorability from participants' identification as frequent travelers.
+% We found no statistically significant effect on photo and Rewind memorability from participants' identification as frequent travelers.
 
 \subsubsection{GPS Usage}
-Our findings suggests that Rewinds, rather than photos, may be a more suitable form of digital memory for GPS users.
-Remembrance of Rewinds was higher than remembrance of photos for regular GPS users by a difference of 15\%, $\chi^2(1, N=118) = 2.145$, $p = .0715 (<.1)$.
-There was no significant difference between photo remembrance and Rewind remembrance in non-regular GPS users.
+Our findings show that GPS usage significantly affected photo remembrance (Table 2), but not Rewind remembrance.
+Non-regular GPS users recalled the location in a photo 58\% of the time whereas regular GPS users recalled the location 33\% of the time.
+A regular GPS user mentioned during the study that ``I don't really pay attention to my surroundings when I'm driving.
+I'm focused on the GPS and the road.''
 % h - prob explain this a little bit more
@@
 
-Our findings show that GPS usage significantly affected photo remembrance (Table 2), but not Rewind remembrance.
-Non-regular GPS users recalled the location in a photo 58\% of the time whereas regular GPS users recalled the location 33\% of the time.
-A regular GPS user mentioned during the study that ``I don't really pay attention to my surroundings when I'm driving.
-I'm focused on the GPS and the road.''
+\subsubsection{Travel Companions}
+% trip accompanies have siginificant effects on both location and trip rememberance. 
+% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
+% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
+Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way.
+For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compared to 55\% reported by participants who believed that they traveled in groups, with $\chi^2(1, N=94) = 31.812$, $p <.00001$.
+On the other hand, trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and I walked a certain way -- don't usually take this route".
+Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1, N=133) = 9.016$, $p <.01)$.
 
@@
 \subsection{Believability}
+%Rewinds should be believable as memories, and be able to serve as digitally-sourced memories of locations and trips. For that purpose,
 Rewinds should be believable as digitally-sourced memories, so we define the believability of a Rewind as its accuracy to the participant's memories.
-For distance and visit frequency, we found no statistically significant results, but in addition to our five metrics, we solicited other factors that affected a photo or Rewind's believability from participants.
+Overall, users were more likely to believe a Rewind was part of their memory (80\% to 78\%), but this was not statistically significant,
+but in addition to our five metrics, we solicited other factors that affected a photo or Rewind's believability from participants.
+
+\subsubsection{GPS Usage}
+% no significant effects on location belivability $\chi^2(1,86) = 0.666$, p = 0.2073(> 0.05)
+% signifant effects on trip belivability $\chi^2(1,128) = 2.917$, p = 0.0483(< 0.05)
+% GPS - 69%, non-GPS - 81%
+When splitting users between GPS users and non-GPS users, participants who were non-regular GPS users found photos and Rewinds to be accurate to their memory more often than regular GPS users did in terms of percentage ($\chi^2(1, N=128) = 2.917$, $p <.05$).
+Photos and Rewinds could only be considered accurate to a participant's memory if the participant first confirmed that they remembered the locations in them.
+% The results in this section reflect percentages from a total pool of only photos and Rewinds that have remembered locations.
+Regular GPS users found 65\% of photos and 45\% of Rewinds accurate to their memory out of the photos and Rewinds in which they remembered the locations.
+Participants who did not regularly use GPS found 78\% of photos and 63\% of Rewinds accurate to their memory.
+%So far, our findings show that
+So regular GPS users remembered the locations in their digital memories less often, and from the locations they did remember, they were less likely to find a photo or Rewind accurate to their memory.
+One participant who identified as a regular GPS user said, ``I really don't pay attention to my surroundings when I'm driving.
+I'm focused on the GPS and the road,'' when asked about the accuracy of a trip.
+%Our results show that GPS usage influences what features participants pick out when deciding whether Rewinds are accurate reflections of their own memories of their trips.
+When we split the responses of regular GPS users from the other participants' responses, we saw that GPS users looked at signs in the Rewind the most to determine accuracy.
+Participants who were not regular GPS users cited the route and surrounding landmarks as features which made the Rewind believable as memories.
+
+%\subsubsection{Frequent Travelers}
+% no significant effects on photo belivability $\chi^2(1,86) = 0$, p = 0.4947(> 0.05)
+% significant effects on video belivability $\chi^2(1,128) = 5.837$, p = 0.0079 (< 0.01)
+% frequent - 86%, non-frequent - 65%
 
@@
 % traveling alone - 84%, not alone - 72%
+%Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind was desired to be kept.
+Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep.
+Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others.
+This difference is mildly significant $\chi^2(1, N=127) = 1.865$, $p <.1)$.
+The data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.
+
+%\subsubsection{Distance}
+% no significant effects on photo/location belivability $\chi^2(5,86) = 7.745$, p = 0.1709 (> 0.05)
+% significant effects on video/trip belivability if we use alpha = 0.1 - $\chi^2(5,128) = 10.093$, p = 0.0726(< 0.1)
+% 0 - 100%, 1 - 75%, 2 - 75%, 3 - 85%, 4 - 80%, 5 - 33%
+
 Our findings show that in both photos and Rewinds, believability was higher when participants were traveling alone.

### 2016-09-21 paper/uist_2016/paper.tex
typo, apostrophe and table

@@
 Similarly in his seminal paper, \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through ``associative trails'', giving mankind the ability of ``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''.
-Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one’s sensory experiences about past visits.
+Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one's sensory experiences about past visits.
 
@@
 	\centering
-	\caption{Participant responses about the memorability, believability, and desirability or Rewinds and photos. The aggregate responses for the two mediums are compared.}
+	\caption{Participant responses about the memorability, believability, and desirability of Rewinds and photos. The aggregate responses for the two mediums are compared.}
 	\small
@@
 		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
-		\multicolumn{1}{|c|}{\%} & 0.97 & \multicolumn{2}{c|}{0.50} & 0.54 & 0.78 & 0.80 & 0.11 & 0.15 \\ \hline
+		\multicolumn{1}{|c|}{\%} & 97 & \multicolumn{2}{c|}{0.50} & 54 & 78 & 80 & 11 & 15 \\ \hline
 		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
 	\end{tabular}
-\label{table:Rewindvsphotos}
 \end{table*}
@@
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 60} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 119} & 120 & 59 & 74 & 11 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 5} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 8} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 18} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 71} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 64} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 10} & \cellcolor[HTML]{ACDDAA}47 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 81} \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.33} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.58} & 0.51 & 0.47 & 1.00 & 1.00 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 1.00} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.75} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.72} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.44} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.52} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.10} & \cellcolor[HTML]{ACDDAA}0.72 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.36} \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 33} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.58} & 0.51 & 0.47 & 1.00 & 1.00 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 1.00} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 75} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 72} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 44} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 52} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 10} & \cellcolor[HTML]{ACDDAA}72 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 36} \\ \cline{3-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{Photo}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$ \\ p =0.0016\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$ \\ p = 0.3953\end{tabular}} & \multicolumn{2}{c|}{N/A} & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$ \\ p = 0.0028\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$ \\ p = 0.0001\end{tabular}} \\ \cline{2-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 58 & 119 & 120 & 57 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 94} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 39} & 5 & 8 & 18 & 71 & 64 & 10 & 46 & 80 \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.48 & 0.56 & 0.53 & 0.54 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.62} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.90} & 0.60 & 0.25 & 0.56 & 0.59 & 0.50 & 0.60 & 0.52 & 0.56 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 48 & 56 & 53 & 54 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 62} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 90} & 60 & 25 & 56 & 59 & 50 & 60 & 52 & 56 \\ \cline{3-17}
 \multicolumn{1}{|c|}{\multirow{-6}{*}{Memorability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{Rewinds}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$ \\ p =0.1992\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$ \\ p = 0.4478\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 9.016$ \\ p = 0.0013\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$ \\ p = 0.4467\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$ \\ p = 0.3987\end{tabular}} \\ \hline
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 19 & 67 & 61 & 25 & \cellcolor[HTML]{ACDDAA}71 & \cellcolor[HTML]{ACDDAA}11 & 5 & 5 & 13 & 30 & 32 & 1 & 34 & 27 \\ \cline{3-17} 
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.68 & 0.81 & 0.77 & 0.80 & \cellcolor[HTML]{ACDDAA}0.82 & \cellcolor[HTML]{ACDDAA}0.45 & 0.80 & 0.60 & 0.69 & 0.90 & 0.75 & 0.00 & 0.71 & 0.89 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 68 & 81 & 77 & 80 & \cellcolor[HTML]{ACDDAA}82 & \cellcolor[HTML]{ACDDAA}45 & 80 & 60 & 69 & 90 & 75 & 0 & 71 & 89 \\ \cline{3-17} 
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{Photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$ \\ p = 0.2073\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$ \\ p = 0.4947\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 82) = 5.137$ \\ p = 0.0117\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$ \\ p= 0.1709\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$ \\ p =0.078\end{tabular}} \\ \cline{2-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}39 & \cellcolor[HTML]{ACDDAA}89 & \cellcolor[HTML]{ACDDAA}91 & \cellcolor[HTML]{ACDDAA}37 & 88 & 39 & 4 & 4 & 12 & 53 & 49 & 6 & 33 & 58 \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & 0.84 & 0.72 & 1.00 & 0.75 & 0.75 & 0.85 & 0.80 & 0.33 & 0.70 & 0.81 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}69 & \cellcolor[HTML]{ACDDAA}84 & \cellcolor[HTML]{ACDDAA}86 & \cellcolor[HTML]{ACDDAA}65 & 84 & 72 & 100 & 75 & 75 & 85 & 80 & 33 & 70 & 81 \\ \cline{3-17}
 \multicolumn{1}{|c|}{\multirow{-6}{*}{Believability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{Rewinds}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 60 & 119 & 120 & 59 & 74 & 11 & 5 & 8 & 18 & 71 & 67 & 10 & 47 & 81 \\ \cline{3-17} 
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.13 & 0.92 & 0.13 & 0.07 & 0.12 & 0.18 & 0.20 & 0.38 & 0.06 & 0.07 & 0.13 & 0.10 & 0.15 & 0.10 \\ \cline{3-17} 
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 13 & 92 & 13 & 7 & 12 & 18 & 20 & 38 & 6 & 7 & 13 & 10 & 15 & 10 \\ \cline{3-17} 
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{Photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$ \\ p = 0.2804\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$ \\ p = 0.3948\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$ \\ p = 0.1492\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$ \\ p = 0.2858\end{tabular}} \\ \cline{2-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 58} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 119} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 120} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 57} & 94 & 39 & 5 & 8 & 18 & 70 & 66 & 10 & 46 & 80 \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.09} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.02} & 0.13 & 0.26 & 0.00 & 0.00 & 0.11 & 0.10 & 0.20 & 0.40 & 0.11 & 0.18 \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 9} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 2} & 13 & 26 & 0 & 0 & 11 & 10 & 20 & 40 & 11 & 18 \\ \cline{3-17}
 \multicolumn{1}{|c|}{\multirow{-6}{*}{Desirability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{Rewinds}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$ \\ p = 0.0034\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$ \\ p = 0.059\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$ \\ p= 0.0729\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$ \\ p = 0.2288\end{tabular}} \\ \hline

### 2016-09-21 paper/uist_2016/paper.tex
removed mildly significant

@@
 Our findings show that in both photos and Rewinds, believability was higher when participants were traveling alone.
-For photos, the difference in believability between those traveling alone and those traveling with company was 37\%, $\chi^2(1, N=82) = 5.137$, $p < .05$.
-For Rewinds, the difference was 12\%, $\chi^2(1, 127) = 1.865$, $p = 0.086 (<.1)$.
+For photos, the difference in believability between those traveling alone and those traveling with company was 37\%, $\chi^2(1, N=82) = 5.137$, $p <.05$.
+For Rewinds, the difference was 12\%, $\chi^2(1, 127) = 1.865$, $p <.1)$.
 The smaller difference suggests that Rewinds are more believable than photos for trips taken with company.
@@
 % frequent - 86%, non-frequent - 65%
-Participants who identified as frequent travelers found 86\% of Rewinds believable and accurate to their memory, while non-frequent travelers found 65\% of Rewinds believable, $\chi^2(1, 128) = 5.835$
+Participants who identified as frequent travelers found 86\% of Rewinds believable and accurate to their memory, while non-frequent travelers found 65\% of Rewinds believable, $\chi^2(1, N=128) = 5.835$
 $p < .05$. This suggests that Rewinds would be more suitable for a particular type of person.
@@
 Our results show that participants who were non-regular GPS users found Rewinds believable more often than regular GPS users, suggesting the appropriate audience for Rewinds.
-Regular GPS users found Rewinds believable 69\% of the time, while non-regular users found Rewinds believable 84\% of the time, $\chi^2(1, 128) = 2.917$, $p < .05$.
+Regular GPS users found Rewinds believable 69\% of the time, while non-regular users found Rewinds believable 84\% of the time, $\chi^2(1, N=128) = 2.917$, $p < .05$.
 
@@
 Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others.
-This difference is mildly significant $\chi^2(1, N=127) = 1.865$, $p <.1)$.
-The data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.
+This difference is however not significant $\chi^2(1, N=127) = 1.865$, $p <.1)$, although the data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.
 

### 2016-09-21 paper/uist_2016/paper.tex
shorten Distance description

@@
 	\item Distance: how does the location's distance away from the participant's home influence the participant's perception of Rewinds and static photos?
-Distances ranged from 0 to 206,155 meters.
-For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 was 10--100 meters; Group 2 was 100--1,000 meters; Group 3 was 1,000--10,000 meters; Group 4 was 10,000--100,000 meters; and Group 5 was 100,000--1,000,000 meters from the participant's home location.
+Distances ranged from 0 to 206,155 meters so for analysis, these distances were logarithmically mapped to six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' The groups 0--6 were a distance of 0--10 meters, 10--100 meters, 100--1,000 meters, 1,000-10,000 meters, 10,000--100,000 meters, and over 100,000 meters from the user's home, respectively.
 	\item Visit frequency: do participants react differently to Rewinds and static photos depicting locations they visit frequently compared to locations they rarely visit?

### 2016-09-21 paper/uist_2016/paper.tex
fix some formatting bugs

@@
 
+% TODO explain tables
+\begin{table*}[t]
+	\centering
+	\caption{Participant responses about the memorability, believability, and desirability of Rewinds and photos. The aggregate responses for the two mediums are compared.}
+	\small
+	\label{within-subject-table}
+	\begin{tabular}{c|c|c|c|c|c|c|c|c|}
+		\cline{2-9}
+		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Believability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
+		& \begin{tabular}[c]{@{}c@{}}Rewinds\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}Photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}Rewinds\\ trip\end{tabular} & Photo & Rewinds & Photo & Rewinds \\ \hline
+		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
+		\multicolumn{1}{|c|}{\%} & 97 & \multicolumn{2}{c|}{0.50} & 54 & 78 & 80 & 11 & 15 \\ \hline
+		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
+	\end{tabular}
+\end{table*}
+
 % heather - need to be rephrased perhaps? Should we give a high level summary of all the relationships we've found? More analysis to be done for photo vs. videos, another table?
@@
 The findings of our user study center on the participants' relationships to the Rewinds generated from their location data compared to the static photos.
-We focus on the participants' judgments of their Rewinds' memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds (Table \ref{table:Rewindvsphotos}).
+We focus on the participants' judgments of their Rewinds' memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds (Table \ref{within-subject-table}).
 %We also discuss the participants' interactions with and reactions to their Rewinds.
@@
 \end{enumerate}
-
-% TODO explain tables
-\begin{table*}[t]
-	\centering
-	\caption{Participant responses about the memorability, believability, and desirability of Rewinds and photos. The aggregate responses for the two mediums are compared.}
-	\small
-	\label{within-subject-table}
-	\begin{tabular}{c|c|c|c|c|c|c|c|c|}
-		\cline{2-9}
-		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Believability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
-		& \begin{tabular}[c]{@{}c@{}}Rewinds\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}Photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}Rewinds\\ trip\end{tabular} & Photo & Rewinds & Photo & Rewinds \\ \hline
-		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
-		\multicolumn{1}{|c|}{\%} & 97 & \multicolumn{2}{c|}{0.50} & 54 & 78 & 80 & 11 & 15 \\ \hline
-		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
-	\end{tabular}
-\end{table*}
 
@@
 
-\section{Memorability}
+\subsection{Memorability}
 Rewinds, and digitally-mediated memories in general, are meant to engage a person's memory.

### 2016-09-21 paper/uist_2016/paper.tex
changes of table and companionship on memorability

@@
 		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
-		\multicolumn{1}{|c|}{\%} & 97 & \multicolumn{2}{c|}{0.50} & 54 & 78 & 80 & 11 & 15 \\ \hline
+		\multicolumn{1}{|c|}{\%} & 97 & \multicolumn{2}{c|}{50} & 54 & 78 & 80 & 11 & 15 \\ \hline
 		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
@@
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 60} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 119} & 120 & 59 & 74 & 11 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 5} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 8} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 18} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 71} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 64} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 10} & \cellcolor[HTML]{ACDDAA}47 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 81} \\ \cline{3-17}
-\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 33} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.58} & 0.51 & 0.47 & 1.00 & 1.00 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 1.00} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 75} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 72} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 44} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 52} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 10} & \cellcolor[HTML]{ACDDAA}72 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 36} \\ \cline{3-17}
+\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 33} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 58} & 51 & 47 & 100 & 100 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 100} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 75} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 72} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 44} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 52} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 10} & \cellcolor[HTML]{ACDDAA}72 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 36} \\ \cline{3-17}
 \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{Photo}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$ \\ p =0.0016\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$ \\ p = 0.3953\end{tabular}} & \multicolumn{2}{c|}{N/A} & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$ \\ p = 0.0028\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$ \\ p = 0.0001\end{tabular}} \\ \cline{2-17}
@@
 % trip accompanies have siginificant effects on both location and trip rememberance. 
-% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
+% location rememberance: travel alone -  100%, not alone - 100%, $\chi^2(1,94) = 31.812$, p < 0.01
 % trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
-Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way.
-For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compared to 55\% reported by participants who believed that they traveled in groups, with $\chi^2(1, N=94) = 31.812$, $p <.00001$.
-On the other hand, trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and I walked a certain way -- don't usually take this route".
+Our study shows that trip remembrance is influenced by the presence of travel companions.
+Trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and I walked a certain way -- don't usually take this route".
 Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1, N=133) = 9.016$, $p <.01)$.
+For location rememberance, participants who believed that they traveled alone and those who believed that they traveled with companions all had a 100\% successful recalling rate.
+Note that this is because those who reported on their companionship were the ones that recognized the places from the images.
 

### 2016-09-22 paper/uist_2016/paper.tex
submitted version

@@
 By picking a start and end location from a particular trip and generating a Rewind between these points, the user relives their memories in a continuous manner.
-Similarly in his seminal paper, \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through ``associative trails'', giving mankind the ability of ``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''.
+Similarly in his seminal paper, \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access, giving mankind the ability of ``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''.
 Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one's sensory experiences about past visits.
@@
 \subsection{Location History}
-Silva and Aizawa build on location data to provide a visual examination of interested traveling routes by linking geo-tagging metadata with online imageries, specifically Google Street View images \cite{deSilva:2009:RMT:1631272.1631414}.
-The authors proposed a sketch-based interface that would perform spatial and temporal queries on line drawings specified by the users.
-Rewind resembles this interactive system, in a way that the reconstructed sceneries are of a careful mapping results from geolocation data and Google Street View images.
-However, Rewind differs in that the mapping is finalized with geolocation data provided by users tracked using smartphones.
-This means that Rewind serves more of a geteway for recalling episodic memory rather than reviewing a potential travelling itinerary, aiming to provide a mechanism for reminiscence and sharing of past experience while exploring users' behavioral patterns.
-Moreover, the reconstruction techniques used in Rewind would differentiate the same retrieved image with various temporal cues such as changes in seasons.
-%; yet the immediate results from the temporal queries suggested by de Silva and Aizawa have not been fully revealed.
-
 Larsen et al.
@@
 Rewind inputs geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images (although other street side photo services may be used).
-The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues.
+The sceneries in each photo-video pair are customized for each user based on times of the day, weather conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues.
 The current version of Rewind system is a open-sourced, web-based application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store them.
@@
 
-Since environmental characteristics, such as meteorological attributes, of images retrieved using Google Street View Static Image API are not directly exposed nor adjustable, it is hard to conclude if the retrieved images would correctly reflect the timely and ambient properties at the time when the user undertook the path.
-To compensate for this, pixel-wise adjustment was applied on each Google Street View image to better convey time-specific messages including times of the day, seasonal variances and meteorological specifics.
+Since environmental characteristics, such as weather attributes, of images retrieved using Google Street View Static Image API are not directly exposed nor adjustable, it is hard to conclude if the retrieved images would correctly reflect the timely and ambient properties at the time when the user undertook the path.
+To compensate for this, pixel-wise adjustment was applied on each Google Street View image to better convey time-specific messages including times of the day, seasonal variances and weather specifics.
 Previous work done by \cite{laffont2014transient,shih2013data} have successfully reconstructed images with varying diurnal and seasonal cycles, yet it would be computationally expensive to replicate the proposed techniques in real-time on large sets of images.
@@
 
-For meteorological conditions, a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations was used for weather lookup (for the study, only data from [anonymized: our state/province] was loaded).
+For weather conditions, a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations was used for weather lookup (for the study, only data from [anonymized: our state/province] was loaded).
 Sky colors were adjusted again using the technique mentioned previously for overcast, rainy and snowy sky.
